### 2021-11-02 src/ms.tex
Initial commit

% Define document class
\documentclass[twocolumn]{aastex631}

% Filler text
\usepackage{blindtext}

% Begin!
\begin{document}

% Title
\title{An open source scientific article}

% Author list
\author{First Author}

% Abstract with filler text
\begin{abstract}
    \blindtext
\end{abstract}

% Main body with filler text
\section{Introduction}
\Blindtext[4]

\end{document}

### 2021-11-02 src/figures/detector_sc_compare.py
add all figure scripts

@@ -1,0 +1,50 @@
+import legwork as lw
+import numpy as np
+import astropy.units as u
+import matplotlib.pyplot as plt
+
+plt.rc('font', family='serif')
+plt.rcParams['text.usetex'] = False
+fs = 24
+
+# update various fontsizes to match
+params = {'figure.figsize': (12, 8),
+          'legend.fontsize': fs,
+          'axes.labelsize': fs,
+          'xtick.labelsize': 0.9 * fs,
+          'ytick.labelsize': 0.9 * fs,
+          'axes.linewidth': 1.1,
+          'xtick.major.size': 7,
+          'xtick.minor.size': 4,
+          'ytick.major.size': 7,
+          'ytick.minor.size': 4}
+plt.rcParams.update(params)
+
+# create new figure
+fig, ax = plt.subplots()
+
+# define the frequency range of interest
+fr = np.logspace(-4, 0, 1000) * u.Hz
+
+# plot a sensitivity curve for different mission lengths
+linewidth = 4
+for i, t_obs in enumerate([0.5, 2.0, 4.0]):
+    lw.visualisation.plot_sensitivity_curve(frequency_range=fr, t_obs=t_obs * u.yr,
+                                            fig=fig, ax=ax, show=False, fill=False, linewidth=linewidth,
+                                            color=plt.get_cmap("Blues")((i + 1) * 0.3),
+                                            label=r"LISA ($t_{{\rm obs}} = {{{}}} \, {{\rm yr}}$)".format(t_obs))
+
+# plot the LISA curve with an approximate response function
+lw.visualisation.plot_sensitivity_curve(frequency_range=fr, approximate_R=True,
+                                        fig=fig, ax=ax, show=False, fill=False, linewidth=linewidth,
+                                        color=plt.get_cmap("Purples")(0.5),
+                                        label=r"LISA (approximate $\mathcal{R}(f)$)")
+
+# plot the TianQin curve
+lw.visualisation.plot_sensitivity_curve(frequency_range=fr, instrument="TianQin", label="TianQin",
+                                        fig=fig, ax=ax, show=False, linewidth=linewidth,
+                                        color=plt.get_cmap("Greens")(0.6), fill=False)
+
+ax.legend(fontsize=0.7*fs)
+
+plt.savefig("detector_sc_compare.pdf", format="pdf", bbox_inches="tight")

### 2021-11-02 src/figures/detector_snr_ratio.py

@@ -1,0 +1,92 @@
+import legwork as lw
+import numpy as np
+import astropy.units as u
+import matplotlib.pyplot as plt
+from matplotlib.colors import TwoSlopeNorm
+
+plt.rc('font', family='serif')
+plt.rcParams['text.usetex'] = False
+fs = 24
+
+# update various fontsizes to match
+params = {'figure.figsize': (12, 8),
+          'legend.fontsize': fs,
+          'axes.labelsize': fs,
+          'xtick.labelsize': 0.9 * fs,
+          'ytick.labelsize': 0.9 * fs,
+          'axes.linewidth': 1.1,
+          'xtick.major.size': 7,
+          'xtick.minor.size': 4,
+          'ytick.major.size': 7,
+          'ytick.minor.size': 4}
+plt.rcParams.update(params)
+
+# spread out some frequencies and eccentricities
+f_orb_s = np.logspace(-4, -1, 200) * u.Hz
+ecc_s = np.linspace(0, 0.9, 150)
+
+# turn them into a grid
+F, E = np.meshgrid(f_orb_s, ecc_s)
+
+# flatten the grid
+F_flat, E_flat = F.flatten(), E.flatten()
+
+# put all of the sources at the same distance with the same mass
+m_1 = np.repeat(10, len(F_flat)) * u.Msun
+m_2 = np.repeat(10, len(F_flat)) * u.Msun
+dist = np.repeat(8, len(F_flat)) * u.kpc
+
+# define a set of sources
+sources = lw.source.Source(m_1=m_1, m_2=m_2, f_orb=F_flat, ecc=E_flat, dist=dist, gw_lum_tol=1e-3)
+sources.get_merger_time()
+
+# compute the LISA SNR
+LISA_snr = sources.get_snr(verbose=True, which_sources=sources.t_merge > 0.1 * u.yr)
+
+# compute the TianQin SNR
+sources.update_sc_params({"instrument": "TianQin", "L": None})
+TQ_snr = sources.get_snr(instrument="TianQin", verbose=True, which_sources=sources.t_merge > 0.1 * u.yr)
+
+# create a figure
+fig, ax = plt.subplots(figsize=(14, 12))
+ax.set_xscale("log")
+ax.set_xlabel(r"Orbital Frequency, $f_{\rm orb} \, [{\rm Hz}]$")
+ax.set_ylabel(r"Eccentricity, $e$")
+
[…]

### 2021-11-02 src/figures/horizon_distance.py

@@ -1,0 +1,164 @@
+import legwork as lw
+import numpy as np
+import astropy.units as u
+import matplotlib.pyplot as plt
+
+plt.rc('font', family='serif')
+plt.rcParams['text.usetex'] = False
+fs = 24
+
+# update various fontsizes to match
+params = {'figure.figsize': (12, 8),
+          'legend.fontsize': fs,
+          'axes.labelsize': fs,
+          'xtick.labelsize': 0.9 * fs,
+          'ytick.labelsize': 0.9 * fs,
+          'axes.linewidth': 1.1,
+          'xtick.major.size': 7,
+          'xtick.minor.size': 4,
+          'ytick.major.size': 7,
+          'ytick.minor.size': 4}
+plt.rcParams.update(params)
+
+# create a list of masses and frequencies
+m_c_grid = np.logspace(-1, np.log10(50), 500) * u.Msun
+f_orb_grid = np.logspace(np.log10(4e-5), np.log10(3e-1), 400) * u.Hz
+
+# turn the two lists into grids
+MC, FORB = np.meshgrid(m_c_grid, f_orb_grid)
+
+# flatten grids
+m_c, f_orb = MC.flatten(), FORB.flatten()
+
+# convert chirp mass to individual masses for source class
+q = 1.0
+m_1 = m_c / q**(3/5) * (1 + q)**(1/5)
+m_2 = m_1 * q
+
+# use a fixed distance and circular binaries
+dist = np.repeat(1, len(m_c)) * u.kpc
+ecc = np.zeros(len(m_c))
+
+# create the source class
+sources = lw.source.Source(m_1=m_1, m_2=m_2, dist=dist, f_orb=f_orb, ecc=ecc, gw_lum_tol=1e-3)
+
+# calculate merger times and then SNR
+sources.get_merger_time()
+sources.get_snr(verbose=True)
+
+# reshape the output into grids
+t_merge_grid = sources.t_merge.reshape(MC.shape)
+snr_grid = sources.snr.reshape(MC.shape)
+
+def fmt_time(x):
+    if x == 4:
+        return r"$t_{\rm merge} = T_{\rm obs}$"
+    elif x >= 1e9:
+        return "{0:1.0f} Gyr".format(x / 1e9)
+    elif x >= 1e6:
+        return "{0:1.0f} Myr".format(x / 1e6)
+    elif x >= 1e3:
+        return "{0:1.0f} kyr".format(x / 1e3)
+    elif x >= 1:
[…]

### 2021-11-02 src/figures/merger_time_contours.py

@@ -1,0 +1,53 @@
+import legwork as lw
+import numpy as np
+import astropy.units as u
+import matplotlib.pyplot as plt
+
+plt.rc('font', family='serif')
+plt.rcParams['text.usetex'] = False
+fs = 24
+
+# update various fontsizes to match
+params = {'figure.figsize': (12, 8),
+          'legend.fontsize': fs,
+          'axes.labelsize': fs,
+          'xtick.labelsize': 0.9 * fs,
+          'ytick.labelsize': 0.9 * fs,
+          'axes.linewidth': 1.1,
+          'xtick.major.size': 7,
+          'xtick.minor.size': 4,
+          'ytick.major.size': 7,
+          'ytick.minor.size': 4}
+plt.rcParams.update(params)
+
+f_range = np.logspace(-5, -1, 100) * u.Hz
+e_range = np.linspace(0, 0.99, 500)
+
+m_1 = np.repeat(10, len(f_range) * len(e_range)) * u.Msun
+m_2 = np.repeat(10, len(f_range) * len(e_range)) * u.Msun
+
+F, E = np.meshgrid(f_range, e_range)
+
+t_merge = lw.evol.get_t_merge_ecc(ecc_i=E.flatten(), f_orb_i=F.flatten(), m_1=m_1, m_2=m_2).reshape(F.shape)
+
+fig, ax = plt.subplots()
+
+cont = ax.contourf(F, E, np.log10(t_merge.to(u.yr).value), cmap="plasma_r", levels=np.linspace(-8, 10, 19))
+cbar = fig.colorbar(cont, label=r"Merger time, $\log_{10} (t_{\rm merge} / {\rm yr})$")
+ax.set_xscale("log")
+
+# hide edges that show up in rendered PDFs
+for c in cont.collections:
+    c.set_edgecolor("face")
+
+mass_string = ""
+mass_string += r"$m_1 = {{{}}} \, {{ \rm M_{{\odot}}}}$".format(m_1[0].value)
+mass_string += "\n"
+mass_string += r"$m_2 = {{{}}} \, {{ \rm M_{{\odot}}}}$".format(m_2[0].value)
+ax.annotate(mass_string, xy=(0.5, 0.04), xycoords="axes fraction", fontsize=0.6*fs,
+            bbox=dict(boxstyle="round", color="white", ec="white", alpha=0.5), ha="center", va="bottom")
+
[…]

### 2021-11-02 src/figures/role_eccentricity.py

@@ -1,0 +1,87 @@
+import legwork as lw
+import numpy as np
+import astropy.units as u
+import matplotlib.pyplot as plt
+
+plt.rc('font', family='serif')
+plt.rcParams['text.usetex'] = False
+fs = 24
+
+# update various fontsizes to match
+params = {'figure.figsize': (12, 8),
+          'legend.fontsize': fs,
+          'axes.labelsize': fs,
+          'xtick.labelsize': 0.9 * fs,
+          'ytick.labelsize': 0.9 * fs,
+          'axes.linewidth': 1.1,
+          'xtick.major.size': 7,
+          'xtick.minor.size': 4,
+          'ytick.major.size': 7,
+          'ytick.minor.size': 4}
+plt.rcParams.update(params)
+
+# set eccentricities
+ecc = np.array([1e-6, 0.6, 0.9])
+n_binaries = len(ecc)
+
+# use constant values for mass, f_orb and distance
+m_1 = np.repeat(0.6, n_binaries) * u.Msun
+m_2 = np.repeat(0.6, n_binaries) * u.Msun
+f_orb = np.repeat(1.5e-3, n_binaries) * u.Hz
+dist = np.repeat(15, n_binaries) * u.kpc
+
+# get the SNR in each harmonic
+snr2_n = lw.snr.snr_ecc_evolving(m_1=m_1, m_2=m_2, f_orb_i=f_orb, ecc=ecc, dist=dist,
+                                 harmonics_required=100, t_obs=4 * u.yr, n_step=1000,
+                                 ret_snr2_by_harmonic=True)
+
+snr = snr2_n.sum(axis=1)**(0.5)
+
+# plot LISA sensitivity curve
+fig, ax = lw.visualisation.plot_sensitivity_curve(frequency_range=np.logspace(-3.5, 0, 1000) * u.Hz,
+                                                  show=False)
+
+# plot each sources
+colours = [plt.get_cmap("plasma")(i) for i in [0.1, 0.5, 0.8]]
+for i in range(len(snr2_n)):
+    # work out the harmonic frequencies and ASDs
+    f_harm = f_orb[i] * range(1, len(snr2_n[0]) + 1)
+    y_vals = lw.psd.lisa_psd(f_harm)**(0.5) * np.sqrt(snr2_n)[i]
+
+    # only plot points above the sensitivity curve
+    mask = np.sqrt(snr2_n)[i] > 1.0
+
+    # compute the index of the maximal SNR value
[…]

### 2021-11-02 src/figures/snr_over_time.py

@@ -1,0 +1,86 @@
+import legwork as lw
+import numpy as np
+import astropy.units as u
+import matplotlib.pyplot as plt
+
+plt.rc('font', family='serif')
+plt.rcParams['text.usetex'] = False
+fs = 24
+
+# update various fontsizes to match
+params = {'figure.figsize': (12, 8),
+          'legend.fontsize': fs,
+          'axes.labelsize': fs,
+          'xtick.labelsize': 0.9 * fs,
+          'ytick.labelsize': 0.9 * fs,
+          'axes.linewidth': 1.1,
+          'xtick.major.size': 7,
+          'xtick.minor.size': 4,
+          'ytick.major.size': 7,
+          'ytick.minor.size': 4}
+plt.rcParams.update(params)
+
+m_1 = 15 * u.Msun
+m_2 = 15 * u.Msun
+dist = 20 * u.kpc
+ecc = 0.5
+f_orb = 3e-5 * u.Hz
+
+t_merge = lw.evol.get_t_merge_ecc(m_1=m_1, m_2=m_2, ecc_i=ecc, f_orb_i=f_orb)
+
+ecc_evol, f_orb_evol, timesteps = lw.evol.evol_ecc(m_1=m_1,
+                                                   m_2=m_2,
+                                                   ecc_i=ecc,
+                                                   f_orb_i=f_orb,
+                                                   t_evol=t_merge - 100 * u.yr,
+                                                   avoid_merger=False,
+                                                   output_vars=["ecc", "f_orb", "timesteps"],
+                                                   n_step=1000)
+
+source = lw.source.Source(m_1=np.repeat(m_1, len(ecc_evol)),
+                          m_2=np.repeat(m_2, len(ecc_evol)),
+                          dist=np.repeat(dist, len(ecc_evol)),
+                          ecc=ecc_evol,
+                          f_orb=f_orb_evol)
+
+snr = source.get_snr()
+
+fig, axes = plt.subplots(3, 1, figsize=(8, 15))
+fig.subplots_adjust(hspace=0.3)
+
+# calculate the time before the merger rather than timesteps
+t_before_merger = (t_merge - timesteps).to(u.Myr)
+
+# plot the eccentricity
+axes[0].plot(t_before_merger, source.ecc, lw=3)
[…]

### 2021-11-02 src/ms.tex
add entire tex file

@@
-% Define document class
-\documentclass[twocolumn]{aastex631}
+\documentclass[twocolumn]{aastex63}
+\received{\today}
+\shorttitle{LEGWORK}
+\graphicspath{{./}{figures/}}
 
-% Filler text
-\usepackage{blindtext}
+\usepackage{physics}
+\usepackage{mathtools}
+\usepackage{etoolbox}
+\usepackage{fontawesome5}
 
-% Begin!
+% remove indents in footnotes
+\usepackage[hang,flushmargin]{footmisc}
+
+\newcommand{\todo}[1]{{\color{red}{[TODO: #1}]}}
+
+% custom function for adding units
+\makeatletter
+\newcommand{\unit}[1]{%
+    \,\mathrm{#1}\checknextarg}
+\newcommand{\checknextarg}{\@ifnextchar\bgroup{\gobblenextarg}{}}
+\newcommand{\gobblenextarg}[1]{\,\mathrm{#1}\@ifnextchar\bgroup{\gobblenextarg}{}}
+\makeatother
+
+\newcommand{\avg}[1]{\left\langle#1\right\rangle}
+
+% LEGWORK stuff
+\newcommand{\lw}{LEGWORK}
+\newcommand{\lwColour}{SeaGreen}
+\newcommand{\lwModURL}[1]{https://legwork.readthedocs.io/en/latest/modules.html\#module-legwork.#1}
+\newcommand{\lwModLink}[1]{\href{https://legwork.readthedocs.io/en/latest/modules.html\#module-legwork.#1}{\color{\lwColour}{\texttt{#1}}}}
+\newcommand{\lwFuncURL}[2]{https://legwork.readthedocs.io/en/latest/api/legwork.#1.#2.html\#legwork.#1.#2}
+
+% icons and links
+\newcommand{\docsIcon}{{\color{\lwColour}{\faFileCode}}}
+\newcommand{\docsLink}[1]{\href{#1}{\docsIcon}}
+
+\newcommand{\tutorialIcon}{{\color{\lwColour}{\faLaptopCode}}}
+\newcommand{\tutorialLink}[1]{\href{#1}{\tutorialIcon}}
+
+\newcommand{\notebookIcon}{{\color{\lwColour}{\faBook}}}
+\newcommand{\notebookLink}[1]{\href{#1}{\notebookIcon}}
+
+% add documentation links to equation environments
+% Luger+19 inspired this!
+\newtagform{eqtag}[]{(}{)}
+
+\renewenvironment{equation}[1]{%
+    \ifstrempty{#1}{%
+        \renewtagform{eqtag}[]{(}{)}%
+    }{%
+        \renewtagform{eqtag}[]{\docsLink{#1}\,(}{)}%
+    }%
+    \usetagform{eqtag}%
+    \align%
+    }{%
+    \endalign%
+    \renewtagform{eqtag}[]{(}{)}%
+    \usetagform{eqtag}%
+}
+
 \begin{document}
 
-% Title
-\title{An open source scientific article}
+\title{LEGWORK: LISA Evolution and Gravitational Wave Orbit Kit}
 
-% Author list
-\author{First Author}
+% affiliations
+\newcommand{\cfa}{Center for Astrophysics | Harvard \& Smithsonian, 60 Garden Street, Cambridge, MA 02138, USA}
+\newcommand{\mpa}{Max-Planck-Institut für Astrophysik, Karl-Schwarzschild-Straße 1, 85741 Garching, Germany}
+\newcommand{\cca}{Center for Computational Astrophysics, Flatiron Institute, 162 Fifth Ave, New York, NY, 10010, USA}
+\newcommand{\UoA}{Anton Pannekoek Institute for Astronomy and GRAPPA, University of Amsterdam, NL-1090 GE Amsterdam, The Netherlands}
+\newcommand{\UW}{Department of Astronomy, University of Washington, Seattle, WA, 98195}
 
-% Abstract with filler text
+\author[0000-0001-6147-5761]{T. Wagg}
+\affiliation{\UW}
+\affiliation{\cfa}
+\affiliation{\mpa}
+
+\author[0000-0001-5228-6598]{K. Breivik}
+\affiliation{\cca}
+
+\author[0000-0001-9336-2825]{S. E. de Mink}
+\affiliation{\mpa}
+\affiliation{\UoA}
+\affiliation{\cfa}
+
+\correspondingauthor{Tom Wagg}
+\email{tomjwagg@gmail.com}
+
 \begin{abstract}
-    \blindtext
+    We present \lw{}, a Python package for making predictions about stellar-origin gravitational wave sources and their detectability in LISA and other space-based gravitational wave detectors.
+\lw{} can be used to evolve sources over time, calculate gravitational wave strains, compute signal-to-noise ratios and visualise the results.
+In this paper we give an overview of the structure and functionality of the package, as well as highlight several optimisations that make it particularly efficient.
+We demonstrate the various capabilities of \lw{} through a series of example use cases.
+These begin with a basic example of calculating the signal-to-noise ratio of a source but also include using \lw{} to calculate horizon distances and make comparisons between gravitational-wave detectors.
+We additionally explain in detail the derivation of the equations behind \lw{} in order to clarify some conflicts currently present in the literature.
 \end{abstract}
 
-% Main body with filler text
+\keywords{gravitational waves, LISA}
+
 \section{Introduction}
-\Blindtext[4]
+
+The planned space-based gravitational wave detector LISA (Laser Interferometer Space Antenna) will present an entirely new view of gravitational waves by focusing on lower frequencies ($10^{-5} < f / \unit{Hz} < 10^{-1}$) than ground-based detectors.
+This will enable the study of the gravitational wave mergers of supermassive black holes that are undetectable with ground-based detectors \citep[e.g.][]{Begelman+1980, Klein+2016}.
+However, this frequency regime is also of interest for the detection of local stellar-mass binaries during their inspiral phase.
+LISA is expected to detect Galactic stellar-origin compact objects, ranging from the numerous double white dwarf (WDWD) population, to the rare but loud double black hole (BHBH) population.
+
+The potential to detect stellar-origin sources with LISA has been studied in the past \citep[e.g.][]{Nelemans+2001, Belczynski+2010}.
+More recently, the direct detection of gravitational waves with ground-based detectors has led to renewed interest in this topic with many recent papers addressing the issue \citep[e.g.][]{Christian+2017, Kremer+2017, Kremer+2018, Korol+2017, Korol+2018, Korol+2019, Korol+2020, Lamberts+2018, Lamberts+2019, Fang+2019, Andrews+2020, Lau+2020, Breivik+2020, Breivik+2020a, Roebber+2020, Chen+2020, Sesana+2020}.
+
+Each of these studies require making estimates of the signal-to-noise ratio of individual binary systems and possibly the slow gravitational wave inspiral that lead to the present-day parameters.
+So far, most studies made use of custom made codes which have not been made publicly available.
+
+We believe that the large renewed interest in LISA and the stellar-origin sources it may detect will lead to many more studies in the near future that would need similar computations.
+This leads to a significant amount of redundancy which, at best results in extra work for each individual and at worst leads to an increased chance of introducing mistakes and inconsistencies when coding up the necessary expressions.
+
+\lw{} is a Python package designed to streamline the process of making predictions of LISA detection rates for stellar-origin binaries such that it is fast, reliable and simple.
+With \lw{} one can evolve the orbits of a binary or a collection of binaries and calculate their strain amplitudes for any range of harmonics.
+One can compute the sensitivity curve for LISA or other future gravitational wave detectors (e.g.
+TianQin's curve, or that of a custom instrument) and use it to compute the signal-to-noise ratio of a collection of sources.
+Furthermore, \lw{} provides tools to visualise all of the results with easy-to-use plotting functions.
+
+Specifically, we implement the expressions by \citet{Peters+1963} and \citet{Peters+1964} for the evolution of binary orbits, equations for the strain amplitudes and signal-to-noise ratios of binaries from various papers \citep[e.g.][]{Flanagan+1998, Finn+2000, Barack+2004, Moore+2015} and approximations for the LISA and TianQin sensitivity curves given in \citet{Robson+2019} and \citet{Huang+2020} respectively.
+
+The open-source nature of the project means that new users as well as seasoned experts in the field can work together in a collaborative setting to consider new features and enhancements to the package as well as check the implementation.
+At the same time, with our thorough online documentation, derivations and tutorials, we hope \lw{} can make this functionality more accessible to the broader scientific community.
+
+\lw{} can be installed with pip or obtained from the GitHub repository \href{https://github.com/TeamLEGWORK/LEGWORK}{\faGithub}\footnote{\url{https://github.com/TeamLEGWORK/LEGWORK}}.
+All examples shown in this paper and code to reproduce the figures are available in the repository.
+Throughout this paper a \tutorialIcon{} icon in a section links to a related online tutorial and a \notebookIcon{} icon links to a Jupyter notebook with related code examples.
+Instructions for installation and basic usage are provided in the online documentation\footnote{\url{https://legwork.readthedocs.io/en/latest/}} which contain the most up-to-date instructions.
+
+The paper is organised as follows.
+In Section~\ref{sec:LEGWORK-overview} we give an overview of the capabilities of the \lw{} package and its various modules.
+In Section~\ref{sec:example-uses} we outline some example use cases of \lw{} to demonstrate its use.
+We detail the derivations of the equations relevant for \lw{} in Section~\ref{sec:derivations}.
+Finally, in Section~\ref{sec:summary} we conclude and summarise our work.
+
+\section{Package Overview}\label{sec:LEGWORK-overview}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=\columnwidth]{package_overview_witharrows.png}
+    \caption{Package structure of \lw{}. Each box represents a module and describes its function. The arrows indicate the inter-dependencies of the modules.}
+    \label{fig:package_overview}
+\end{figure}
+
+The \lw{} package is composed of seven modules that each focus on a particular aspect of calculations useful for LISA gravitational wave sources.
+In Fig.~\ref{fig:package_overview}, we illustrate the general structure of the package with its various modules.
+The source module is the central module of the package and provides an simple interface to the functions in the rest of the modules.
+For more complex analyses, users may want to interact directly with individual modules, particularly those in the top row of Fig.~\ref{fig:package_overview} as they comprise the core functionality of \lw{}.
+Below we explain the capabilities of each module in detail.
+
+\lwModLink{evol} deals with the orbital evolution of a binary due to gravitational waves.
+It includes functions for computing the merger times of both circular and eccentric binaries.
+In addition, you can use this module to evolve binary orbit parameters forward in time with any number or arrangement of timesteps.
+We discuss the relevant equations in Sec.~\ref{sec:deriv_evol}.
+
+\lwModLink{strain} contains two functions that compute a binary's gravitational wave strain and characteristic strain amplitude respectively.
+Each of these functions is capable of computing the strain for a 3-dimensional array of binaries at any number of timesteps and evaluated at any number of harmonics.
+We discuss the relevant equations in Sec.~\ref{sec:deriv_strain}.
+
+\lwModLink{psd} is used for evaluating the effective noise power spectral density of a detector at different frequencies.
+The module contains both the LISA and TianQin sensitivity curves that can be tweaked by adjusting parameters such as the observation time, confusion noise and even the arm length.
+Additionally, this module allows the user to specify a custom detector sensitivity curve.
+We discuss the relevant equations in Sec.~\ref{sec:deriv_psd}.
+
+\lwModLink{snr} uses the functions in \texttt{evol}, \texttt{strain} and \texttt{psd} to compute the signal-to-noise ratio of sources.
+It contains four functions that cover the permutations of whether a source is circular or eccentric and stationary in frequency space on the timescale of the mission or evolving.
+We discuss the relevant equations in Sec.~\ref{sec:deriv_snr}.
+
+\lwModLink{visualisation} contains several wrappers for plotting 1- and 2-dimensional distributions with histograms, scatter plots, and kernel density estimator (KDE) plots in order to quickly analyse a collection of sources.
+In addition, it provides functions for plotting sources directly onto a sensitivity curve.
+
+\lwModLink{source} provides a direct and simple interface to the functions in other modules through the \texttt{Source} Class.
+You can instantiate this Class with an array of sources and use it compute their strains or signal-to-noise ratios directly.
+Moreover, depending on the user's choice of allowed gravitational wave luminosity error, the Class dynamically decides on the number of harmonics needed to capture the full signal of each binary and at what eccentricity to no longer consider a binary circular.
+This Class also provides a quick means of evolving the sources, visualising the parameters of each source and allows you to plot the binaries on the sensitivity curve.
+
+\lwModLink{utils} is a collection of miscellaneous utility functions mainly consisting of conversions between variables as well as constants and expressions from \citet{Peters+1964}.
+We discuss the relevant equations in Sec.~\ref{sec:deriv_utils}.
+
+\subsection{Optimistations}
+
+We developed \lw{} with an emphasis on increasing the efficiency of these computations in order to make large scale simulations more tractable.
+As a simple first step, we ensured that the entirety of \lw{} is vectorised and thus scales well with larger populations.
+In addition, we made a several specific optimisations to further increase the speed of calculations.
+
+In certain cases one can apply approximations in place of the general SNR calculations.
+Although it is possible to use each of these approximations directly through the \lwModLink{snr} module, the \lwModLink{source} module will automatically apply the most appropriate function for each individual source.
+\lw{} dynamically classifies each source as one of four types, which cover the permutations of whether a binary is effectively circular or eccentric and whether or not it is stationary in frequency space on the timescale of the LISA mission.
+Then when computing the SNR, it applies a different function to each type of the source.
+This avoids computing unnecessary, time intensive integrals.
+
+Moreover, for increasingly eccentric sources, gravitational waves are emitted in an increasing number of higher harmonics.
+Although the total SNR is formally calculated as a the sum of the SNR over an infinite number of harmonics, in practice it is sufficient to only consider a subset.
+In the \lwModLink{source} module, the user can provide \texttt{gw\_lum\_tol}, a maximum allowable tolerance for the accuracy of the gravitational wave luminosity.
+Given this tolerance, \lw{} automatically calculates the required number of harmonics to satisfy this tolerance and thus minimise the computation time.
+
+Lastly, as a simple (yet thoroughly effective) optimisation, we interpolate (1) $g(n, e)$, which is a complicated combination of Bessel functions used in several calculations (see Eq.~\ref{eq:g(n,e)}) (2) the given sensitivity curve $S_{\rm n}(f)$.
+This significantly reduces the runtime of most strain and SNR calculations for large populations of sources.
+
+\section{Use cases}\label{sec:example-uses}
+In this section, we demonstrate \lw{}'s range of capabilities through a series of example use cases.
+The plots and results in each subsection are reproduced directly in online demos in the \lw{} documentation, which are each based on individual Jupyter notebooks.
+These are linked at the start of each subsection with the \tutorialIcon{} and \notebookIcon{} icons respectively.
+
+\subsection{Computing the SNR of a binary system\texorpdfstring{ - \tutorialLink{https://legwork.readthedocs.io/en/latest/demos/BasicSNRCalculation.html} \notebookLink{https://github.com/TeamLEGWORK/LEGWORK/blob/main/docs/demos/BasicSnrCalculation.ipynb}}{}}
+
+The most fundamental use case of \lw{} is to compute the SNR of a binary system in LISA.
+This can be accomplished in \lw{} with only two lines of code - one line to set up the source and another to compute the SNR.
+As an example one could consider a binary with the parameters
+\begin{align*}
+    m_1 = m_2 &= 10 \unit{M_{\odot}},\ d = 8 \unit{kpc},\\
+    f_{\rm orb} &= 10^{-4} \unit{Hz},\ e = 0.2,
+\end{align*}
+where $m_1, m_2$ are the primary and secondary masses, $d$ is the distance to the source, $f_{\rm orb}$ is the orbital frequency and $e$ is the eccentricity.
+As we don't specify a position, polarisation or inclination, \lw{} will calculate the SNR averaged over these quantities.
+One can now instantiate a source in \lw{} using these parameters (leaving the LISA mission parameters as the default values, such that we compute the SNR for a 4-year LISA mission).
+As shown in the linked demo, \lw{} quickly computes that the SNR of this binary is $4.49$.
+In the background, \lw{} decides which SNR approximation is most applicable given the eccentricity of the binary and whether it is stationary in frequency space.
+
+Moreover, this can be generalised to a population of many binary systems with ease.
+Instead of inputting single values for each parameter, one can input arrays of values where each entry corresponds to a different binary.
+As an example, we can take the same parameters as above for 3 different binaries but vary the primary as $m_1 = [5, 10, 15] \unit{M_{\odot}}$.
+Using \lw{} we find that the SNR for each of these cases is $\rho = [2.47, 4.49, 7.85]$.
+
+\subsection{Horizon distance\texorpdfstring{ - \tutorialLink{https://legwork.readthedocs.io/en/latest/demos/HorizonDistance.html} \notebookLink{https://github.com/TeamLEGWORK/LEGWORK/blob/main/docs/demos/HorizonDistance.ipynb}}{}}
+
+\begin{figure*}[htb]
+    \centering
+    \includegraphics[width=\textwidth]{horizon_distance_chirp_mass.pdf}
+    \caption{The horizon distance for circular stellar mass binaries in a four-year LISA mission.
+The filled contours indicate the horizon distance for different orbital frequencies and chirp masses.
+We add white dotted contours at $8, 50, 800 \unit{kpc}$ and $40 \unit{Mpc}$ to highlight the distances to the centre of the Milky Way, the Magellanic Clouds, the Andromeda galaxy and the nearest ground-based gravitational wave detection (GW170817, \citealp{Abbott+2017_GW170817}) respectively.
+The diagonal line black line shows the frequencies and chirp masses at which the merger time is equal to the observation time.
+This line emphasises the sharp contrast for the horizon distance for binaries that merge before the LISA mission finishes observing (to the right of the line).
+The horizontal black lines indicate the approximate location of some common double compact object types on this plot, with the assumed masses labelled below in solar masses.}
+    \label{fig:horizon_distance}
+\end{figure*}
+
+A common question to consider with stellar mass sources in LISA is how far away a certain source could be detected.
+In other words, what is the horizon distance beyond which a source no longer has a SNR greater than some chosen threshold.
+We can explore this question using \lw{}.
+
+Let us compute the horizon distance for a grid of chirp masses and orbital frequencies.
+First, we can recall that the signal-to-noise ratio of a source is inversely proportional to its distance from LISA and so we can find the horizon distance, $D_{\rm hor}$ as
+\begin{equation}{}
+    \label{eq:snr_to_hor_dist}
+    D_{\rm hor} = \frac{\rho(D)}{\rho_{\rm detect}} \cdot D,
+\end{equation}
+where $\rho(D)$ is the signal-to-noise ratio as some distance $D$ and $\rho_{\rm detect}$ is the threshold above which we consider a source to be detectable.
+For the purpose of this example we will set $\rho_{\rm detect} = 7$.
+Therefore, we can start by finding the signal-to-noise ratio for each source at an arbitrary distance and convert that to a horizon distance.
+
+This can be most efficiently accomplished using \lw{}'s source class.
+Although the source class only takes one-dimensional lists of sources, one can flatten a grid of chirp masses and orbital frequencies to make the input work.
+\lw{} can then compute the merger times and signal-to-noise ratio of each source with only two lines of code.
+These results can then be reshaped to match the original grid of chirp masses and frequencies.
+
+We convert these SNRs to horizon distances using Eq.~\ref{eq:snr_to_hor_dist} and plot the result in Figure~\ref{fig:horizon_distance}.
+The shape of the LISA sensitivity curve is clearly reflected in this plot of the horizon distance.
+This is because circular sources emit the vast majority of their single at a single frequency and thus every feature in the sensitivity curve has a strong effect on the SNR (and therefore horizon distance) for circular sources.
+We also see that once the merger time of a source is shorter than the LISA mission length (shown by the black dotted line), the horizon distance sharply decreases.
+This is because if a source merges before the LISA mission concludes, it has less time to accumulate signal and thus has a lower SNR and horizon distance.
+
+One can use Figure~\ref{fig:horizon_distance} to estimate the horizon distance for any circular source of interest.
+To illustrate this, we add solid black lines to indicate the typical chirp masses of some possible stellar mass gravitational wave sources as well as white dotted lines to show the distances to nearby galaxies as well as the nearest ground-based gravitational wave detection (GW170817, \citealp{Abbott+2017_GW170817}).
+For example, we see that a circular NSNS with an orbital frequency greater than a mHz is detectable in the Magellanic clouds.
+
+\subsection{The role of eccentricity\texorpdfstring{ - \tutorialLink{https://legwork.readthedocs.io/en/latest/demos/TheRoleofEccentricity.html} \notebookLink{https://github.com/TeamLEGWORK/LEGWORK/blob/main/docs/demos/TheRoleofEccentricity.ipynb}}{}}\label{sec:eccentricity_role}
+
+The role of eccentricity is an important concept to consider in the detection of gravitational waves with LISA as sources can still have significant eccentricity during their inspiral phase.
+A high eccentricity has two major effects on the SNR of a gravitational wave source in LISA and we can investigate this using \lw{}.
+
+Let's use three toy sources that are identical apart from their eccentricities, $e_i$.
+\begin{align*}{}
+    m_1 &= m_2 = 0.6 \unit{M_{\odot}}, f_{\rm orb} = 1.5 \unit{mHz}, d = 15 \unit{kpc}, \\
+    e_i &= \{0.0, 0.6, 0.9 \},
+\end{align*}
+Using \lw{} to calculate their signal-to-noise ratios, $\rho_i$, we find
+\begin{equation*}{}
+    \rho_i = \{ 31.7, 50.2, 38.8 \}
+\end{equation*}
+
+We see two effects in the signal-to-noise ratio here.
+First, increasing the eccentricity from essentially circular to $e = 0.6$ results in a higher signal-to-noise ratio ($\rho=31.7 \to \rho=50.2$).
+This is because an eccentric binary has enhanced energy emission via gravitational waves \citep{Peters+1963}.
+This means that an eccentric binary will not only inspiral faster than an otherwise identical circular binary, but also will always have a stronger gravitational wave strain.
+The enhancement factor and its exact dependence on eccentricity is discussed in more detail Section~\ref{sec:derivations} (specifically Eq.~\ref{eq:eccentricity_enhancement_factor}).
+
+The second effect is more intriguing.
+We see that increasing the eccentricity from $e = 0.6$ to $e = 0.9$ results in a relative \textit{decrease} in SNR ($\rho=50.2 \to \rho=38.8$).
+The reason for this is that eccentric binaries emit gravitational waves at many harmonic frequencies (unlike circular binaries, which emit predominantly twice the orbital frequency).
+This leads to the gravitational wave signal being diluted over many frequencies higher than the orbital frequency, where the higher the eccentricity, the more harmonics are required to capture all of the gravitational luminosity \citep[see][Fig.\,3]{Peters+1963}.
+Therefore, if the eccentricity is too high, the majority of the signal may be emitted at a frequency to which LISA is less sensitive.
+
+We can illustrate this point with \lw{} by calculating the SNR at each individual harmonic using the \lwModLink{snr} module.
+We plot this distribution of signal over different harmonics with the LISA sensitivity curve overlaid in Fig.~\ref{fig:ecc_effects} using \lw{}'s \lwModLink{visualisation} module.
+A point is plotted for each harmonic of each source that has an SNR greater than unity and such that its height above the sensitivity curve corresponds to its SNR.
+
+\begin{figure}[tb]
+    \centering
+    \includegraphics[width=\columnwidth]{role_eccentricity.pdf}
+    \caption{An illustration of the effect of eccentricity on the detectability of a LISA source.
+The three sets of points are coloured by their eccentricity and each individual point corresponds to a harmonic frequency, where its height above the curve gives its SNR.
+We annotate each set of points with its total SNR and overlay the LISA sensitivity curve.
+The dotted vertical lines indicate the frequency at which the majority of the gravitational wave signal is concentrated.}
+    \label{fig:ecc_effects}
+\end{figure}
+
+From Fig.~\ref{fig:ecc_effects}, we can better understand why a source with $e = 0.9$ has a lower SNR than the same source with $e = 0.6$.
+From the dotted lines, we can note that the signal from the $e = 0.9$ source is concentrated at a frequency of around $4 \times 10^{-2} \unit{Hz}$.
+The LISA sensitivity at this point is much weaker than the $6 \times 10^{-3} \unit{Hz}$ at which the $e =0.6$ source is concentrated.
+Therefore, although the strain from a more eccentric binary is stronger, the SNR is lower due to the increased noise in the LISA detector.
+
+Overall, we can therefore conclude that for LISA sources of this nature, higher eccentricity will produce more detectable binaries only if the orbital frequency is not already at or above the minimum of the LISA sensitivity curve.
+
+\begin{figure}[htb]
+    \centering
+    \includegraphics[width=\columnwidth]{merger_time_contours.pdf}
+    \caption{The merger time for a binary with both a primary and secondary mass of $10 \unit{M_{\odot}}$ over different eccentricities and orbital frequencies.}
+    \label{fig:merger_time}
+\end{figure}
+
+Another consideration for more massive binaries is whether the increased eccentricity will cause the binary to merge before the mission ends, which would cause a significant decrease in signal-to-noise ratio.
+We can also use \lw{} to find how the merger time of a source varies with frequency and eccentricity over a grid of sources.
+
+We plot the results of this calculation in Figure~\ref{fig:merger_time}.
+This plot shows that for most eccentricities the merger is time is largely determined by the orbital frequency.
+However, for high eccentricities ($e > 0.8$), the eccentricity significantly reduces the merger time.
+
+\subsection{Compare different gravitational wave detectors\texorpdfstring{ - \tutorialLink{https://legwork.readthedocs.io/en/latest/demos/CompareSensitivityCurves.html} \notebookLink{https://github.com/TeamLEGWORK/LEGWORK/blob/main/docs/demos/CompareSensitivityCurves.ipynb}}{}}
+
+It may also be useful to consider how changing the specifications of the LISA detector, or using a different detector entirely, could affect the SNR of a particular source.
+\lw{} is capable of adjusting the LISA mission specifications or using a different sensitivity curve and thus we can use it to explore these differences.
+
+As a first step, we can use \lw{} to plot a series of sensitivity curves in Figure~\ref{fig:detector_sc_compare}.
+We show the LISA sensitivity curve for the default 4 year mission length but also illustrate how the curve changes for shorter mission lengths.
+At 0.5 and 2 years, we see a stronger noise level around $3 \unit{mHz}$ as a result of the increased Galactic confusion noise.
+This noise decreases with increasing mission length since more individual foreground sources can be resolved and thus removed from the confusion noise.
+We also see that using an approximated response function smooths out the sensitivity curve at higher frequencies.
+Finally, the TianQin curve is higher than the 4 year LISA curve until around $5 \unit{mHz}$, beyond which it has a lower noise level.
+
+\begin{figure}[htb]
+    \centering
+    \includegraphics[width=\columnwidth]{detector_sc_compare.pdf}
+    \caption{The strain spectral density of the LISA detector (with different specifications) and the TianQin detector.
+We show the LISA curve for three different mission lengths and once with an approximate response function.}
+    \label{fig:detector_sc_compare}
+\end{figure}
+
+Although comparing the sensitivity curves would suffice for a stationary and circular source (since it would remain at a single frequency), \lw{} can also be used to see how the relative SNR between two detectors changes over a range of eccentricities and frequencies.
+
+Using \lw{}, we can compute the SNR of a grid of sources (spanning a range of frequencies and eccentricities) for both detectors.
+In Figure~\ref{fig:detector_snr_ratio}, we show the ratio of the SNR in LISA to the SNR in TianQin.
+This plot shows that for circular binaries, the SNR of the source in LISA is stronger up to an orbital frequency of approximately $2.5 \unit{mHz}$, beyond which the SNR of the source is stronger in TianQin.
+This transition frequency becomes lower with increasing eccentricity as one would expect since eccentric sources emit more at higher harmonics and thus higher frequencies.
+
+\begin{figure}[htb]
+    \centering
+    \includegraphics[width=\columnwidth]{detector_snr_ratio.pdf}
+    \caption{The ratio of the SNR in LISA (for a four year mission) to the SNR in TianQin.
+The dashed line indicates the transition at which the SNR is equal in both detectors.
+We annotate the regions in which either detector has a higher SNR and also annotate the mass and distance of each source in the grid.}
+    \label{fig:detector_snr_ratio}
+\end{figure}
+
+\subsection{Track SNR of a binary over time\texorpdfstring{ - \tutorialLink{https://legwork.readthedocs.io/en/latest/demos/SNROverTime.html} \notebookLink{https://github.com/TeamLEGWORK/LEGWORK/blob/main/docs/demos/SNROverTime.ipynb}}{}}
+
+As a binary inspirals its orbital frequency and eccentricity change and this in turn affects the SNR of the binary.
+For this use case we will demonstrate how \lw{} can be used to track the evolution of these parameters and pinpoint the moment at which a binary becomes detectable.
+
+Let's consider a binary with the following initial parameters
+\begin{align*}
+    m_1 &= m_2 = 15 \unit{M_{\odot}},\ d = 20 \unit{kpc},\\
+    f_{\rm orb, i} &= 3 \times 10^{-5} \unit{Hz},\ e_i = 0.5,
+\end{align*}
+and use \lw{} to evolve the system until 100 years before its merger with 1000 linearly spaced timesteps, recording the eccentricity and frequency at each timestep.
+
+We plot this evolution of the eccentricity and frequency in the top two panels of Fig.~\ref{fig:snr_over_time} as a function of the time before the merger.
+We see that the binary circularises and increases its orbital frequency as it inspirals as we would expect.
+
+To take this a step further, we can consider the binary at each timestep to be a separate source with the current eccentricity and frequency.
+It is then trivial to use \lw{} to calculate the SNR for each of these `sources' and thus attain the SNR evolution, which we plot in the last panel of Fig.~\ref{fig:snr_over_time}.
+
+We see that the SNR increases monotonically over time and sharply increases as the binary approaches its merger.
+Around $1 \unit{Myr}$ before the merger, the SNR reaches the detection threshold and thus could then be seen by a 4-year LISA mission.
+
+Note that \lw{} could also be used in this way to find the SNR of any system in which the orbital evolution is know.
+Thus for a triple system or a binary experiencing gas drag (as long the evolution of the eccentricity and orbital frequency is known) \lw{} is entirely capable of calculating the SNR evolution.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=\columnwidth]{snr_over_time.pdf}
+    \caption{The evolution of a binary system's eccentricity (top), orbital frequency (middle) and signal-to-noise ratio (bottom).
+Each panel is annotated with the constant parameters of the system.
+The SNR is calculated for a 4-year LISA mission.
+We annotate in  a line the bottom panel at $\mathrm{SNR} = 7$ to highlight the moment at which the source becomes detectable.}
+    \label{fig:snr_over_time}
+\end{figure}
+
+% \subsection{SNR calculation for verification binaries}
+
+%\section{Benchmarks}\label{sec:speed}
+%A section to show off \lw{}'s speed.
+
+\section{Derivations}\label{sec:derivations}
+In this section, we present a derivation of the equations using in \lw{}.
+We emphasise that these are not new derivations, conversely, they are in fact given frequently in the literature.
+However, they are often incomplete, unclear or contain spurious constant factors that arise from invalid combinations of previous work.
+Here, we aim to present a clear, clean and concise explanation of the expressions we use in \lw{}.
+
+A \docsIcon{} symbol in an equation will link to the relevant \lw{} documentation for the implementation of that equation.
+These derivations are also given in more detail in the \lw{} documentation \href{https://legwork.readthedocs.io/en/latest/notebooks/Derivations.html}{here}, where we show each of the intervening steps in more detail.
+
+\subsection{Conversions and definitions {\normalfont (\texorpdfstring{\lwModLink{utils}}{utils})}}\label{sec:deriv_utils}
+We start these derivations by defining some useful conversions and definitions. The chirp mass of a binary is the mass quantity measured by LISA and is given by
+\begin{equation}{\lwFuncURL{utils}{chirp_mass}}
+    \mathcal{M}_c \equiv \frac{(m_1 m_2)^{3/5}}{(m_1 + m_2)^{1/5}},
+    \label{eq:chirpmass}
+\end{equation}
+where $m_1$ and $m_2$ are the primary and secondary masses of the double compact object.
+
+It is often convenient to convert between orbital frequency, $f_{\rm orb}$, and the semi-major axis, $a$, of a binary and this can be accomplished with Kepler's third law.
+\begin{equation}{\lwFuncURL{utils}{get_a_from_f_orb}}
+    a = \qty(\frac{G(m_1 + m_2)}{(2 \pi f_{\rm orb})^{2}})^{1/3},
+    \label{eq:kepler3rd}
+\end{equation}
+or inversely
+\begin{equation}{\lwFuncURL{utils}{get_a_from_f_orb}}
+    f_{\rm orb} = \frac{1}{2 \pi} \sqrt{\frac{G(m_1 + m_2)}{a^3}}.
+    \label{eq:kepler3rd_reverse}
+\end{equation}
+
+For eccentric binaries, we need to consider all harmonics of gravitational wave emission. These are defined such that the $n^{\rm th}$ harmonic frequency is
+\begin{equation}{}
+    f_{n} \equiv n \cdot f_{\rm orb}.
+    \label{eq:nth_freq}
+\end{equation}
+It will be important to know the relative power radiated into the $n^{\rm th}$ harmonic for a binary with eccentricity $e$, which is given by \citep[][Eq.\,20]{Peters+1963}
+\begin{equation}{\lwFuncURL{utils}{peters_g}}
+    \begin{aligned}
+        g(n, e) = \frac{n^{4}}{32} & \Big\{ \Big[ J_{n-2}(n e)-2 e J_{n-1}(n e)+\frac{2}{n} J_{n}(n e) \\
+        &\left. +2 e J_{n+1}(n e)-J_{n+2}(n e)\Big]^{2}\right.\\
+        &\left.\kern-\nulldelimiterspace\right.
+            \!\!\begin{aligned}
+            +\big(1-e^{2}\big)\Big[&J_{n-2}(n e)-2 J_{n}(n e) \\
+            &+J_{n+2}(n e)\Big]^{2} \\
+            \end{aligned}\\
+        &+\frac{4}{3 n^{2}}\Big[J_{n}(n e)\Big]^{2}\Big\},
+    \end{aligned}
+    \label{eq:g(n,e)}
+\end{equation}
+where $J_{n}(v)$ is the Bessel function of the first kind.
+Thus, the \textit{sum} of $g(n, e)$ over all harmonics gives the factor by which the gravitational wave emission is stronger for a binary of eccentricity $e$ over an equivalent circular binary.
+This enhancement factor is \citep[][Eq.\,17]{Peters+1963}
+\begin{equation}{\lwFuncURL{utils}{peters_f}}
+    F(e) \equiv \sum_{n = 1}^{\infty} g(n, e) = \frac{1 + \frac{73}{24} e^2 + \frac{37}{96} e^4}{(1 - e^2)^{7/2}}.
+    \label{eq:eccentricity_enhancement_factor}
+\end{equation}
+A fun number to remember is that $F(0.5) \approx 5.0$, or in words, a binary with eccentricity $0.5$ loses energy to gravitational waves at 5 times the rate of an equivalent circular binary.
+
+\subsection{Orbital evolution {\normalfont (\texorpdfstring{\lwModLink{evol}}{evol})}}\label{sec:deriv_evol}
+\subsubsection{Circular binaries}
+For a circular binary, the evolution can be calculated analytically, as the rate at which the separation of the binary shrinks is simply a function of its mass and the current separation \citep[][Eq.~5.6]{Peters+1964}
+\begin{equation}{}
+    \dv{a}{t}_{e = 0} = -\frac{\beta}{a^3},
+\end{equation}
+where the constant $\beta$ is defined as
+\begin{equation}{\lwFuncURL{utils}{beta}}
+    \beta(m_1, m_2) = \frac{64}{5} \frac{G^3}{c^5} m_1 m_2 (m_1 + m_2),
+    \label{eq:beta_peters}
+\end{equation}
+where $m_1$ is the primary mass and $m_2$ is the secondary mass. This gives the semi-major axis of a circular binary as a function of time, $t$, as \citep[][Eq.~5.9]{Peters+1964}
+\begin{equation}{\lwFuncURL{evol}{evol_circ}}
+    a(t, m_1, m_2) = [a_0^4 - 4 t \beta(m_1, m_2)]^{1/4},
+    \label{eq:a_over_time_circ}
+\end{equation}
+where $a_0$ is the initial semi-major axis. Moreover, we can solve for the merger time, the time until the binary will merge, by setting the final semi-major axis in Eq.~\ref{eq:a_over_time_circ}
+\begin{equation}{\lwFuncURL{evol}{get_t_merge_circ}}
+    t_{\rm merge, circ} = \frac{a_0^4}{4 \beta}.
+    \label{eq:t_merge_circular}
+\end{equation}
+
+\subsubsection{Eccentric binaries}
+The orbital evolution is more complex for eccentric binaries since the semi-major axis and eccentricity both evolve simultaneously and depend on one another.
+These equations cannot be solved analytically and require numerical integration.
+The semi major axis, $a$, and eccentricity, $e$, are related as \citep[][Eq.~5.11]{Peters+1964}
+\begin{equation}{\lwFuncURL{utils}{get_a_from_ecc}}
+    a(e) = c_0 \frac{e^{12/19}}{(1 - e^2)} \left(1 + \frac{121}{304} e^2\right)^{870/2299},
+    \label{eq:a_from_e}
+\end{equation}
+where $c_0$ satisfies the initial conditions such that $a(e_0) = a_0$. The time derivative of the eccentricity, $e$, is given by
+\begin{equation}{\lwFuncURL{evol}{de_dt}}
+    \frac{\mathrm{d}e}{\mathrm{d}t} = -\frac{19}{12} \frac{\beta}{c_{0}^{4}} \frac{e^{-29 / 19}\left(1-e^{2}\right)^{3 / 2}}{\left[1+(121 / 304) e^{2}\right]^{\frac{1181}{2299}}},
+    \label{eq:dedt}
+\end{equation}
+which we can integrate to find $e(t)$ and convert to $a(t)$ using Eq.~\ref{eq:a_from_e} (\docsLink{\lwFuncURL{evol}{evol_ecc}}).
+
+Inverting this function and applying the fact that we know that $e \to 0$ when the binary merges gives the merger time \citep[][Eq.~5.14]{Peters+1964}
+\begin{equation}{\lwFuncURL{evol}{get_t_merge_ecc}}
+    t_{\rm merge} = \frac{12}{19} \frac{c_{0}^{4}}{\beta} \int_0^{e_0} \frac{\left[1+(121 / 304) e^{2}\right]^{\frac{1181}{2299}}}{e^{-29 / 19}\left(1-e^{2}\right)^{3 / 2}} \mathrm{d}e.
+    \label{eq:t_merge_eccentric}
+\end{equation}
+For very small or very large eccentricities we approximate this integral using the following expressions (given in unlabelled equations after \citealp[][Eq.~5.14]{Peters+1964})
+\begin{align}
+    t_{\rm merge,\, e^2 \ll 1} &= \frac{c_0^4}{4 \beta} \cdot e_0^{48 / 19}, \\
+    t_{\rm merge,\, (1 - e^2) \ll 1} &= \frac{768}{425} \frac{a_0^4}{4 \beta} (1 - e_0^2)^{7/2}.
+\end{align}
+
+\subsection{Strains {\normalfont (\texorpdfstring{\lwModLink{strain}}{strain})}}\label{sec:deriv_strain}
+The strength of a gravitational wave in a detector at any one moment is determined by the strain amplitude, $h_0$.
+However, for the LISA mission, the signal can be present in the detector for many years.
+This means that, the $n^{\rm th}$ harmonic of the binary will spend approximately $f_n / \dot{f}_n$ seconds (or $f_n^2 / \dot{f}_n$ cycles) in the vicinity of a frequency $f_n$ \citep{Finn+2000}.
+This leads to the signal `accumulating' at the frequency $f_n$.
+
+Therefore, to account for the integration of the signal over the mission, we can introduce the `characteristic' strain amplitude of the $n^{\rm th}$ harmonic \citep[e.g][]{Finn+2000, Moore+2015}\footnote{Note that this is factor of 2 different from \citet{Finn+2000}.
+This is because the factor of 2 is already included in the \citet{Robson+2019} sensitivity curve and so we remove it here.}
+\begin{equation}{}
+    h_{c, n}^2 = \qty(\frac{f_n^2}{\dot{f}_n}) h_{0, n}^2,
+    \label{eq:strain-charstrain}
+\end{equation}
+where $h_{0, n}$ is the strain amplitude in the $n^{\rm th}$ harmonic.
+
+The characteristic strain represents the strain measured by the detector over the duration of the mission (approximated as a single broad-band burst), whilst the strain amplitude is the strength of the GW emission at each instantaneous moment.
+
+\subsubsection{Characteristic Strain}
+
+The characteristic strain from a stellar mass binary in the $n^{\rm th}$ harmonic is given by (e.g. \citealp[][Eq.\,56]{Barack+2004}; \citealp[][Eq.\,5.1]{ Flanagan+1998})
+\begin{equation}{}
+    h_{c,n}^2 = \frac{1}{(\pi D_L)^2} \qty( \frac{2 G}{c^3} \frac{\dot{E_n}}{\dot{f_n}} ),
+    \label{eq:char_strain_dedf}
+\end{equation}
+where $D_L$ is the luminosity distance to the binary, $\dot{E}_n$ is the power radiated in the $n^{\rm th}$ harmonic and $\dot{f}_n$ is the rate of change of the $n^{\rm th}$ harmonic frequency.
+
+The power radiated in the $n^{\rm th}$ harmonic can be expressed as \citep[][Eq. 19]{Peters+1963}
+\begin{equation}{}
+    \dot{E}_n = \frac{32}{5} \frac{G^{4}}{c^5} \frac{m_{1}^{2} m_{2}^{2}\left(m_{1}+m_{2}\right)}{a^{5}} g(n, e),
+    \label{eq:edot_peters}
+\end{equation}
+where $g(n, e)$ is given in Eq.~\ref{eq:g(n,e)}.
+By substituting $a$ for $f_{\rm orb}$ (Eq.~\ref{eq:kepler3rd_reverse}) and applying the definition of the chirp mass (Eq.~\ref{eq:chirpmass}) we obtain a more useful form for making gravitational wave predictions
+\begin{equation}{}
+    \dot{E}_n(\mathcal{M}_c, f_{\rm orb}, e) = \frac{32}{5} \frac{G^{7 / 3}}{c^{5}}\left(2 \pi f_{\mathrm{orb}} \mathcal{M}_{c}\right)^{10 / 3} g(n, e). \label{eq:edot}
+\end{equation}
+The last term needed to define the characteristic strain in Eq.~\ref{eq:char_strain_dedf} is the rate of change of the $n^{\rm th}$ harmonic frequency as a result of gravitational wave inspiral, which we can write as
+\begin{equation}{}
+    \dot{f}_{n} = \dv{f_{n}}{a} \dv{a}{t}.
+    \label{eq:fdot_chainrule}
+\end{equation}
+We can find an expression for $\dd{f_{n}} / \dd{a}$ by substituting Eq.~\ref{eq:kepler3rd_reverse} into Eq.~\ref{eq:nth_freq} and differentiating 
+\begin{equation}{}
+    \dv{f_{n}}{a} = -\frac{3 n}{4 \pi} \frac{\sqrt{G(m_1 + m_2)}}{a^{5/2}}.
+    \label{eq:dfda}
+\end{equation}
+The rate at which the semi-major axis decreases is \citep[][Eq. 5.6]{Peters+1964}
+\begin{equation}{}
+    \dv{a}{t} = -\frac{64}{5} \frac{G^{3} m_{1} m_{2}\left(m_{1}+m_{2}\right)}{c^{5} a^{3}} F(e).
+    \label{eq:dadt}
+\end{equation}
+Substituting Eq.~\ref{eq:dfda} and Eq.~\ref{eq:dadt} into Eq.~\ref{eq:fdot_chainrule} gives an expression for $\dot{f}_{n}$
+\begin{equation}{}
+    \dot{f}_n = \frac{48 n}{5 \pi} \frac{G^{7/2}}{c^5} \qty(m_1 m_2 (m_1 + m_2)^{3/2}) \frac{F(e)}{a^{11/2}},
+\end{equation}
+which, as above with $\dot{E}_n$, we can recast using Kepler's third law and the definition of the chirp mass
+\begin{equation}{\lwFuncURL{utils}{fn_dot}}
+    \dot{f}_n = \frac{48 n}{5 \pi} \frac{\qty(G \mathcal{M}_c)^{5/3}}{c^5} (2 \pi f_{\rm orb})^{11/3} F(e).
+    \label{eq:fdot}
+\end{equation}
+With definitions of both $\dot{E}_n$ and $\dot{f}_n$, we are now in a position to find an expression for the characteristic strain by plugging Eq.~\ref{eq:edot} and Eq.~\ref{eq:fdot} into Eq.~\ref{eq:char_strain}:
+\begin{equation}{\lwFuncURL{strain}{h_c_n}}
+    h_{c,n}^2 = \frac{2^{5/3}}{3 \pi^{4/3}} \frac{(G \mathcal{M}_c)^{5/3}}{c^3 D_L^2} \frac{1}{f_{\rm orb}^{1/3}} \frac{g(n, e)}{n F(e)}. \label{eq:char_strain}
+\end{equation}
+
+\subsubsection{Strain}
+In order to get an expression for the strain amplitude of gravitational waves in the $n^{\rm th}$ harmonic, we can use Eq.~\ref{eq:strain-charstrain} and plug in Eq.~\ref{eq:fdot} and Eq.~\ref{eq:char_strain}
+\begin{equation}{\lwFuncURL{strain}{h_0_n}}
+    h_n^2 = \frac{2^{28/3}}{5} \frac{(G \mathcal{M}_c)^{10/3}}{c^8 D_L^2} \frac{g(n, e)}{n^2} \qty(\pi f_{\rm orb})^{4/3} . 
+    \label{eq:strain}
+\end{equation}
+
+\subsection{Sensitivity Curves {\normalfont (\texorpdfstring{\lwModLink{psd}}{psd})}}\label{sec:deriv_psd}
+
+\subsubsection{LISA}
+For the LISA sensitivity curve we use the equations from \citet{Robson+2019}. The \textit{effective} strain spectral density of the noise is defined as
+\begin{equation}{\lwFuncURL{psd}{lisa_psd}}
+    S_{\rm n}(f) \equiv \frac{P_n(f)}{\mathcal{R}(f)} + S_c(f),
+\end{equation}
+where $P_{\rm n}(f)$ is the power spectral density of the detector noise and $\mathcal{R}(f)$ is the sky and polarisation averaged signal response function of the instrument.
+Alternatively if we expand out $P_n(f)$, approximate $\mathcal{R}(f)$ and simplify we find \citep[][Eq.~1]{Robson+2019}
+\begin{equation}{}
+    \begin{split}
+        S_{\rm n}(f) &= \frac{10}{3 L^2} \qty(P_{\rm OMS}(f) + \frac{4 P_{\rm acc}(f)}{(2 \pi f)^4}) \\
+        &\times \qty(1 + \frac{6}{10} \qty(\frac{f}{f_*}^2)) + S_c(f),
+    \end{split}
+    \label{eq:LISA_Sn}
+\end{equation}
+where $L = 2.5 \unit{Gm}$ is detector arm length, $f^* = c / 2 \pi L = 19.09 \unit{mHz}$ is the transfer frequency, 
+\begin{equation}{}
+    \begin{split}
+        P_{\rm OMS}(f) &= \left(1.5 \times 10^{-11} \mathrm{m}\right)^{2} \\
+        &\times \left(1+\left(\frac{2 \mathrm{mHz}}{f}\right)^{4}\right) \mathrm{Hz}^{-1},
+    \end{split}
+\end{equation}
+is the single-link optical metrology noise \citep[][Eq.~10]{Robson+2019},
+\begin{equation}{}
+    \begin{split}
+        P_{\rm acc}(f) &= \left(3 \times 10^{-15} \mathrm{ms}^{-2}\right)^{2}\left(1+\left[\frac{0.4 \mathrm{mHz}}{f}\right]^{2}\right)\\
+        &\times \left(1+\left[\frac{f}{8 \mathrm{mHz}}\right]^{4}\right) \mathrm{Hz}^{-1},
+    \end{split}
+\end{equation}
+is the single test mass acceleration noise \citep[][Eq.~11]{Robson+2019} and
+\begin{equation}{}
+    \begin{split}
+        S_{c}(f)&=A f^{-7 / 3} e^{-f^{\alpha}+\beta f \sin (\kappa f)} \\
+        &\times \left[1+\tanh \left(\gamma\left(f_{k}-f\right)\right)\right] \mathrm{Hz}^{-1},
+    \end{split}
+\end{equation}
+is the galactic confusion noise \citep[][Eq.~14]{Robson+2019}, where the amplitude $A$ is fixed as $9 \times 10^{-45}$ and the various parameters change over time:
+$$
+    \begin{array}{|c|c|c|c|c|}
+        \hline
+        & 6 \mathrm{mo} & 1 \mathrm{yr} & 2 \mathrm{yr} & 4 \mathrm{yr} \\
+        \hline
+        \alpha & 0.133 & 0.171 & 0.165 & 0.138 \\
+        \beta & 243 & 292 & 299 & -221 \\
+        \kappa & 482 & 1020 & 611 & 521 \\
+        \gamma & 917 & 1680 & 1340 & 1680 \\
+        f_{k} & 0.00258 & 0.00215 & 0.00173 & 0.00113 \\
+        \hline
+    \end{array}
+$$
+
+\subsubsection{TianQin}
+For the TianQin sensitivity curve we use the power spectral density given in \citet[][Eq.~13]{Huang+2020}
+\begin{equation}{}
+    \begin{split}
+    S_{N}(f) &= \frac{1}{L^{2}}\left[\frac{4 S_{a}}{(2 \pi f)^{4}}\left(1+\frac{10^{-4} \unit{Hz}}{f}\right)+S_{x}\right] \\
+    & \times\left[1+0.6\left(\frac{f}{f_{*}}\right)^{2}\right],
+    \end{split}
+\label{eq:tianqin}
+\end{equation}
+where $L = \sqrt{3} \times 10^5 \unit{km}$ is the arm length, $S_a = 1 \times 10^{-30} \unit{m^2}{s^{-4}}{Hz^{-1}}$ is the acceleration noise, $S_x = 1 \times 10^{-24} \unit{m^2}{Hz^{-1}}$ is the displacement measurement noise and $f_* = c / 2 \pi L$ is the transfer frequency.
+
+\subsection{SNR for 6-link LISA {\normalfont (\texorpdfstring{\lwModLink{snr}}{snr})}}\label{sec:deriv_snr}
+
+Please note that this section draws heavily from \citet{Flanagan+1998} Section II C.
+
+\subsubsection{Defining general SNR}
+In order to calculate the signal to noise ratio for a given source of gravitational waves (GWs) in the LISA detector, we need to consider the following parameters:
+
+\begin{itemize}
+    \item position of the source on the sky: ($\theta$, $\phi$)
+    \item direction from the source to the detector: ($\iota$, $\beta$)
+    \item orientation of the source, which fixes the polarisation of the GW: $\psi$
+    \item the distance from the source to the detector: $D_L$
+\end{itemize}
+
+Then, assuming a matched filter analysis of the GW signal $s(t) + n(t)$ (where $s(t)$ is the signal and $n(t)$ is the noise), which relies on knowing the shape of the signal, the signal to noise ratio, $\rho$, is given in the frequency domain as
+
+\begin{align}{}
+\label{eq:snr_general_start}
+    \rho^2(D_L, \theta, \phi, \psi, \iota, \beta) &= \frac{\langle s(t)^{\star}s(t)\rangle}{\langle n(t)^{\star}n(t)\rangle}, \\
+    &= 2 \int_{-\infty}^{+\infty} \frac{|\tilde{s}(f)|^2}{P_{\rm n}(f)} df, \\
+    &= 4 \int_0^{\infty} \frac{|\tilde{s}(f)|^2}{P_{\rm n}(f)} df,
+\end{align}
+where $\tilde{s}(f)$ is the Fourier transform of the signal, $s(t)$, and $P_{\rm n}(f)$ is the one sided power spectral density of the noise defined as as $\langle n(t)^{\star}n(t)\rangle = \int_0^{\infty} \frac{1}{2}P_{\rm n}(f) df$ \citep[c.f.][Eq.\,2]{Robson+2019}.
+Here, $\tilde{s}(f)$ is implicitly also dependent on $D_L, \theta, \phi, \psi, \iota,$ and $\beta$ as
+
+\begin{equation}{}
+\label{eq:signal}
+    \begin{split}
+        |\tilde{s}(f)|^2 = |&F_+(\theta, \phi, \psi)\tilde{h}_+(t, D_L, \iota, \beta) \\
+        &+ F_{\times}(\theta, \phi, \psi)\tilde{h}_{\times}(t, D_L, \iota, \beta)|^2,
+    \end{split}
+\end{equation}
+where $F_{+,\times}$ are the `plus' and `cross' antenna patterns of the LISA detector to the `plus' and `cross' strains, $h_{+,\times}$.
+Note throughout any parameters discussed with the subscript $x_{+,\times}$ refers to both $x_{+}$ and $x_{\times}$.
+
+In LISA's case, when averaged over all angles and polarisations, the antenna patterns are orthogonal thus $\langle F_+ F_{\times}\rangle = 0$. This means we can rewrite Eq.~\ref{eq:signal} as 
+\begin{equation}{}
+    \begin{split}
+        |\tilde{s}(f)|^2 &= |F_+(\theta, \phi, \psi)\tilde{h}_+(t, D_L, \iota, \beta)|^2\\
+        &+ |F_{\times}(\theta, \phi, \psi)\tilde{h}_{\times}(t, D_L, \iota, \beta)|^2,
+    \end{split}
+\end{equation} 
+which can then be applied to Eq.~\ref{eq:snr_general_start} as
+\begin{equation}{}
+\label{eq:snr_general_simpler}
+    \rho^2 = 4 \int_0^{\infty} \frac{|F_+\tilde{h}_+|^2 + |F_{\times}\tilde{h}_{\times}|^2}{P_{\rm n}(f)} df.
+\end{equation}
+
+\subsubsection{Average over position and polarisation}
+Now, we can consider averaging over different quantities. In particular, we can average over the sky position and polarisation as
+
+\begin{equation}{}
+\label{eq:position_orientation_ave}
+    \langle \rho \rangle^2_{\theta,\phi,\psi} = 4 \int_0^{\infty} df \int \frac{d\Omega_{\theta,\phi}}{4\pi} \int \frac{d\psi}{\pi} \frac{|F_+\,\tilde{h}_+|^2 + |F_{\times}\,\tilde{h}_{\times}|^2}{P_{\rm n}(f)}.
+\end{equation}
+From \cite{Robson+2019}, we can write the position and polarisation average of the signal response function of the instrument, $\mathcal{R}$, as
+
+\begin{equation}{}
+\label{eq:response}
+    \begin{split}
+        \mathcal{R} &= \langle F_+F^{\star}_+ \rangle = \langle F_{\times}F^{\star}_{\times} \rangle,\\
+    \rm{where}\,\,
+   \langle F_{+,\times}F^{\star}_{+,\times} \rangle &= \int \frac{d\Omega_{\theta,\phi}}{4 \pi} \int \frac{d\psi}{\pi} |F_{+,\times}|^2.
+    \end{split}
+\end{equation}
+Then combining Eq.~\ref{eq:position_orientation_ave} and Eq.~\ref{eq:response}, we then find\footnote{Note that this is written in \cite{Flanagan+1998} for the LIGO response function which is $\mathcal{R} = \langle F_{+,\times} \rangle ^2 = 1/5$.}
+
+\begin{equation}{}
+\label{eq:averaged_antenna_simp}
+    \langle \rho \rangle^2_{\theta,\phi,\psi} = 4 \int_0^{\infty} df \mathcal{R}(f)\, \left(\frac{|\tilde{h}_+|^2 + |\tilde{h}_{\times}|^2}{P_{\rm n}(f)}\right).
+\end{equation}
+
+\subsubsection{Average over orientation}
+Now, we can average over the orientation of the source: $(\iota, \beta)$, noting that the averaging is independent of the distance $D_L$.
+With this in mind, we can rewrite $|\tilde{h}_+|^2 + |\tilde{h}_{\times}|^2$ in terms of two functions $|\tilde{H}_+|^2$  and  $|\tilde{H}_{\times}|^2$, where $\tilde{h}_{+,\times} = \tilde{H}_{+,\times}/D_L$.
+Given this, averaging over the source direction gives
+\begin{equation}{}
+\label{eq:averaged_all}
+    \langle \rho \rangle^2_{(\theta,\phi,\psi),(\iota,\beta)} = \frac{4}{D_L^2} \int_0^{\infty} df \mathcal{R}(f)\,\int \frac{d\Omega_{\iota,\beta}}{4 \pi} \frac{|\tilde{H}_+|^2 + |\tilde{H}_{\times}|^2}{P_{\rm n}(f)},
+\end{equation}
+where we would like to express $\tilde{H}_{+,\times}(f)^2$ in terms of the energy spectrum of the GW.
+To do this, we note that the local energy flux of GWs at the detector is given by \citep[e.g.][Eq.\,6]{Press+1972}
+
+\begin{equation}{}
+\label{eq:energy_flx}
+    \frac{dE}{dAdt} = \frac{1}{16\pi} \overline{\left[\left(\frac{dh_{+}}{dt}\right)^2 + \left(\frac{dh_{\times}}{dt}\right)^2\right]},
+\end{equation}
+where the bar indicates an average over several cycles of the wave which is appropriate for LISA sources. We can transform Eq.~\ref{eq:energy_flx} using Parseval's theorem, where we can write
+
+\begin{align}
+    \int_{-\infty}^{+\infty}dt\int dA \frac{dE}{dAdt} &= \int_{0}^{\infty}df \int dA \frac{\pi f^2}{2} \left(|\tilde{h}_{+}|^2 + |\tilde{h}_{\times}|^2 \right).
+\label{eq:Parseval}
+\end{align}
+Note that the factor of frequency squared comes from the Fourier transform of the square of the time derivative in Eq.~\ref{eq:Parseval}.
+Now, since $A = D_L^2 \Omega$ and $|\tilde{h}_{+,\times}|^2 = |\tilde{H}_{+,\times}|^2 / D_L^2$, we know
+\begin{equation}{}
+\label{eq:little_h_to_big}
+    |\tilde{h}_{+,\times}|^2 dA = |\tilde{H}_{+,\times}|^2 d\Omega_{\iota,\beta},
+\end{equation}
+then we can write Eq.~\ref{eq:Parseval} in terms of $|H_{+,\times}|^2$ as 
+\begin{equation}{}
+    \int_{-\infty}^{+\infty}dt\int dA \frac{dE}{dAdt} = \int_{0}^{\infty}df \frac{\pi f^2}{2} \int d\Omega \left(|\tilde{H}_{+}|^2 + |\tilde{H}_{\times}|^2 \right).
+\label{eq:Parseval_2}
+\end{equation}
+Alternatively, by using Eq.~\ref{eq:little_h_to_big} and performing a Fourier transform we also have that
+\begin{equation}{}
+    \int_{-\infty}^{+\infty}dt\int dA \frac{dE}{dAdt} = \int_{0}^{\infty}df \int d\Omega \frac{dE}{d\Omega df}.
+    \label{eq:deriv_relation}
+\end{equation}
+From inspection of Eq.~\ref{eq:Parseval_2} and Eq.~\ref{eq:deriv_relation}, we can write the spectral energy flux as
+\begin{equation}{}
+    \int d\Omega \frac{dE}{d\Omega df} = \frac{\pi f^2}{2} \int d\Omega \left(|\tilde{H}_{+}|^2 + |\tilde{H}_{\times}|^2 \right) .
+    \label{eq:se_flux}
+\end{equation}
+
+\subsubsection{Fulled averaged SNR}
+We are now in a position to write an expression for the fully averaged SNR.
+Note for brevity we write $\langle \rho \rangle^2$ when referring to $\langle \rho \rangle^2_{(\theta,\phi,\psi),(\iota,\beta)}$.
+The application of Eq.~\ref{eq:se_flux} to Eq.~\ref{eq:averaged_all} yields
+\begin{equation}{}
+    \langle \rho \rangle^2 = \frac{4}{D_L^2} \int_0^{\infty} df \frac{1}{P_{\rm n}(f)/\mathcal{R}(f)} \int \frac{d\Omega}{4\pi} \frac{dE}{d\Omega df} \frac{2}{\pi f^2}.
+\end{equation}
+This simplifies nicely to 
+\begin{equation}{}
+    \langle \rho \rangle^2 = \frac{2}{\pi^2 D_L^2}\int_0^{\infty}df \frac{dE}{df}\frac{1}{f^2 P_{\rm n}(f)/\mathcal{R}(f)}.
+\end{equation}
+Finally, noting that $dE/df = dE/dt \times dt/df = \dot{E}/\dot{f}$, we can use the definition of the characteristic strain from Eq.~\ref{eq:char_strain_dedf} (and use $c=G=1$),
+\begin{equation}{}
+    h_{c}^2 = \frac{1}{\pi^2 D_L^2} \left(\frac{2\dot{E}}{\dot{f}}\right),
+\end{equation}
+to finish up our position, direction, and orientation/polarisation averaged SNR as
+\begin{equation}{}
+   \langle \rho \rangle^2 = \int_0^{\infty}df \frac{h_{c}^2}{f^2P_{\rm n}(f)/\mathcal{R}(f)} = \int_0^{\infty}df \frac{h_{c}^2}{f^2 S_{\rm n}(f)},
+   \label{eq:snr_finished_circ}
+\end{equation}
+where we have used that the effective power spectral density of the noise is defined as $S_{\rm n}(f) = P_{\rm n}(f) / \mathcal{R}(f)$.
+
+It is also important to note that this is only the SNR for a circular binary for which we need only consider the $n = 2$ harmonic.
+In the general case, a binary could be eccentric and requires a sum over \textit{all} harmonics.
+Thus we can generalise Eq.~\ref{eq:snr_finished_circ} to eccentric binaries with
+\begin{equation}{\lwFuncURL{snr}{snr_ecc_evolving}}
+    \langle \rho \rangle^2 = \sum_{n = 1}^{\infty} \langle \rho_n \rangle^2 = \sum_{n = 1}^{\infty} \int_0^{\infty} d f_n \frac{h_{c, n}^2}{f_n^2 S_{\rm n}(f_n)},
+   \label{eq:snr_general}
+\end{equation}
+where $h_{c, n}$ is defined in Eq.~\ref{eq:char_strain} and $S_{\rm n}$ in Eq.~\ref{eq:LISA_Sn}.
+
+\subsubsection{SNR Approximations}
+Although Eq.~\ref{eq:snr_general} can be used for every binary, it can be useful to consider different cases in which we can avoid unnecessary sums and integrals.
+There are four possible cases for binaries in which we can use increasingly simple expressions for the signal-to-noise ratio. Binaries can be circular and stationary in frequency space.
+
+Circular binaries emit only in the $n=2$ harmonic and so the sum over harmonics can be removed.
+Stationary binaries have $f_{n, i} \approx f_{n, f}$ and so the small interval allows one to approximate the integral.
+Note we refer to non-stationary binaries as `evolving' here though many papers also use `chirping'.
+
+For an evolving and eccentric binary, no approximate can be made and the SNR is found using Eq.~\ref{eq:snr_general}.
+
+For a evolving and circular binary, the sum can be removed and so the SNR found as
+\begin{equation}{\lwFuncURL{snr}{snr_circ_evolving}}
+    \rho^2_{\rm c, e} = \frac{1}{4} \int_{f_{2, i}}^{f_{2, f}} \frac{h_{c, 2}^2}{f_2^2 S_{\rm n}(f_2)} \dd{f_2}. \label{eq:snr_chirp_circ}
+\end{equation}
+
+For a stationary and eccentric binary we can approximate the integral.
+\begin{align}
+    \rho^2_{\rm e, s} &= \frac{1}{4} \sum_{n=1}^{\infty}  \lim_{\Delta f \to 0} \int_{f_{n}}^{f_{n} + \Delta f_n} \frac{h_{c, n}^2}{f_n^2 S_{\rm n}(f_n)} \dd{f_n}, \\
+    &= \frac{1}{4} \sum_{n=1}^{\infty} \frac{\Delta f_n \cdot h_{c, n}^2}{f_n^2 S_{\rm n}(f_n)}, \\
+    &= \frac{1}{4} \sum_{n=1}^{\infty} \frac{\dot{f}_n \Delta T \cdot h_{c, n}^2}{f_n^2 S_{\rm n}(f_n)}, \\
+    &= \frac{1}{4} \sum_{n=1}^{\infty} \qty(\frac{\dot{f}_n}{f_n^2} h_{c, n}^2) \frac{T_{\rm obs}}{S_{\rm n}(f_n)},
+\end{align}
+where we have applied \eqref{eq:strain-charstrain} to convert between strains. This gives the following expression
+\begin{equation}{\lwFuncURL{snr}{snr_ecc_stationary}}
+    \rho^2_{\rm e, s} = \frac{1}{4} \sum_{n=1}^{\infty} \frac{h_{n}^2 T_{\rm obs}}{S_{\rm n}(f_n)}. \label{eq:snr_stat_ecc}
+\end{equation}
+Finally, for a stationary and circular binary the signal-to-noise ratio is
+\begin{equation}{\lwFuncURL{snr}{snr_circ_stationary}}
+    \rho^2_{\rm c, s} = \frac{1}{4} \frac{h_2^2 T_{\rm obs}}{S_{\rm n}(f_2)}.
+    \label{eq:snr_stat_circ}
+\end{equation}
+
+\section{Conclusion \& Summary}\label{sec:summary}
+
+\todo{}
+
+\software{\lw{} is written in \texttt{Python}, available from \url{python.org}.
+We make use of the following Python packages: \texttt{matplotlib} \citep{Hunter+2007}, \texttt{NumPy} \citep{2020NumPy-Array},
+\texttt{Astropy} \citep[\url{http://www.astropy.org}][]{AstropyCollaboration+2013,AstropyCollaboration+2018}, \texttt{Seaborn} \citep{Waskom+2021}, \texttt{SciPy} \citep{2020SciPy-NMeth}, \texttt{Numba} \citep{numba} and \texttt{Schwimmbad} \citep{Price-Whelan+2017}.}
+
+\acknowledgments{
+% People
+We are grateful to Valeria Korol, Tyson Littenberg, Alberto Sesana, Ilya Mandel, Mike Lau, Lieke van Son, Floor Broekgaarden, Stephen Justham, Will Farr, the CCA GW group, the BinCosmos group and the COMPAS group for stimulating discussions that influenced and motivated us to complete this project.
+We thank the BinCosmos group for testing an early version of the package and providing useful feedback.
+We also thank Lieke van Son for her innovation in inventing a name for \lw{}!
+
+% Grants
+This project was funded in part by the National Science Foundation under Grant No.\ (NSF grant number 2009131), the European Union’s Horizon 2020 research and innovation program from the European Research Council (ERC, Grant agreement No.\ 715063), and by the Netherlands Organization for Scientific Research (NWO) as part of the Vidi research program BinWaves with project number 639.042.728.
+We further acknowledge the Black Hole Initiative funded by a generous contribution of the John Templeton Foundation and the Gordon and Betty Moore Foundation.}
+
+\bibliography{references}
+\bibliographystyle{aasjournal}
 

### 2021-11-02 src/ms.tex
bunch of fixes for aastex631 and figure names

@@
-\documentclass[twocolumn]{aastex63}
+\documentclass[twocolumn]{aastex631}
 \received{\today}
@@
 \usepackage{etoolbox}
-\usepackage{fontawesome5}
+\usepackage{fontawesome}
 
@@
 
+% define colour from xcolor
+\definecolor{SeaGreen}{RGB}{63, 188, 157}
+
 % LEGWORK stuff
@@
 % icons and links
-\newcommand{\docsIcon}{{\color{\lwColour}{\faFileCode}}}
+\newcommand{\docsIcon}{{\color{\lwColour}{\faBook}}}
 \newcommand{\docsLink}[1]{\href{#1}{\docsIcon}}
 
-\newcommand{\tutorialIcon}{{\color{\lwColour}{\faLaptopCode}}}
+\newcommand{\tutorialIcon}{{\color{\lwColour}{\faBook}}}
 \newcommand{\tutorialLink}[1]{\href{#1}{\tutorialIcon}}
@@
     \centering
-    \includegraphics[width=\columnwidth]{package_overview_witharrows.png}
+    \includegraphics[width=\columnwidth]{static/package_overview.png}
     \caption{Package structure of \lw{}. Each box represents a module and describes its function. The arrows indicate the inter-dependencies of the modules.}
@@
     \centering
-    \includegraphics[width=\textwidth]{horizon_distance_chirp_mass.pdf}
+    \includegraphics[width=\textwidth]{figures/horizon_distance.pdf}
     \caption{The horizon distance for circular stellar mass binaries in a four-year LISA mission.
@@
 We can illustrate this point with \lw{} by calculating the SNR at each individual harmonic using the \lwModLink{snr} module.
-We plot this distribution of signal over different harmonics with the LISA sensitivity curve overlaid in Fig.~\ref{fig:ecc_effects} using \lw{}'s \lwModLink{visualisation} module.
+We plot this distribution of signal over different harmonics with the LISA sensitivity curve overlaid in Fig.~\ref{fig:role_eccentricity} using \lw{}'s \lwModLink{visualisation} module.
 A point is plotted for each harmonic of each source that has an SNR greater than unity and such that its height above the sensitivity curve corresponds to its SNR.
@@
     \centering
-    \includegraphics[width=\columnwidth]{role_eccentricity.pdf}
+    \includegraphics[width=\columnwidth]{figures/role_eccentricity.pdf}
     \caption{An illustration of the effect of eccentricity on the detectability of a LISA source.
@@
 The dotted vertical lines indicate the frequency at which the majority of the gravitational wave signal is concentrated.}
-    \label{fig:ecc_effects}
+    \label{fig:role_eccentricity}
 \end{figure}
 
-From Fig.~\ref{fig:ecc_effects}, we can better understand why a source with $e = 0.9$ has a lower SNR than the same source with $e = 0.6$.
+From Fig.~\ref{fig:role_eccentricity}, we can better understand why a source with $e = 0.9$ has a lower SNR than the same source with $e = 0.6$.
 From the dotted lines, we can note that the signal from the $e = 0.9$ source is concentrated at a frequency of around $4 \times 10^{-2} \unit{Hz}$.
@@
     \centering
-    \includegraphics[width=\columnwidth]{merger_time_contours.pdf}
+    \includegraphics[width=\columnwidth]{figures/merger_time.pdf}
     \caption{The merger time for a binary with both a primary and secondary mass of $10 \unit{M_{\odot}}$ over different eccentricities and orbital frequencies.}
@@
     \centering
-    \includegraphics[width=\columnwidth]{detector_sc_compare.pdf}
+    \includegraphics[width=\columnwidth]{figures/detector_sc_compare.pdf}
     \caption{The strain spectral density of the LISA detector (with different specifications) and the TianQin detector.
@@
     \centering
-    \includegraphics[width=\columnwidth]{detector_snr_ratio.pdf}
+    \includegraphics[width=\columnwidth]{figures/detector_snr_ratio.pdf}
     \caption{The ratio of the SNR in LISA (for a four year mission) to the SNR in TianQin.
@@
     \centering
-    \includegraphics[width=\columnwidth]{snr_over_time.pdf}
+    \includegraphics[width=\columnwidth]{figures/snr_over_time.pdf}
     \caption{The evolution of a binary system's eccentricity (top), orbital frequency (middle) and signal-to-noise ratio (bottom).
@@
 
-\acknowledgments{
+\begin{acknowledgements}
     % People
@@
     This project was funded in part by the National Science Foundation under Grant No.\ (NSF grant number 2009131), the European Union’s Horizon 2020 research and innovation program from the European Research Council (ERC, Grant agreement No.\ 715063), and by the Netherlands Organization for Scientific Research (NWO) as part of the Vidi research program BinWaves with project number 639.042.728.
-We further acknowledge the Black Hole Initiative funded by a generous contribution of the John Templeton Foundation and the Gordon and Betty Moore Foundation.}
+We further acknowledge the Black Hole Initiative funded by a generous contribution of the John Templeton Foundation and the Gordon and Betty Moore Foundation.
+\end{acknowledgements}
 

### 2021-11-02 src/ms.tex
comment out breaking figure for now

@@
 
-Using \lw{}, we can compute the SNR of a grid of sources (spanning a range of frequencies and eccentricities) for both detectors.
+% Using \lw{}, we can compute the SNR of a grid of sources (spanning a range of frequencies and eccentricities) for both detectors.
 In Figure~\ref{fig:detector_snr_ratio}, we show the ratio of the SNR in LISA to the SNR in TianQin.
@@
 
-\begin{figure}[htb]
-    \centering
-    \includegraphics[width=\columnwidth]{figures/detector_snr_ratio.pdf}
-    \caption{The ratio of the SNR in LISA (for a four year mission) to the SNR in TianQin.
+% \begin{figure}[htb]
+%     \centering
+%     \includegraphics[width=\columnwidth]{figures/detector_snr_ratio.pdf}
+%     \caption{The ratio of the SNR in LISA (for a four year mission) to the SNR in TianQin.
 The dashed line indicates the transition at which the SNR is equal in both detectors.
 We annotate the regions in which either detector has a higher SNR and also annotate the mass and distance of each source in the grid.}
-    \label{fig:detector_snr_ratio}
-\end{figure}
+%     \label{fig:detector_snr_ratio}
+% \end{figure}
 

### 2021-11-02 src/figures/merger_time.py
change file save name

@@ -50,4 +50,4 @@ ax.annotate(mass_string, xy=(0.5, 0.04), xycoords="axes fraction", fontsize=0.6*
 ax.set_xlabel(r"Orbital frequency, $f_{\rm orb} \, [\rm Hz]$")
 ax.set_ylabel(r"Eccentricity, $e$")
 
-plt.savefig("merger_time_contours.pdf", format="pdf", bbox_inches="tight")
+plt.savefig("merger_time.pdf", format="pdf", bbox_inches="tight")

### 2021-11-02 src/figures/snr_over_time.py
forgot the default are different for this script

@@ -10,9 +10,9 @@ fs = 24
 # update various fontsizes to match
 params = {'figure.figsize': (12, 8),
           'legend.fontsize': fs,
-          'axes.labelsize': fs,
-          'xtick.labelsize': 0.9 * fs,
-          'ytick.labelsize': 0.9 * fs,
+          'axes.labelsize': 0.7 * fs,
+          'xtick.labelsize': 0.6 * fs,
+          'ytick.labelsize': 0.6 * fs,
           'axes.linewidth': 1.1,
           'xtick.major.size': 7,
           'xtick.minor.size': 4,

### 2021-11-02 src/figures/detector_snr_ratio.py
forgot mission length in params

@@ -44,7 +44,7 @@ sources.get_merger_time()
 LISA_snr = sources.get_snr(verbose=True, which_sources=sources.t_merge > 0.1 * u.yr)
 
 # compute the TianQin SNR
-sources.update_sc_params({"instrument": "TianQin", "L": None})
+sources.update_sc_params({"instrument": "TianQin", "t_obs": 4 * u.yr, "L": None})
 TQ_snr = sources.get_snr(instrument="TianQin", verbose=True, which_sources=sources.t_merge > 0.1 * u.yr)
 
 # create a figure

### 2021-11-02 src/ms.tex
change bib file name
uncomment the last figure
change back to fontawesome5 icons
remove links to jupyter notebooks

--- 2021-11-02 src/ms.tex
@@
 \usepackage{etoolbox}
-\usepackage{fontawesome}
 
@@
 % icons and links
-\newcommand{\docsIcon}{{\color{\lwColour}{\faBook}}}
+\newcommand{\docsIcon}{{\color{\lwColour}{\faFileCode}}}
 \newcommand{\docsLink}[1]{\href{#1}{\docsIcon}}
 
-\newcommand{\tutorialIcon}{{\color{\lwColour}{\faBook}}}
+\newcommand{\tutorialIcon}{{\color{\lwColour}{\faLaptopCode}}}
 \newcommand{\tutorialLink}[1]{\href{#1}{\tutorialIcon}}
-
-\newcommand{\notebookIcon}{{\color{\lwColour}{\faBook}}}
-\newcommand{\notebookLink}[1]{\href{#1}{\notebookIcon}}
 
@@
 All examples shown in this paper and code to reproduce the figures are available in the repository.
-Throughout this paper a \tutorialIcon{} icon in a section links to a related online tutorial and a \notebookIcon{} icon links to a Jupyter notebook with related code examples.
 Instructions for installation and basic usage are provided in the online documentation\footnote{\url{https://legwork.readthedocs.io/en/latest/}} which contain the most up-to-date instructions.
@@
 The plots and results in each subsection are reproduced directly in online demos in the \lw{} documentation, which are each based on individual Jupyter notebooks.
-These are linked at the start of each subsection with the \tutorialIcon{} and \notebookIcon{} icons respectively.
+These tutorials are linked at the start of each subsection with the \tutorialIcon{} icon.
 
-\subsection{Computing the SNR of a binary system\texorpdfstring{ - \tutorialLink{https://legwork.readthedocs.io/en/latest/demos/BasicSNRCalculation.html} \notebookLink{https://github.com/TeamLEGWORK/LEGWORK/blob/main/docs/demos/BasicSnrCalculation.ipynb}}{}}
+\subsection{Computing the SNR of a binary system\texorpdfstring{ - \tutorialLink{https://legwork.readthedocs.io/en/latest/demos/BasicSNRCalculation.html}}{}}
 
@@
 
-\subsection{Horizon distance\texorpdfstring{ - \tutorialLink{https://legwork.readthedocs.io/en/latest/demos/HorizonDistance.html} \notebookLink{https://github.com/TeamLEGWORK/LEGWORK/blob/main/docs/demos/HorizonDistance.ipynb}}{}}
+\subsection{Horizon distance\texorpdfstring{ - \tutorialLink{https://legwork.readthedocs.io/en/latest/demos/HorizonDistance.html}}{}}
 
@@
 
-\subsection{The role of eccentricity\texorpdfstring{ - \tutorialLink{https://legwork.readthedocs.io/en/latest/demos/TheRoleofEccentricity.html} \notebookLink{https://github.com/TeamLEGWORK/LEGWORK/blob/main/docs/demos/TheRoleofEccentricity.ipynb}}{}}\label{sec:eccentricity_role}
+\subsection{The role of eccentricity\texorpdfstring{ - \tutorialLink{https://legwork.readthedocs.io/en/latest/demos/TheRoleofEccentricity.html}}{}}\label{sec:eccentricity_role}
 
@@
 
-\subsection{Compare different gravitational wave detectors\texorpdfstring{ - \tutorialLink{https://legwork.readthedocs.io/en/latest/demos/CompareSensitivityCurves.html} \notebookLink{https://github.com/TeamLEGWORK/LEGWORK/blob/main/docs/demos/CompareSensitivityCurves.ipynb}}{}}
+\subsection{Compare gravitational wave detectors\texorpdfstring{ - \tutorialLink{https://legwork.readthedocs.io/en/latest/demos/CompareSensitivityCurves.html}}{}}
 
@@
 
-\subsection{Track SNR of a binary over time\texorpdfstring{ - \tutorialLink{https://legwork.readthedocs.io/en/latest/demos/SNROverTime.html} \notebookLink{https://github.com/TeamLEGWORK/LEGWORK/blob/main/docs/demos/SNROverTime.ipynb}}{}}
+\subsection{Track SNR of a binary over time\texorpdfstring{ - \tutorialLink{https://legwork.readthedocs.io/en/latest/demos/SNROverTime.html}}{}}
 
@@
 
-\bibliography{references}
+\bibliography{bib}
 \bibliographystyle{aasjournal}

### 2021-11-02 src/figures/detector_sc_compare.py
rasterise all plots

@@ -47,4 +47,6 @@ lw.visualisation.plot_sensitivity_curve(frequency_range=fr, instrument="TianQin"
 
 ax.legend(fontsize=0.7*fs)
 
+ax.set_rasterization_zorder(10000)
+
 plt.savefig("detector_sc_compare.pdf", format="pdf", bbox_inches="tight")

### 2021-11-02 src/figures/detector_snr_ratio.py

@@ -89,4 +89,6 @@ source_string += r"$D_L = {{{}}} \, {{ \rm kpc}}$".format(dist[0].value)
 ax.annotate(source_string, xy=(0.98, 0.03), xycoords="axes fraction", ha="right", fontsize=0.75*fs,
             bbox=dict(boxstyle="round", facecolor="white", edgecolor="white", alpha=0.5, pad=0.4))
 
+ax.set_rasterization_zorder(10000)
+
 plt.savefig("detector_snr_ratio.pdf", format="pdf", bbox_inches="tight")

### 2021-11-02 src/figures/horizon_distance.py

@@ -161,4 +161,6 @@ ax.annotate(r"$e = 0.0$", xy=(0.03, 0.04), xycoords="axes fraction", fontsize=0.
 
 ax.set_facecolor(plt.get_cmap("viridis")(0.0))
 
+ax.set_rasterization_zorder(10000)
+
 plt.savefig("horizon_distance.pdf", format="pdf", bbox_inches="tight")

### 2021-11-02 src/figures/merger_time.py

@@ -50,4 +50,6 @@ ax.annotate(mass_string, xy=(0.5, 0.04), xycoords="axes fraction", fontsize=0.6*
 ax.set_xlabel(r"Orbital frequency, $f_{\rm orb} \, [\rm Hz]$")
 ax.set_ylabel(r"Eccentricity, $e$")
 
+ax.set_rasterization_zorder(10000)
+
 plt.savefig("merger_time.pdf", format="pdf", bbox_inches="tight")

### 2021-11-02 src/figures/role_eccentricity.py

@@ -84,4 +84,6 @@ ax.annotate(annotation_string, xy=(3.5e-1, 1.3e-20), ha="center", va="bottom", f
 
 ax.set_ylim(1e-20, 2e-18)
 
+ax.set_rasterization_zorder(10000)
+
 plt.savefig("role_eccentricity.pdf", format="pdf", bbox_inches="tight")

### 2021-11-02 src/figures/snr_over_time.py

@@ -83,4 +83,6 @@ for ax in axes:
                 xycoords="axes fraction", va="top" if ax != axes[0] else "bottom",
                 fontsize=0.5*fs, bbox=dict(boxstyle="round", fc="white", ec="white"))
 
+ax.set_rasterization_zorder(10000)
+
 plt.savefig("snr_over_time.pdf", format="pdf", bbox_inches="tight")

### 2021-11-10 src/figures/verification_binaries_on_sc.py
add verification binary script

@@ -1,0 +1,37 @@
+import legwork as lw
+import numpy as np
+import astropy.units as u
+import matplotlib.pyplot as plt
+
+plt.rc('font', family='serif')
+plt.rcParams['text.usetex'] = False
+fs = 24
+
+# update various fontsizes to match
+params = {'figure.figsize': (12, 8),
+          'legend.fontsize': fs,
+          'axes.labelsize': fs,
+          'xtick.labelsize': 0.6 * fs,
+          'ytick.labelsize': 0.6 * fs,
+          'axes.linewidth': 1.1,
+          'xtick.major.size': 7,
+          'xtick.minor.size': 4,
+          'ytick.major.size': 7,
+          'ytick.minor.size': 4}
+plt.rcParams.update(params)
+
+vbs = lw.source.VerificationBinaries()
+vbs.snr = np.array(vbs.true_snr)
+
+fig, ax = lw.visualisation.plot_sensitivity_curve(frequency_range=np.logspace(-4, 0, 1000) * u.Hz,
+                                                  show=False)
+fig, ax = vbs.plot_sources_on_sc(scatter_s=100, marker="*", snr_cutoff=7, c=vbs.m_1[vbs.snr > 7].to(u.Msun),
+                                 fig=fig, ax=ax, show=False, cmap="Oranges", vmin=0.0, vmax=1.0)
+cbar = fig.colorbar(ax.get_children()[1])
+cbar.set_label(r"Primary Mass, $m_1 \, [{\rm M_{\odot}}]$")
+
+ax.legend(handles=[ax.get_children()[1]], labels=["LISA Verification Binaries (Kupfer+18)"], fontsize=0.7*fs, markerscale=2)
+
+ax.set_rasterization_zorder(10000)
+
+plt.savefig("verification_binaries_on_sc.pdf", format="pdf", bbox_inches="tight")

### 2021-11-10 src/ms.tex
hack the showyourwork colours to match scheme
update repo to match Overleaf

@@
 \definecolor{SeaGreen}{RGB}{63, 188, 157}
+\colorlet{sywScriptUpToDate}{SeaGreen}
 
@@
 \lw{} can be used to evolve sources over time, calculate gravitational wave strains, compute signal-to-noise ratios and visualise the results.
-In this paper we give an overview of the structure and functionality of the package, as well as highlight several optimisations that make it particularly efficient.
+In this paper we give an overview of the structure and functionality of the package, as well as highlight several optimisations that make it particularly efficient for use in population studies which can contain tens-of-millions of sources.
 We demonstrate the various capabilities of \lw{} through a series of example use cases.
@@
 The planned space-based gravitational wave detector LISA (Laser Interferometer Space Antenna) will present an entirely new view of gravitational waves by focusing on lower frequencies ($10^{-5} < f / \unit{Hz} < 10^{-1}$) than ground-based detectors.
-This will enable the study of the gravitational wave mergers of supermassive black holes that are undetectable with ground-based detectors \citep[e.g.][]{Begelman+1980, Klein+2016}.
+This will enable the study of many source classes that are undetectable with ground-based detectors including mergers of supermassive black holes that are undetectable with ground-based detectors \citep[e.g.][]{Begelman+1980, Klein+2016, Bellovary2019}, extreme mass ratio inspirals \citep[e.g.,][]{Berti2006, Barack2007, Babak2017, Moore2017}, and cosmological GW backgrounds \citep[e.g.,][]{Bartolo2016, Caprini2016, Caldwell2019}.
 However, this frequency regime is also of interest for the detection of local stellar-mass binaries during their inspiral phase.
-LISA is expected to detect Galactic stellar-origin compact objects, ranging from the numerous double white dwarf (WDWD) population, to the rare but loud double black hole (BHBH) population.
+LISA is expected to detect Galactic stellar-origin binaries containing combinations of white dwarfs, neutron stars, and black holes, ranging from the numerous double white dwarf population, to the rare but loud double black hole population.
 
@@
 We believe that the large renewed interest in LISA and the stellar-origin sources it may detect will lead to many more studies in the near future that would need similar computations.
-This leads to a significant amount of redundancy which, at best results in extra work for each individual and at worst leads to an increased chance of introducing mistakes and inconsistencies when coding up the necessary expressions.
+This leads to a significant amount of redundancy which, at best results in extra work for each individual and at worst leads to an increased chance of introducing mistakes and inconsistencies when translating the necessary expressions to software.
 
-\lw{} is a Python package designed to streamline the process of making predictions of LISA detection rates for stellar-origin binaries such that it is fast, reliable and simple.
-With \lw{} one can evolve the orbits of a binary or a collection of binaries and calculate their strain amplitudes for any range of harmonics.
+\lw{} is a Python package designed to streamline the process of making predictions of LISA detection rates for stellar-origin binaries such that it is as fast, reliable and simple as possible.
+This goal makes \lw{} unique among other implementations of gravitational-wave tools in the literature, which focus on a more broad coverage of the gravitational-wave spectrum and source classes, rather than an optimised approach for certain sources.
+\citep[e.g.][]{Moore+2015,Yi2021}.
+With \lw{} one can evolve the orbits of a binary or a collection of binaries and calculate their strain amplitudes for any range of frequency harmonics.
 One can compute the sensitivity curve for LISA or other future gravitational wave detectors (e.g.
@@
 Furthermore, \lw{} provides tools to visualise all of the results with easy-to-use plotting functions.
+Finally, \lw{} is fully tested to check for consistency in the derivations described below.
 
-Specifically, we implement the expressions by \citet{Peters+1963} and \citet{Peters+1964} for the evolution of binary orbits, equations for the strain amplitudes and signal-to-noise ratios of binaries from various papers \citep[e.g.][]{Flanagan+1998, Finn+2000, Barack+2004, Moore+2015} and approximations for the LISA and TianQin sensitivity curves given in \citet{Robson+2019} and \citet{Huang+2020} respectively.
+Specifically, we implement the expressions by \citet{Peters+1963} and \citet{Peters+1964} for the evolution of binary orbits due to the emission of gravitational waves, equations for the strain amplitudes and signal-to-noise ratios of binaries from various papers \citep[e.g.][]{Flanagan+1998, Finn+2000, Cornish2003, Barack+2004, Moore+2015} and approximations for the LISA and TianQin sensitivity curves given in \citet{Robson+2019} and \citet{Huang+2020} respectively.
 
@@
 In Section~\ref{sec:LEGWORK-overview} we give an overview of the capabilities of the \lw{} package and its various modules.
+We detail the derivations of the equations relevant for \lw{} in Section~\ref{sec:derivations}.
 In Section~\ref{sec:example-uses} we outline some example use cases of \lw{} to demonstrate its use.
-We detail the derivations of the equations relevant for \lw{} in Section~\ref{sec:derivations}.
 Finally, in Section~\ref{sec:summary} we conclude and summarise our work.
@@
 The \lw{} package is composed of seven modules that each focus on a particular aspect of calculations useful for LISA gravitational wave sources.
-In Fig.~\ref{fig:package_overview}, we illustrate the general structure of the package with its various modules.
+In Fig.~\ref{fig:package_overview}, we illustrate the general structure of the package with each of its modules.
 The source module is the central module of the package and provides an simple interface to the functions in the rest of the modules.
@@
 
-\lwModLink{evol} deals with the orbital evolution of a binary due to gravitational waves.
+\lwModLink{evol} handles the orbital evolution of a binary due to the emission of gravitational waves.
 It includes functions for computing the merger times of both circular and eccentric binaries.
@@
 \lwModLink{strain} contains two functions that compute a binary's gravitational wave strain and characteristic strain amplitude respectively.
-Each of these functions is capable of computing the strain for a 3-dimensional array of binaries at any number of timesteps and evaluated at any number of harmonics.
+Each of these functions is capable of computing the strain for a 3-dimensional array of binaries at any number of timesteps and evaluated at any number of frequency harmonics.
 We discuss the relevant equations in Sec.~\ref{sec:deriv_strain}.
@@
 You can instantiate this Class with an array of sources and use it compute their strains or signal-to-noise ratios directly.
-Moreover, depending on the user's choice of allowed gravitational wave luminosity error, the Class dynamically decides on the number of harmonics needed to capture the full signal of each binary and at what eccentricity to no longer consider a binary circular.
+Moreover, depending on the user's choice of allowed gravitational wave luminosity error, the Class dynamically decides on the number of frequency harmonics needed to capture the full signal of each binary and at what eccentricity to no longer consider a binary circular.
 This Class also provides a quick means of evolving the sources, visualising the parameters of each source and allows you to plot the binaries on the sensitivity curve.
@@
 We discuss the relevant equations in Sec.~\ref{sec:deriv_utils}.
+
+To ensure stability with physical units, all quantities included in \lw{} use the \texttt{astropy.units} module \citep{AstropyCollaboration+2013, AstropyCollaboration+2018}.
+This means that all inputs to \lw{} can be given in the units of the user's choice and will be automatically converted.
+Furthermore, all of the source code in \lw{} is fully tested with continuous integration in the \lw{} GitHub repository.
+We employ several unit tests to ensure consistency between each of the use cases described below.
+For example, we require that the SNR calculation for circular and stationary binaries produces consistent output whether \lw{} uses the stationary and circular approximations or not.
+Similarly, we verify that the antenna patterns described below produce the expected values when averaged over source positions, inclinations, and polarisations.
 
@@
 
-Moreover, for increasingly eccentric sources, gravitational waves are emitted in an increasing number of higher harmonics.
+Moreover, for increasingly eccentric sources, gravitational waves are emitted in an increasing number of higher frequency harmonics.
 Although the total SNR is formally calculated as a the sum of the SNR over an infinite number of harmonics, in practice it is sufficient to only consider a subset.
@@
 
-\section{Use cases}\label{sec:example-uses}
-In this section, we demonstrate \lw{}'s range of capabilities through a series of example use cases.
-The plots and results in each subsection are reproduced directly in online demos in the \lw{} documentation, which are each based on individual Jupyter notebooks.
-These tutorials are linked at the start of each subsection with the \tutorialIcon{} icon.
-
-\subsection{Computing the SNR of a binary system\texorpdfstring{ - \tutorialLink{https://legwork.readthedocs.io/en/latest/demos/BasicSNRCalculation.html}}{}}
-
-The most fundamental use case of \lw{} is to compute the SNR of a binary system in LISA.
-This can be accomplished in \lw{} with only two lines of code - one line to set up the source and another to compute the SNR.
-As an example one could consider a binary with the parameters
-\begin{align*}
-    m_1 = m_2 &= 10 \unit{M_{\odot}},\ d = 8 \unit{kpc},\\
-    f_{\rm orb} &= 10^{-4} \unit{Hz},\ e = 0.2,
-\end{align*}
-where $m_1, m_2$ are the primary and secondary masses, $d$ is the distance to the source, $f_{\rm orb}$ is the orbital frequency and $e$ is the eccentricity.
-As we don't specify a position, polarisation or inclination, \lw{} will calculate the SNR averaged over these quantities.
-One can now instantiate a source in \lw{} using these parameters (leaving the LISA mission parameters as the default values, such that we compute the SNR for a 4-year LISA mission).
-As shown in the linked demo, \lw{} quickly computes that the SNR of this binary is $4.49$.
-In the background, \lw{} decides which SNR approximation is most applicable given the eccentricity of the binary and whether it is stationary in frequency space.
-
-Moreover, this can be generalised to a population of many binary systems with ease.
-Instead of inputting single values for each parameter, one can input arrays of values where each entry corresponds to a different binary.
-As an example, we can take the same parameters as above for 3 different binaries but vary the primary as $m_1 = [5, 10, 15] \unit{M_{\odot}}$.
-Using \lw{} we find that the SNR for each of these cases is $\rho = [2.47, 4.49, 7.85]$.
-
-\subsection{Horizon distance\texorpdfstring{ - \tutorialLink{https://legwork.readthedocs.io/en/latest/demos/HorizonDistance.html}}{}}
-
-\begin{figure*}[htb]
-    \centering
-    \includegraphics[width=\textwidth]{figures/horizon_distance.pdf}
-    \caption{The horizon distance for circular stellar mass binaries in a four-year LISA mission.
-The filled contours indicate the horizon distance for different orbital frequencies and chirp masses.
-We add white dotted contours at $8, 50, 800 \unit{kpc}$ and $40 \unit{Mpc}$ to highlight the distances to the centre of the Milky Way, the Magellanic Clouds, the Andromeda galaxy and the nearest ground-based gravitational wave detection (GW170817, \citealp{Abbott+2017_GW170817}) respectively.
-The diagonal line black line shows the frequencies and chirp masses at which the merger time is equal to the observation time.
-This line emphasises the sharp contrast for the horizon distance for binaries that merge before the LISA mission finishes observing (to the right of the line).
-The horizontal black lines indicate the approximate location of some common double compact object types on this plot, with the assumed masses labelled below in solar masses.}
-    \label{fig:horizon_distance}
-\end{figure*}
-
-A common question to consider with stellar mass sources in LISA is how far away a certain source could be detected.
-In other words, what is the horizon distance beyond which a source no longer has a SNR greater than some chosen threshold.
-We can explore this question using \lw{}.
-
-Let us compute the horizon distance for a grid of chirp masses and orbital frequencies.
-First, we can recall that the signal-to-noise ratio of a source is inversely proportional to its distance from LISA and so we can find the horizon distance, $D_{\rm hor}$ as
-\begin{equation}{}
-    \label{eq:snr_to_hor_dist}
-    D_{\rm hor} = \frac{\rho(D)}{\rho_{\rm detect}} \cdot D,
-\end{equation}
-where $\rho(D)$ is the signal-to-noise ratio as some distance $D$ and $\rho_{\rm detect}$ is the threshold above which we consider a source to be detectable.
-For the purpose of this example we will set $\rho_{\rm detect} = 7$.
-Therefore, we can start by finding the signal-to-noise ratio for each source at an arbitrary distance and convert that to a horizon distance.
-
-This can be most efficiently accomplished using \lw{}'s source class.
-Although the source class only takes one-dimensional lists of sources, one can flatten a grid of chirp masses and orbital frequencies to make the input work.
-\lw{} can then compute the merger times and signal-to-noise ratio of each source with only two lines of code.
-These results can then be reshaped to match the original grid of chirp masses and frequencies.
-
-We convert these SNRs to horizon distances using Eq.~\ref{eq:snr_to_hor_dist} and plot the result in Figure~\ref{fig:horizon_distance}.
-The shape of the LISA sensitivity curve is clearly reflected in this plot of the horizon distance.
-This is because circular sources emit the vast majority of their single at a single frequency and thus every feature in the sensitivity curve has a strong effect on the SNR (and therefore horizon distance) for circular sources.
-We also see that once the merger time of a source is shorter than the LISA mission length (shown by the black dotted line), the horizon distance sharply decreases.
-This is because if a source merges before the LISA mission concludes, it has less time to accumulate signal and thus has a lower SNR and horizon distance.
-
-One can use Figure~\ref{fig:horizon_distance} to estimate the horizon distance for any circular source of interest.
-To illustrate this, we add solid black lines to indicate the typical chirp masses of some possible stellar mass gravitational wave sources as well as white dotted lines to show the distances to nearby galaxies as well as the nearest ground-based gravitational wave detection (GW170817, \citealp{Abbott+2017_GW170817}).
-For example, we see that a circular NSNS with an orbital frequency greater than a mHz is detectable in the Magellanic clouds.
-
-\subsection{The role of eccentricity\texorpdfstring{ - \tutorialLink{https://legwork.readthedocs.io/en/latest/demos/TheRoleofEccentricity.html}}{}}\label{sec:eccentricity_role}
-
-The role of eccentricity is an important concept to consider in the detection of gravitational waves with LISA as sources can still have significant eccentricity during their inspiral phase.
-A high eccentricity has two major effects on the SNR of a gravitational wave source in LISA and we can investigate this using \lw{}.
-
-Let's use three toy sources that are identical apart from their eccentricities, $e_i$.
-\begin{align*}{}
-    m_1 &= m_2 = 0.6 \unit{M_{\odot}}, f_{\rm orb} = 1.5 \unit{mHz}, d = 15 \unit{kpc}, \\
-    e_i &= \{0.0, 0.6, 0.9 \},
-\end{align*}
-Using \lw{} to calculate their signal-to-noise ratios, $\rho_i$, we find
-\begin{equation*}{}
-    \rho_i = \{ 31.7, 50.2, 38.8 \}
-\end{equation*}
-
-We see two effects in the signal-to-noise ratio here.
-First, increasing the eccentricity from essentially circular to $e = 0.6$ results in a higher signal-to-noise ratio ($\rho=31.7 \to \rho=50.2$).
-This is because an eccentric binary has enhanced energy emission via gravitational waves \citep{Peters+1963}.
-This means that an eccentric binary will not only inspiral faster than an otherwise identical circular binary, but also will always have a stronger gravitational wave strain.
-The enhancement factor and its exact dependence on eccentricity is discussed in more detail Section~\ref{sec:derivations} (specifically Eq.~\ref{eq:eccentricity_enhancement_factor}).
-
-The second effect is more intriguing.
-We see that increasing the eccentricity from $e = 0.6$ to $e = 0.9$ results in a relative \textit{decrease} in SNR ($\rho=50.2 \to \rho=38.8$).
-The reason for this is that eccentric binaries emit gravitational waves at many harmonic frequencies (unlike circular binaries, which emit predominantly twice the orbital frequency).
-This leads to the gravitational wave signal being diluted over many frequencies higher than the orbital frequency, where the higher the eccentricity, the more harmonics are required to capture all of the gravitational luminosity \citep[see][Fig.\,3]{Peters+1963}.
-Therefore, if the eccentricity is too high, the majority of the signal may be emitted at a frequency to which LISA is less sensitive.
-
-We can illustrate this point with \lw{} by calculating the SNR at each individual harmonic using the \lwModLink{snr} module.
-We plot this distribution of signal over different harmonics with the LISA sensitivity curve overlaid in Fig.~\ref{fig:role_eccentricity} using \lw{}'s \lwModLink{visualisation} module.
-A point is plotted for each harmonic of each source that has an SNR greater than unity and such that its height above the sensitivity curve corresponds to its SNR.
-
-\begin{figure}[tb]
-    \centering
-    \includegraphics[width=\columnwidth]{figures/role_eccentricity.pdf}
-    \caption{An illustration of the effect of eccentricity on the detectability of a LISA source.
-The three sets of points are coloured by their eccentricity and each individual point corresponds to a harmonic frequency, where its height above the curve gives its SNR.
-We annotate each set of points with its total SNR and overlay the LISA sensitivity curve.
-The dotted vertical lines indicate the frequency at which the majority of the gravitational wave signal is concentrated.}
-    \label{fig:role_eccentricity}
-\end{figure}
-
-From Fig.~\ref{fig:role_eccentricity}, we can better understand why a source with $e = 0.9$ has a lower SNR than the same source with $e = 0.6$.
-From the dotted lines, we can note that the signal from the $e = 0.9$ source is concentrated at a frequency of around $4 \times 10^{-2} \unit{Hz}$.
-The LISA sensitivity at this point is much weaker than the $6 \times 10^{-3} \unit{Hz}$ at which the $e =0.6$ source is concentrated.
-Therefore, although the strain from a more eccentric binary is stronger, the SNR is lower due to the increased noise in the LISA detector.
-
-Overall, we can therefore conclude that for LISA sources of this nature, higher eccentricity will produce more detectable binaries only if the orbital frequency is not already at or above the minimum of the LISA sensitivity curve.
-
-\begin{figure}[htb]
-    \centering
-    \includegraphics[width=\columnwidth]{figures/merger_time.pdf}
-    \caption{The merger time for a binary with both a primary and secondary mass of $10 \unit{M_{\odot}}$ over different eccentricities and orbital frequencies.}
-    \label{fig:merger_time}
-\end{figure}
-
-Another consideration for more massive binaries is whether the increased eccentricity will cause the binary to merge before the mission ends, which would cause a significant decrease in signal-to-noise ratio.
-We can also use \lw{} to find how the merger time of a source varies with frequency and eccentricity over a grid of sources.
-
-We plot the results of this calculation in Figure~\ref{fig:merger_time}.
-This plot shows that for most eccentricities the merger is time is largely determined by the orbital frequency.
-However, for high eccentricities ($e > 0.8$), the eccentricity significantly reduces the merger time.
-
-\subsection{Compare gravitational wave detectors\texorpdfstring{ - \tutorialLink{https://legwork.readthedocs.io/en/latest/demos/CompareSensitivityCurves.html}}{}}
-
-It may also be useful to consider how changing the specifications of the LISA detector, or using a different detector entirely, could affect the SNR of a particular source.
-\lw{} is capable of adjusting the LISA mission specifications or using a different sensitivity curve and thus we can use it to explore these differences.
-
-As a first step, we can use \lw{} to plot a series of sensitivity curves in Figure~\ref{fig:detector_sc_compare}.
-We show the LISA sensitivity curve for the default 4 year mission length but also illustrate how the curve changes for shorter mission lengths.
-At 0.5 and 2 years, we see a stronger noise level around $3 \unit{mHz}$ as a result of the increased Galactic confusion noise.
-This noise decreases with increasing mission length since more individual foreground sources can be resolved and thus removed from the confusion noise.
-We also see that using an approximated response function smooths out the sensitivity curve at higher frequencies.
-Finally, the TianQin curve is higher than the 4 year LISA curve until around $5 \unit{mHz}$, beyond which it has a lower noise level.
-
-\begin{figure}[htb]
-    \centering
-    \includegraphics[width=\columnwidth]{figures/detector_sc_compare.pdf}
-    \caption{The strain spectral density of the LISA detector (with different specifications) and the TianQin detector.
-We show the LISA curve for three different mission lengths and once with an approximate response function.}
-    \label{fig:detector_sc_compare}
-\end{figure}
-
-Although comparing the sensitivity curves would suffice for a stationary and circular source (since it would remain at a single frequency), \lw{} can also be used to see how the relative SNR between two detectors changes over a range of eccentricities and frequencies.
-
-Using \lw{}, we can compute the SNR of a grid of sources (spanning a range of frequencies and eccentricities) for both detectors.
-In Figure~\ref{fig:detector_snr_ratio}, we show the ratio of the SNR in LISA to the SNR in TianQin.
-This plot shows that for circular binaries, the SNR of the source in LISA is stronger up to an orbital frequency of approximately $2.5 \unit{mHz}$, beyond which the SNR of the source is stronger in TianQin.
-This transition frequency becomes lower with increasing eccentricity as one would expect since eccentric sources emit more at higher harmonics and thus higher frequencies.
-
-\begin{figure}[htb]
-    \centering
-    \includegraphics[width=\columnwidth]{figures/detector_snr_ratio.pdf}
-    \caption{The ratio of the SNR in LISA (for a four year mission) to the SNR in TianQin.
-The dashed line indicates the transition at which the SNR is equal in both detectors.
-We annotate the regions in which either detector has a higher SNR and also annotate the mass and distance of each source in the grid.}
-    \label{fig:detector_snr_ratio}
-\end{figure}
-
-\subsection{Track SNR of a binary over time\texorpdfstring{ - \tutorialLink{https://legwork.readthedocs.io/en/latest/demos/SNROverTime.html}}{}}
-
-As a binary inspirals its orbital frequency and eccentricity change and this in turn affects the SNR of the binary.
-For this use case we will demonstrate how \lw{} can be used to track the evolution of these parameters and pinpoint the moment at which a binary becomes detectable.
-
-Let's consider a binary with the following initial parameters
-\begin{align*}
-    m_1 &= m_2 = 15 \unit{M_{\odot}},\ d = 20 \unit{kpc},\\
-    f_{\rm orb, i} &= 3 \times 10^{-5} \unit{Hz},\ e_i = 0.5,
-\end{align*}
-and use \lw{} to evolve the system until 100 years before its merger with 1000 linearly spaced timesteps, recording the eccentricity and frequency at each timestep.
-
-We plot this evolution of the eccentricity and frequency in the top two panels of Fig.~\ref{fig:snr_over_time} as a function of the time before the merger.
-We see that the binary circularises and increases its orbital frequency as it inspirals as we would expect.
-
-To take this a step further, we can consider the binary at each timestep to be a separate source with the current eccentricity and frequency.
-It is then trivial to use \lw{} to calculate the SNR for each of these `sources' and thus attain the SNR evolution, which we plot in the last panel of Fig.~\ref{fig:snr_over_time}.
-
-We see that the SNR increases monotonically over time and sharply increases as the binary approaches its merger.
-Around $1 \unit{Myr}$ before the merger, the SNR reaches the detection threshold and thus could then be seen by a 4-year LISA mission.
-
-Note that \lw{} could also be used in this way to find the SNR of any system in which the orbital evolution is know.
-Thus for a triple system or a binary experiencing gas drag (as long the evolution of the eccentricity and orbital frequency is known) \lw{} is entirely capable of calculating the SNR evolution.
-
-\begin{figure}
-    \centering
-    \includegraphics[width=\columnwidth]{figures/snr_over_time.pdf}
-    \caption{The evolution of a binary system's eccentricity (top), orbital frequency (middle) and signal-to-noise ratio (bottom).
-Each panel is annotated with the constant parameters of the system.
-The SNR is calculated for a 4-year LISA mission.
-We annotate in  a line the bottom panel at $\mathrm{SNR} = 7$ to highlight the moment at which the source becomes detectable.}
-    \label{fig:snr_over_time}
-\end{figure}
-
-% \subsection{SNR calculation for verification binaries}
-
-%\section{Benchmarks}\label{sec:speed}
-%A section to show off \lw{}'s speed.
-
 \section{Derivations}\label{sec:derivations}
@@
 
-A \docsIcon{} symbol in an equation will link to the relevant \lw{} documentation for the implementation of that equation.
+A \docsIcon{} symbol in an equation will link to the relevant \lw{} documentation for the implementation of that equation, which additionally contains a link to exact code used to reproduce the equation.
 These derivations are also given in more detail in the \lw{} documentation \href{https://legwork.readthedocs.io/en/latest/notebooks/Derivations.html}{here}, where we show each of the intervening steps in more detail.
@@
 
-For eccentric binaries, we need to consider all harmonics of gravitational wave emission. These are defined such that the $n^{\rm th}$ harmonic frequency is
+For eccentric binaries, we need to consider all frequency harmonics of gravitational-wave emission. These are defined such that the $n^{\rm th}$ harmonic frequency is
 \begin{equation}{}
@@
 \end{equation}
-It will be important to know the relative power radiated into the $n^{\rm th}$ harmonic for a binary with eccentricity $e$, which is given by \citep[][Eq.\,20]{Peters+1963}
+It will be important to know the relative gravitational-wave power radiated into the $n^{\rm th}$ harmonic for a binary with eccentricity $e$ for the following strain and SNR calculations.
+This is given by \citep[][Eq.\,20]{Peters+1963}
 \begin{equation}{\lwFuncURL{utils}{peters_g}}
@@
 where $J_{n}(v)$ is the Bessel function of the first kind.
-Thus, the \textit{sum} of $g(n, e)$ over all harmonics gives the factor by which the gravitational wave emission is stronger for a binary of eccentricity $e$ over an equivalent circular binary.
+Thus, the \textit{sum} of $g(n, e)$ over all harmonics gives the factor by which the gravitational-wave emission is stronger for a binary of eccentricity $e$ over an equivalent circular binary.
 This enhancement factor is \citep[][Eq.\,17]{Peters+1963}
@@
 \end{equation}
-A fun number to remember is that $F(0.5) \approx 5.0$, or in words, a binary with eccentricity $0.5$ loses energy to gravitational waves at 5 times the rate of an equivalent circular binary.
+A useful rule of thumb is that $F(0.5) \approx 5.0$, or in words, a binary with eccentricity $0.5$ loses energy to gravitational waves at 5 times the rate of an equivalent circular binary.
 
@@
 \subsubsection{Circular binaries}
-For a circular binary, the evolution can be calculated analytically, as the rate at which the separation of the binary shrinks is simply a function of its mass and the current separation \citep[][Eq.~5.6]{Peters+1964}
+For a circular binary, the orbital evolution due to gravitational-wave emission can be calculated analytically, as the rate at which the separation of the binary shrinks is simply a function of its mass and the current separation \citep[][Eq.~5.6]{Peters+1964}
 \begin{equation}{}
@@
 \end{align}
+\noindent The standard threshold employed by \lw{} for small eccentricities is $e=0.01$ and for large eccentricities is $e=0.99$, though we note that this can be customised by the user as well.
 
@@
 Therefore, to account for the integration of the signal over the mission, we can introduce the `characteristic' strain amplitude of the $n^{\rm th}$ harmonic \citep[e.g][]{Finn+2000, Moore+2015}\footnote{Note that this is factor of 2 different from \citet{Finn+2000}.
-This is because the factor of 2 is already included in the \citet{Robson+2019} sensitivity curve and so we remove it here.}
+This is because the factor of 2 is already included in the \citet{Robson+2019} sensitivity curve and so is removed here.}
 \begin{equation}{}
@@
 \subsubsection{Strain}
-In order to get an expression for the strain amplitude of gravitational waves in the $n^{\rm th}$ harmonic, we can use Eq.~\ref{eq:strain-charstrain} and plug in Eq.~\ref{eq:fdot} and Eq.~\ref{eq:char_strain}
+In order to obtain an expression for the strain amplitude of gravitational waves in the $n^{\rm th}$ harmonic, we can use Eq.~\ref{eq:strain-charstrain} and plug in Eq.~\ref{eq:fdot} and Eq.~\ref{eq:char_strain}
 \begin{equation}{\lwFuncURL{strain}{h_0_n}}
@@
 \end{equation}
+
+\subsubsection{Amplitude modulation for orbit averaged sources}
+\label{sec:amplitude_mod}
+Because the LISA detectors are not stationary and instead follow an Earth-trailing orbit, the antenna pattern of LISA is not isotropically distributed or stationary.
+For sources that have a known position, inclination, and polarisation, we can consider the amplitude modulation of the strain due to the average motion of LISA's orbit.
+We closely follow the results of \citet{Cornish2003} to write down the amplitude modulation as
+
+\begin{equation}{\lwFuncURL{strain}{amplitude_modulation}}
+    A_{\rm{mod}}^{2}=\frac{1}{2} \left[\left(1+\cos ^{2} \iota\right)^{2}\left\langle F_{+}^{2}\right\rangle+4 \cos ^{2} \iota\left\langle F_{\times}^{2}\right\rangle\right],
+\label{eq:amp_mod}
+\end{equation}
+where $\left\langle F_{+}^{2}\right\rangle$ and $\left\langle F_{\times}^{2}\right\rangle$, the orbit-averaged detector responses, are defined as
+\begin{equation}{\lwFuncURL{utils}{F_plus_squared}}
+    \begin{split}
+        \avg{ F_{+}^{2}} = \frac{1}{4}\big(\cos ^{2} 2 \psi\left\langle D_{+}^{2}\right\rangle &-\sin 4 \psi\left\langle D_{+} D_{\times}\right\rangle\\
+        &+\sin ^{2} 2 \psi\left\langle D_{\times}^{2}\right\rangle\big),
+    \end{split}
+\label{eq:response_fplus}
+\end{equation}
+
+\begin{equation}{\lwFuncURL{utils}{F_cross_squared}}
+    \begin{split}
+        \avg{ F_{\times}^{2}} = \frac{1}{4}\big(\cos^{2} 2 \psi \avg{ D_{\times}^{2}} &+\sin 4 \psi \avg{ D_{+} D_{\times}}\\
+        &+\sin ^{2} 2 \psi \avg{ D_{+}^{2}} \big),
+    \end{split}
+\label{eq:response_fcross}
+\end{equation}
+and
+\begin{equation}{\lwFuncURL{utils}{D_plus_D_cross}}
+    \begin{split}
+       \avg{ D_{+} D_{\times}} = \frac{243}{512} \cos \theta \sin 2 \phi &\left(2 \cos ^{2} \phi-1\right) \\ &\times \left(1+\cos ^{2} \theta\right),
+    \end{split}
+\label{eq:d_plus_cross}
+\end{equation}
+\begin{equation}{\lwFuncURL{utils}{D_cross_squared}}
+    \begin{split}
+        \avg{ D_{\times}^{2}} = \frac{3}{512}\big(120 \sin ^{2} \theta &+\cos ^{2} \theta \\
+        &+162 \sin ^{2} 2 \phi \cos ^{2} \theta\big),
+    \end{split}
+\label{eq:d_cross}
+\end{equation}
+\begin{equation}{\lwFuncURL{utils}{D_plus_squared}}
+    \begin{split}
+       \avg{ D_{+}^{2} } =  \frac{3}{2048}\big[&487+158 \cos ^{2} \theta+7 \cos ^{4} \theta\\
+        &-162 \sin ^{2} 2 \phi\left(1+\cos ^{2} \theta\right)^{2}\big].
+    \end{split}
+\label{eq:d_plus}
+\end{equation}
+In the equations above, the inclination is given by $\iota$, the right ascension and declination are given by $\phi$ and $\theta$ respsectively, and the polarisation is given by $\psi$.
+
+The orbital motion of LISA smears the source frequency by roughly $10^{-4}\,\rm{mHz}$ due to the antenna pattern changing as the detector orbits, the Doppler shift from the motion, and the phase modulation from the $+$ and $\cross$ polarisations in the antenna pattern.
+Generally, the modulation reduces the strain amplitude because the smearing in frequency reduces the amount of signal build up at the true source frequency.
+
+We note that since the orbit averaging is carried out in Fourier space, this requires the frequency to be monochromatic and thus is only implemented in \lw{} for quasi-circular binaries.
+We also note that since the majority of the calculations in \lw{} are carried out for the full position, polarisation, and inclination averages, we place a pre-factor of $5/4$ on the amplitude modulation in the software implementation to undo the factor of $4/5$ which arises from the averaging of Equations~\ref{eq:response_fplus} and \ref{eq:response_fcross}.
 
@@
 
-Please note that this section draws heavily from \citet{Flanagan+1998} Section II C.
+We note that this section draws heavily from \citet{Flanagan+1998} Section II C.
 
@@
 
-In LISA's case, when averaged over all angles and polarisations, the antenna patterns are orthogonal thus $\langle F_+ F_{\times}\rangle = 0$. This means we can rewrite Eq.~\ref{eq:signal} as 
+In LISA's case, when averaged over all angles and polarisations, the antenna patterns are orthogonal and thus $\langle F_+ F_{\times}\rangle = 0$. This means we can rewrite Eq.~\ref{eq:signal} as 
 \begin{equation}{}
@@
 Note that the factor of frequency squared comes from the Fourier transform of the square of the time derivative in Eq.~\ref{eq:Parseval}.
-Now, since $A = D_L^2 \Omega$ and $|\tilde{h}_{+,\times}|^2 = |\tilde{H}_{+,\times}|^2 / D_L^2$, we know
+Now, since $A = D_L^2 \Omega$ and $|\tilde{h}_{+,\times}|^2 = |\tilde{H}_{+,\times}|^2 / D_L^2$, we find
 \begin{equation}{}
@@
 \end{equation}
-Alternatively, by using Eq.~\ref{eq:little_h_to_big} and performing a Fourier transform we also have that
+Alternatively, by using Eq.~\ref{eq:little_h_to_big} and performing a Fourier transform we can also write that
 \begin{equation}{}
@@
 
+For SNR calculations that take into account the amplitude modulation due to LISA's orbital motion (Section~\ref{sec:amplitude_mod}, we apply the calculations as described above but include the modulation in either the strain or characteristic strain as is appropriate.
+
+\section{Use cases}\label{sec:example-uses}
+In this section, we demonstrate \lw{}'s range of capabilities through a series of example use cases.
+The plots and results in each subsection are reproduced directly in online demos in the \lw{} documentation, which are each based on individual Jupyter notebooks.
+These tutorials are linked at the start of each subsection with the \tutorialIcon{} icon.
+
+\subsection{Computing the SNR of a binary system\texorpdfstring{ - \tutorialLink{https://legwork.readthedocs.io/en/latest/demos/BasicSNRCalculation.html}}{}}
+
+The most fundamental use case of \lw{} is to compute the SNR of a binary system in LISA.
+This can be accomplished in \lw{} with only two lines of code - one line to set up the source and another to compute the SNR.
+As an example one could consider a binary with the parameters
+\begin{align*}
+    m_1 = m_2 &= 10 \unit{M_{\odot}},\ d = 8 \unit{kpc},\\
+    f_{\rm orb} &= 10^{-4} \unit{Hz},\ e = 0.2,
+\end{align*}
+where $m_1, m_2$ are the primary and secondary masses, $d$ is the distance to the source, $f_{\rm orb}$ is the orbital frequency and $e$ is the eccentricity.
+As we don't specify a position, polarisation or inclination, \lw{} will calculate the SNR averaged over these quantities.
+One can now instantiate a source in \lw{} using these parameters (leaving the LISA mission parameters as the default values, such that we compute the SNR for a 4-year LISA mission).
+As shown in the linked demo, \lw{} quickly computes that the SNR of this binary is $4.49$.
+In the background, \lw{} decides which SNR approximation is most applicable given the eccentricity of the binary and whether it is stationary in frequency space.
+
+Moreover, this can be generalised to a population of many binary systems with ease.
+Instead of inputting single values for each parameter, one can input arrays of values where each entry corresponds to a different binary.
+As an example, we can take the same parameters as above for 3 different binaries but vary the primary as $m_1 = [5, 10, 15] \unit{M_{\odot}}$.
+Using \lw{} we find that the SNR for each of these cases is $\rho = [2.47, 4.49, 7.85]$.
+
+\subsection{Horizon distance\texorpdfstring{ - \tutorialLink{https://legwork.readthedocs.io/en/latest/demos/HorizonDistance.html}}{}}
+
+\begin{figure*}[htb]
+    \centering
+    \includegraphics[width=\textwidth]{figures/horizon_distance.pdf}
+    \caption{The horizon distance for circular stellar mass binaries in a four-year LISA mission.
+The filled contours indicate the horizon distance for different orbital frequencies and chirp masses.
+We add white dotted contours at $8, 50, 800 \unit{kpc}$ and $40 \unit{Mpc}$ to highlight the distances to the centre of the Milky Way, the Magellanic Clouds, the Andromeda galaxy and the nearest ground-based gravitational wave detection (GW170817, \citealp{Abbott+2017_GW170817}) respectively.
+The diagonal line black line shows the frequencies and chirp masses at which the merger time is equal to the observation time.
+This line emphasises the sharp contrast for the horizon distance for binaries that merge before the LISA mission finishes observing (to the right of the line).
+The horizontal black lines indicate the approximate location of some common double compact object types on this plot, with the assumed masses labelled below in solar masses.}
+    \label{fig:horizon_distance}
+\end{figure*}
+
+A common question to consider with stellar mass sources in LISA is how far away a certain source could be detected.
+In other words, what is the horizon distance beyond which a source no longer has a SNR greater than some chosen threshold.
+We can explore this question using \lw{}.
+
+Let us compute the horizon distance for a grid of chirp masses and orbital frequencies.
+First, we can recall that the signal-to-noise ratio of a source is inversely proportional to its distance from LISA and so we can find the horizon distance, $D_{\rm hor}$ as
+\begin{equation}{}
+    \label{eq:snr_to_hor_dist}
+    D_{\rm hor} = \frac{\rho(D)}{\rho_{\rm detect}} \cdot D,
+\end{equation}
+where $\rho(D)$ is the signal-to-noise ratio as some distance $D$ and $\rho_{\rm detect}$ is the threshold above which we consider a source to be detectable.
+For the purpose of this example we will set $\rho_{\rm detect} = 7$.
+We can then, as a function of chirp mass and frequency, determine the maximum distance for which the source of interest is detected based on this SNR threshold.
+
+This can be most efficiently accomplished using \lw{}'s source class.
+Although the source class only reads in one-dimensional lists of sources, one can flatten a grid of chirp masses and orbital frequencies to make the input work.
+\lw{} can then compute the merger times and signal-to-noise ratio of each source with only two lines of code.
+These results can then be reshaped to match the original grid of chirp masses and frequencies.
+
+We convert these SNRs to horizon distances using Eq.~\ref{eq:snr_to_hor_dist} and plot the result in Figure~\ref{fig:horizon_distance}.
+The shape of the LISA sensitivity curve is clearly reflected in the horizon distance.
+This is because circular sources only emit at a single frequency and thus every feature in the sensitivity curve has a strong effect on the SNR (and therefore horizon distance) for circular sources.
+We also see that once the merger time of a source is shorter than the LISA mission length (shown by the black dotted line), the horizon distance sharply decreases.
+This is because if a source merges before the LISA mission concludes, it has less time to accumulate signal and thus has a lower SNR and horizon distance.
+
+One can use Figure~\ref{fig:horizon_distance} to estimate the horizon distance for any circular source of interest.
+To illustrate this, we add solid black lines to indicate the typical chirp masses of some possible stellar mass gravitational wave sources as well as white dotted lines to show the distances to nearby galaxies as well as the nearest ground-based gravitational wave detection (GW170817, \citealp{Abbott+2017_GW170817}).
+For example, we see that a circular NSNS with an orbital frequency greater than a mHz is detectable in the Magellanic clouds.
+
+\subsection{The role of eccentricity\texorpdfstring{ - \tutorialLink{https://legwork.readthedocs.io/en/latest/demos/TheRoleofEccentricity.html}}{}}\label{sec:eccentricity_role}
+
+The role of eccentricity is an important concept to consider in the detection of gravitational waves with LISA as sources can still have significant eccentricity during their inspiral phase.
+A high eccentricity has two major effects on the SNR of a gravitational wave source in LISA and we can investigate this using \lw{}.
+
+Let's use three toy sources that are identical apart from their eccentricities, $e_i$.
+\begin{align*}{}
+    m_1 &= m_2 = 0.6 \unit{M_{\odot}}, f_{\rm orb} = 1.5 \unit{mHz}, d = 15 \unit{kpc}, \\
+    e_i &= \{0.0, 0.6, 0.9 \},
+\end{align*}
+Using \lw{} to calculate their signal-to-noise ratios, $\rho_i$, we find
+\begin{equation*}{}
+    \rho_i = \{ 31.7, 50.2, 38.8 \}
+\end{equation*}
+
+We see two effects in the signal-to-noise ratio here.
+First, increasing the eccentricity from essentially circular to $e = 0.6$ results in a higher signal-to-noise ratio ($\rho=31.7 \to \rho=50.2$).
+This is because an eccentric binary has enhanced energy emission via gravitational waves \citep{Peters+1963}.
+This means that an eccentric binary will not only inspiral faster than an otherwise identical circular binary, but also will always produce a stronger gravitational wave strain.
+The enhancement factor and its exact dependence on eccentricity is discussed in more detail Section~\ref{sec:derivations} (specifically Eq.~\ref{eq:eccentricity_enhancement_factor}).
+
+The second effect is more intriguing.
+We see that increasing the eccentricity from $e = 0.6$ to $e = 0.9$ results in a relative \textit{decrease} in SNR ($\rho=50.2 \to \rho=38.8$).
+The reason for this is that eccentric binaries emit gravitational waves at many harmonic frequencies (unlike circular binaries, which emit predominantly twice the orbital frequency).
+This leads to the gravitational wave signal being diluted over many frequencies higher than the orbital frequency, where the higher the eccentricity, the more harmonics are required to capture all of the gravitational luminosity \citep[see][Fig.\,3]{Peters+1963}.
+Therefore, if the eccentricity is too high, the majority of the signal may be emitted at a frequency to which LISA is less sensitive.
+
+We can illustrate this point with \lw{} by calculating the SNR at each individual harmonic using the \lwModLink{snr} module.
+We plot this distribution of signal over different harmonics with the LISA sensitivity curve overlaid in Fig.~\ref{fig:role_eccentricity} using \lw{}'s \lwModLink{visualisation} module.
+A point is plotted for each harmonic of each source that has an SNR greater than unity and such that its height above the sensitivity curve corresponds to its SNR.
+
+\begin{figure}[tb]
+    \centering
+    \includegraphics[width=\columnwidth]{figures/role_eccentricity.pdf}
+    \caption{An illustration of the effect of eccentricity on the detectability of a LISA source.
+The three sets of points are coloured by their eccentricity and each individual point corresponds to a harmonic frequency, where its height above the curve gives its SNR.
+We annotate each set of points with its total SNR and overlay the LISA sensitivity curve.
+The dotted vertical lines indicate the frequency at which the majority of the gravitational wave signal is concentrated.}
+    \label{fig:role_eccentricity}
+\end{figure}
+
+From Fig.~\ref{fig:role_eccentricity}, we can better understand why a source with $e = 0.9$ has a lower SNR than the same source with $e = 0.6$.
+From the dotted lines, we can note that the signal from the $e = 0.9$ source is concentrated at a frequency of around $4 \times 10^{-2} \unit{Hz}$.
+The LISA sensitivity at this point is much weaker than the $6 \times 10^{-3} \unit{Hz}$ at which the $e =0.6$ source is concentrated.
+Therefore, although the strain from a more eccentric binary is stronger, the SNR is lower due to the increased noise in the LISA detector.
+
+Overall, we can therefore conclude that for LISA sources of this nature, higher eccentricity will produce more detectable binaries only if the orbital frequency is not already at or above the minimum of the LISA sensitivity curve.
+
+\begin{figure}[htb]
+    \centering
+    \includegraphics[width=\columnwidth]{figures/merger_time.pdf}
+    \caption{The merger time for a binary with both a primary and secondary mass of $10 \unit{M_{\odot}}$ over different eccentricities and orbital frequencies.}
+    \label{fig:merger_time}
+\end{figure}
+
+Another consideration for more massive binaries is whether the increased eccentricity will cause the binary to merge before the mission ends, which would cause a significant decrease in signal-to-noise ratio.
+We can also use \lw{} to find how the merger time of a source varies with frequency and eccentricity over a grid of sources.
+
+We plot the results of this calculation in Figure~\ref{fig:merger_time}.
+This plot shows that for most eccentricities the merger is time is largely determined by the orbital frequency.
+However, for high eccentricities ($e > 0.8$), the eccentricity significantly reduces the merger time.
+
+\subsection{Compare gravitational wave detectors\texorpdfstring{ - \tutorialLink{https://legwork.readthedocs.io/en/latest/demos/CompareSensitivityCurves.html}}{}}
+
+It may also be useful to consider how changing the specifications of the LISA detector, or using a different detector entirely, could affect the SNR of a particular source.
+\lw{} is capable of adjusting the LISA mission specifications or using a different sensitivity curve and thus we can use it to explore these differences.
+
+As a first step, we can use \lw{} to plot a series of sensitivity curves in Figure~\ref{fig:detector_sc_compare}.
+We show the LISA sensitivity curve for the default 4 year mission length but also illustrate how the curve changes for shorter mission lengths.
+At 0.5 and 2 years, we see a stronger noise level around $3 \unit{mHz}$ as a result of the increased Galactic confusion noise.
+This noise decreases with increasing mission length since more individual foreground sources can be resolved and thus removed from the confusion noise.
+We also see that using an approximated response function smooths out the sensitivity curve at higher frequencies.
+Finally, the TianQin curve is higher than the 4 year LISA curve until around $5 \unit{mHz}$, beyond which it has a lower noise level.
+
+\begin{figure}[htb]
+    \centering
+    \includegraphics[width=\columnwidth]{figures/detector_sc_compare.pdf}
+    \caption{The strain spectral density of the LISA detector with different specifications \citep{Robson+2019} and the TianQin detector \citep{Huang+2020}.
+We show the LISA curve for three different mission lengths and once with an approximate response function.}
+    \label{fig:detector_sc_compare}
+\end{figure}
+
+Although comparing the sensitivity curves would suffice for a stationary and circular source (since it would remain at a single frequency), \lw{} can also be used to see how the relative SNR between two detectors changes over a range of eccentricities and frequencies.
+
+Using \lw{}, we can compute the SNR of a grid of sources (spanning a range of frequencies and eccentricities) for both detectors.
+In Figure~\ref{fig:detector_snr_ratio}, we show the ratio of the SNR in LISA to the SNR in TianQin.
+This plot shows that for circular binaries, the SNR of the source in LISA is stronger up to an orbital frequency of approximately $2.5 \unit{mHz}$, beyond which the SNR of the source is stronger in TianQin.
+This transition frequency becomes lower with increasing eccentricity as one would expect since eccentric sources emit more at higher harmonics and thus higher frequencies.
+
+\begin{figure}[htb]
+    \centering
+    \includegraphics[width=\columnwidth]{figures/detector_snr_ratio.pdf}
+    \caption{The ratio of the SNR in LISA (for a four year mission) to the SNR in TianQin.
+The dashed line indicates the transition at which the SNR is equal in both detectors.
+We annotate the regions in which either detector has a higher SNR and also annotate the mass and distance of each source in the grid.}
+    \label{fig:detector_snr_ratio}
+\end{figure}
+
+\subsection{Track SNR of a binary over time\texorpdfstring{ - \tutorialLink{https://legwork.readthedocs.io/en/latest/demos/SNROverTime.html}}{}}
+
+As a binary inspirals its orbital frequency and eccentricity change and this in turn affects the SNR of the binary.
+For this use case we will demonstrate how \lw{} can be used to track the evolution of these parameters and pinpoint the moment at which a binary becomes detectable.
+
+Let's consider a binary with the following initial parameters
+\begin{align*}
+    m_1 &= m_2 = 15 \unit{M_{\odot}},\ d = 20 \unit{kpc},\\
+    f_{\rm orb, i} &= 3 \times 10^{-5} \unit{Hz},\ e_i = 0.5,
+\end{align*}
+and use \lw{} to evolve the system until 100 years before its merger with 1000 linearly spaced timesteps, recording the eccentricity and frequency at each timestep.
+
+We plot this evolution of the eccentricity and frequency in the top two panels of Fig.~\ref{fig:snr_over_time} as a function of the time before the merger.
+We see that the binary circularises and increases its orbital frequency as it inspirals as we would expect.
+
+To take this a step further, we can consider the binary at each timestep to be a separate source with the current eccentricity and frequency.
+It is then trivial to use \lw{} to calculate the SNR for each of these `sources' and thus attain the SNR evolution, which we plot in the last panel of Fig.~\ref{fig:snr_over_time}.
+
+We see that the SNR increases monotonically over time and sharply increases as the binary approaches its merger.
+Around $1 \unit{Myr}$ before the merger, the SNR reaches the detection threshold and thus could then be seen by a 4-year LISA mission.
+
+Note that \lw{} could also be used in this way to find the SNR of any system in which the orbital evolution is known.
+Thus for a triple system or a binary experiencing gas drag (as long the evolution of the eccentricity and orbital frequency is known) \lw{} is entirely capable of calculating the SNR evolution.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=\columnwidth]{figures/snr_over_time.pdf}
+    \caption{The evolution of a binary system's eccentricity (top), orbital frequency (middle) and signal-to-noise ratio (bottom).
+Each panel is annotated with the constant parameters of the system.
+The SNR is calculated for a 4-year LISA mission.
+We annotate in  a line the bottom panel at $\mathrm{SNR} = 7$ to highlight the moment at which the source becomes detectable.}
+    \label{fig:snr_over_time}
+\end{figure}
+
+\subsection{LISA verification binaries\texorpdfstring{ - \tutorialLink{https://legwork.readthedocs.io/en/latest/demos/VerificationBinaries.html}}{}}
+\citet{Kupfer+2018} presents the LISA verification binaries, a collection of known binary systems that have gravitational-waves that are strong enough to be detected by LISA.
+In \lw{}, we provide easy access to this data through the \href{https://legwork.readthedocs.io/en/latest/api/legwork.source.VerificationBinaries}{\color{\lwColour}{\texttt{VerificationBinaries}}} class, which is a subclass of \href{https://legwork.readthedocs.io/en/latest/api/legwork.source.Source}{\color{\lwColour}{\texttt{Source}}}.
+This means that the class works identically to \texttt{source} but has the verification binary data preloaded into the variables.
+In addition to the base variables, this class also includes the designation of each binary and the SNR that \citet{Kupfer+2018} computed\footnote{We note that this SNR differs from the SNR that \lw{} gives for each binary.
+This is because \citet{Kupfer+2018} run a full LISA simulation for these binaries, whilst we follow the orbit-averaged approach (see Section~\ref{sec:amplitude_mod}), since the former would be intractable for any large number of sources.}.
+
+As an example of how you could use this data, we use the \texttt{VerificationBinaries} class to plot the sources on the LISA sensitivity curve with the SNR calculated by \citet{Kupfer+2018} for a 4-year LISA mission and colour the binaries by their primary mass.
+We see that the verification binaries tend to be detected between $1$-$10 \unit{mHz}$ and have masses estimated to be between $0.1$-$1 \unit{M_{\odot}}$.
+
+\begin{figure}[htb]
+    \centering
+    \includegraphics[width=\columnwidth]{verification_binaries_on_sc.pdf}
+    \caption{The LISA verification binaries from \citet{Kupfer+2018} plotted on the LISA sensitivity curve \citep{Robson+2019} for a 4-year LISA mission. Points are coloured by their primary mass.}
+    \label{fig:verification_binaries_on_sc}
+\end{figure}
+
 \section{Conclusion \& Summary}\label{sec:summary}
-
-\todo{}
+We have presented \lw{}, a package designed to aid in calculations for stellar-origin binary sources of mHz gravitational-wave observatories like LISA.
+We outlined the implementation of orbital evolution due to gravitational-wave emission, gravitational wave strain, SNR, and visualisation modules and provided a detailed derivation for each of the equations required for each module.
+Finally, we provided several use case examples for how \lw{} can be used to better understand the detectability of compact-object binaries.
 
@@
     % People
-    We are grateful to Valeria Korol, Tyson Littenberg, Alberto Sesana, Ilya Mandel, Mike Lau, Lieke van Son, Floor Broekgaarden, Stephen Justham, Will Farr, the CCA GW group, the BinCosmos group and the COMPAS group for stimulating discussions that influenced and motivated us to complete this project.
+    We are grateful to Valeria Korol, Tyson Littenberg, Alberto Sesana, Stas Babak, Ilya Mandel, Mike Lau, Lieke van Son, Floor Broekgaarden, Stephen Justham, Will Farr, Tom Callister, the CCA GW group, the BinCosmos group and the COMPAS group for stimulating discussions that influenced and motivated us to complete this project.
 We thank the BinCosmos group for testing an early version of the package and providing useful feedback.
@@
 We further acknowledge the Black Hole Initiative funded by a generous contribution of the John Templeton Foundation and the Gordon and Betty Moore Foundation.
+The Flatiron Institute is funded by the Simons Foundation.
 \end{acknowledgements}

### 2021-11-12 src/figures/merger_time.py
update merger time plot

@@ -28,11 +28,11 @@ m_2 = np.repeat(10, len(f_range) * len(e_range)) * u.Msun
 
 F, E = np.meshgrid(f_range, e_range)
 
-t_merge = lw.evol.get_t_merge_ecc(ecc_i=E.flatten(), f_orb_i=F.flatten(), m_1=m_1, m_2=m_2).reshape(F.shape)
-
+t_merge = lw.evol.get_t_merge_ecc(ecc_i=E.flatten(), f_orb_i=F.flatten(), m_1=m_1, m_2=m_2,
+                                  small_e_tol=0.15, large_e_tol=0.9999).reshape(F.shape)
 fig, ax = plt.subplots()
 
-cont = ax.contourf(F, E, np.log10(t_merge.to(u.yr).value), cmap="plasma_r", levels=np.linspace(-8, 10, 19))
+cont = ax.contourf(F, E, np.log10(t_merge.to(u.yr).value), cmap="plasma_r", levels=np.linspace(-6, 10, 17))
 cbar = fig.colorbar(cont, label=r"Merger time, $\log_{10} (t_{\rm merge} / {\rm yr})$")
 ax.set_xscale("log")
 
@@ -49,6 +49,10 @@ ax.annotate(mass_string, xy=(0.5, 0.04), xycoords="axes fraction", fontsize=0.6*
 
 ax.set_xlabel(r"Orbital frequency, $f_{\rm orb} \, [\rm Hz]$")
 ax.set_ylabel(r"Eccentricity, $e$")
+
+mission_length = ax.contour(F, E, np.log10(t_merge.to(u.yr).value), levels=np.log10([4]),
+                            linestyles="--", linewidths=2)
+ax.clabel(mission_length, fmt={np.log10(4): r"$t_{\rm merge} = 4\,{\rm years}$"}, fontsize=0.7*fs, manual=[(1e-2, 0.5)])
 
 ax.set_rasterization_zorder(10000)
 

### 2021-11-12 src/ms.tex
need full path
update after SdM final comments

@@
 
-\title{LEGWORK: LISA Evolution and Gravitational Wave Orbit Kit}
+\title{LEGWORK: A python package for computing the evolution and detectability \\ of stellar-origin gravitational-wave sources with space-based detectors}
 
@@
 \begin{abstract}
-    We present \lw{}, a Python package for making predictions about stellar-origin gravitational wave sources and their detectability in LISA and other space-based gravitational wave detectors.
+% Original
+%    We present \lw{}, a Python package for making predictions about stellar-origin gravitational wave sources and their detectability in LISA and other space-based gravitational wave detectors.
 \lw{} can be used to evolve sources over time, calculate gravitational wave strains, compute signal-to-noise ratios and visualise the results.
@@
 We additionally explain in detail the derivation of the equations behind \lw{} in order to clarify some conflicts currently present in the literature.
+
+% -------------
+
+% Selma version
+% We present \lw{} (LISA Evolution and Gravitational Wave Orbit Kit) an open-source Python package developed to aid studies of stellar-origin gravitational wave sources detectable by space-based gravitational wave detectors such as LISA.
+% %
+% This package can be used to follow the gravitational wave driven inspiral of a compact binary consisting of, for example, white dwarfs, neutron stars and/or stellar-mass black holes.
+We calculate the gravitational wave strains using the post-Newtonian approximations and estimate the signal-to-noise ratio for a given detector sensitivity.
+We optimised \lw{} to make it feasible to make predictions for populations of tens-of-millions of sources.
+In principle, \lw{} can be used for any systems with a user-specified orbital evolution, such as those affected by a third object or gas drag.
+% %
+% This paper describes the package and presents several use cases.
+We provide the derivations behind the expressions and we identify and clarify some discrepancies in the expressions presented in earlier literature.
+We hope that \lw{} will enable and accelerate future studies triggered by the rapidly growing interest in gravitational wave sources.
+
+We present \lw{} (LISA Evolution and Gravitational Wave Orbit Kit), an open-source Python package for making predictions about stellar-origin gravitational wave sources and their detectability in LISA or other space-based gravitational wave detectors.
+\lw{} can be used to evolve the orbits of sources due to gravitational wave emission, calculate gravitational wave strains (using post-Newtonian approximations), compute signal-to-noise ratios and visualise the results.
+It can be applied to a variety of potential sources, including binaries consisting of white dwarfs, neutron stars and black holes.
+Although we focus on double compact objects, in principle \lw{} can be used for any system with a user-specified orbital evolution, such as those affected by a third object or gas drag.
+We optimised the package to make it efficient for use in population studies which can contain tens-of-millions of sources.
+This paper describes the package and presents several potential use cases.
+We explain in detail the derivations of the expressions behind the package as well as identify and clarify some discrepancies currently present in the literature.
+We hope that \lw{} will enable and accelerate future studies triggered by the rapidly growing interest in gravitational wave sources.
 \end{abstract}
 
-\keywords{gravitational waves, LISA}
+\keywords{open source software, gravitational waves, gravitational wave detectors, compact objects, orbital evolution, white dwarfs, neutron stars, stellar mass black holes }
 
@@
 The planned space-based gravitational wave detector LISA (Laser Interferometer Space Antenna) will present an entirely new view of gravitational waves by focusing on lower frequencies ($10^{-5} < f / \unit{Hz} < 10^{-1}$) than ground-based detectors.
-This will enable the study of many source classes that are undetectable with ground-based detectors including mergers of supermassive black holes that are undetectable with ground-based detectors \citep[e.g.][]{Begelman+1980, Klein+2016, Bellovary2019}, extreme mass ratio inspirals \citep[e.g.,][]{Berti2006, Barack2007, Babak2017, Moore2017}, and cosmological GW backgrounds \citep[e.g.,][]{Bartolo2016, Caprini2016, Caldwell2019}.
+This will enable the study of many new source classes including mergers of supermassive black holes \citep[e.g.][]{Begelman+1980, Klein+2016, Bellovary2019}, extreme mass ratio inspirals \citep[e.g.,][]{Berti2006, Barack2007, Babak2017, Moore2017}, and cosmological GW backgrounds \citep[e.g.,][]{Bartolo2016, Caprini2016, Caldwell2019}.
 However, this frequency regime is also of interest for the detection of local stellar-mass binaries during their inspiral phase.
@@
 
-The potential to detect stellar-origin sources with LISA has been studied in the past \citep[e.g.][]{Nelemans+2001, Belczynski+2010}.
-More recently, the direct detection of gravitational waves with ground-based detectors has led to renewed interest in this topic with many recent papers addressing the issue \citep[e.g.][]{Christian+2017, Kremer+2017, Kremer+2018, Korol+2017, Korol+2018, Korol+2019, Korol+2020, Lamberts+2018, Lamberts+2019, Fang+2019, Andrews+2020, Lau+2020, Breivik+2020, Breivik+2020a, Roebber+2020, Chen+2020, Sesana+2020}.
+The potential to detect stellar-origin sources with LISA has been studied in the past \citep[e.g.][]{Nelemans+2001, Liu+2009, Liu+2014, Ruiter+2010, Belczynski+2010, Yu+2010, Nissanke+2012}.
+More recently, the direct detection of gravitational waves with ground-based detectors has led to renewed interest in this topic with many recent papers addressing the issue \citep[e.g.][]{Korol+2017, Korol+2018, Korol+2019, Korol+2020, Christian+2017, Kremer+2017, Kremer+2018, Lamberts+2018, Lamberts+2019, Fang+2019, Andrews+2020, Lau+2020, Breivik+2020, Breivik+2020a, Roebber+2020, Chen+2020, Sesana+2020, Shao+2021}.
 
@@
 
-\lw{} is a Python package designed to streamline the process of making predictions of LISA detection rates for stellar-origin binaries such that it is as fast, reliable and simple as possible.
+\lw{} is an open-source Python package designed to streamline the process of making predictions of LISA detection rates for stellar-origin binaries such that it is as fast, reliable and simple as possible.
 This goal makes \lw{} unique among other implementations of gravitational-wave tools in the literature, which focus on a more broad coverage of the gravitational-wave spectrum and source classes, rather than an optimised approach for certain sources.
@@
 
-Specifically, we implement the expressions by \citet{Peters+1963} and \citet{Peters+1964} for the evolution of binary orbits due to the emission of gravitational waves, equations for the strain amplitudes and signal-to-noise ratios of binaries from various papers \citep[e.g.][]{Flanagan+1998, Finn+2000, Cornish2003, Barack+2004, Moore+2015} and approximations for the LISA and TianQin sensitivity curves given in \citet{Robson+2019} and \citet{Huang+2020} respectively.
+Specifically, we implement the post-Newtonian expressions by \citet{Peters+1963} and \citet{Peters+1964} for the evolution of binary orbits due to the emission of gravitational waves, equations for the strain amplitudes and signal-to-noise ratios of binaries from various papers \citep[e.g.][]{Flanagan+1998, Finn+2000, Cornish2003, Barack+2004, Moore+2015} and approximations for the LISA and TianQin sensitivity curves given in \citet{Robson+2019} and \citet{Huang+2020} respectively.
 
@@
 At the same time, with our thorough online documentation, derivations and tutorials, we hope \lw{} can make this functionality more accessible to the broader scientific community.
+
+\lw{} has been adopted in multiple studies.
+Wagg et al.\ (in prep) investigates several populations of potential LISA sources (double black holes, black hole neutron stars and double neutron stars).
+They use \lw{} to evolve each synthesised source over the age of the Milky Way, make predictions about the LISA detectable population and explore how it varies with different binary physics assumptions.
+Additionally, Thiele et al.\ (in prep) examines the implications of assuming a metallicity-dependent binary fraction for the formation of close double white dwarfs (WDWDs) in the LISA frequency band.
+They use \lw{} to calculate the SNR of WDWDs and, in particular, apply a custom noise model that combines the LISA sensitivity curve from \citet{Robson+2019} with a new fit for the Galactic confusion noise based on their WDWD population.
 
@@
 
+The \lw{} package is composed of seven modules that each focus on a particular aspect of calculations useful for gravitational wave sources that are detectable by space-based detectors.
+In Fig.~\ref{fig:package_overview}, we illustrate the general structure of the package with each of its modules.
+The \texttt{source} module is the central module of the package and provides an simple interface to the functions in the rest of the modules.
+For more complex analyses, users may want to interact directly with individual modules, particularly those in the top row of Fig.~\ref{fig:package_overview} as they comprise the core functionality of \lw{}.
+Below we explain the capabilities of each module in detail.
+
 \begin{figure}
@@
 
-The \lw{} package is composed of seven modules that each focus on a particular aspect of calculations useful for LISA gravitational wave sources.
-In Fig.~\ref{fig:package_overview}, we illustrate the general structure of the package with each of its modules.
-The source module is the central module of the package and provides an simple interface to the functions in the rest of the modules.
-For more complex analyses, users may want to interact directly with individual modules, particularly those in the top row of Fig.~\ref{fig:package_overview} as they comprise the core functionality of \lw{}.
-Below we explain the capabilities of each module in detail.
-
 \lwModLink{evol} handles the orbital evolution of a binary due to the emission of gravitational waves.
@@
 \lwModLink{strain} contains two functions that compute a binary's gravitational wave strain and characteristic strain amplitude respectively.
-Each of these functions is capable of computing the strain for a 3-dimensional array of binaries at any number of timesteps and evaluated at any number of frequency harmonics.
+Each of these functions is capable of computing the strain for an array of binaries at any number of timesteps and evaluated at any number of frequency harmonics.
 We discuss the relevant equations in Sec.~\ref{sec:deriv_strain}.
@@
 \lwModLink{psd} is used for evaluating the effective noise power spectral density of a detector at different frequencies.
-The module contains both the LISA and TianQin sensitivity curves that can be tweaked by adjusting parameters such as the observation time, confusion noise and even the arm length.
+The module currently contains the LISA and TianQin sensitivity curves that can be tweaked by adjusting parameters such as the observation time, confusion noise and even the arm length.
 Additionally, this module allows the user to specify a custom detector sensitivity curve.
@@
 
-We developed \lw{} with an emphasis on increasing the efficiency of these computations in order to make large scale simulations more tractable.
-As a simple first step, we ensured that the entirety of \lw{} is vectorised and thus scales well with larger populations.
+We developed \lw{} with an emphasis on increasing the efficiency of these computations in order to make simulations of large populations of systems tractable.
+We ensured that the entirety of \lw{} is vectorised and thus scales well with larger populations.
 In addition, we made a several specific optimisations to further increase the speed of calculations.
+
+Firstly, we found that the runtime of calculating strains and SNRs for large populations of sources was mainly limited by the computation of (1) the relative gravitational-wave power in each harmonic for eccentric systems (see Eq.~\ref{eq:g(n,e)}) (2) the sensitivity curve of the given detector.
+Therefore, in order to significantly reduce the runtime of strain and SNR computations, by default \lw{} automatically interpolates these functions upon instantiation of any \texttt{Source} class with a large number of sources.
+Thereafter all functions use the tabulated values instead of calculating them exactly.
 
@@
 
-Lastly, as a simple (yet thoroughly effective) optimisation, we interpolate (1) $g(n, e)$, which is a complicated combination of Bessel functions used in several calculations (see Eq.~\ref{eq:g(n,e)}) (2) the given sensitivity curve $S_{\rm n}(f)$.
-This significantly reduces the runtime of most strain and SNR calculations for large populations of sources.
-
 \section{Derivations}\label{sec:derivations}
-In this section, we present a derivation of the equations using in \lw{}.
+In this section, we present a derivation of the equations used in \lw{}.
 We emphasise that these are not new derivations, conversely, they are in fact given frequently in the literature.
-However, they are often incomplete, unclear or contain spurious constant factors that arise from invalid combinations of previous work.
+However, they are often incomplete, unclear and, in some cases, contain spurious constant factors that arise from invalid combinations of previous work.
 Here, we aim to present a clear, clean and concise explanation of the expressions we use in \lw{}.
 
-A \docsIcon{} symbol in an equation will link to the relevant \lw{} documentation for the implementation of that equation, which additionally contains a link to exact code used to reproduce the equation.
+A \docsIcon{} symbol in an equation directly links to the relevant online \lw{} documentation for the implementation of that equation, which additionally contains a link to exact code used to reproduce the equation.
 These derivations are also given in more detail in the \lw{} documentation \href{https://legwork.readthedocs.io/en/latest/notebooks/Derivations.html}{here}, where we show each of the intervening steps in more detail.
@@
 \end{equation}
-where $m_1$ and $m_2$ are the primary and secondary masses of the double compact object.
+where $m_1$ and $m_2$ are the primary and secondary masses of the binary.
 
@@
 \end{equation}
-or inversely
+where $G$ is the gravitational constant. Inversely we could write
 \begin{equation}{\lwFuncURL{utils}{get_a_from_f_orb}}
@@
 
-For eccentric binaries, we need to consider all frequency harmonics of gravitational-wave emission. These are defined such that the $n^{\rm th}$ harmonic frequency is
+For circular binaries, gravitational-wave emission occurs at twice the orbital frequency ($f_{\rm GW} = 2 f_{\rm orb}$).
+However, for eccentric binaries, we need to consider all frequency harmonics of gravitational-wave emission.
+These are defined such that the $n^{\rm th}$ harmonic frequency is
 \begin{equation}{}
@@
 It will be important to know the relative gravitational-wave power radiated into the $n^{\rm th}$ harmonic for a binary with eccentricity $e$ for the following strain and SNR calculations.
-This is given by \citep[][Eq.\,20]{Peters+1963}
+This is given by \citet[][Eq.\,20]{Peters+1963}
 \begin{equation}{\lwFuncURL{utils}{peters_g}}
@@
             +\big(1-e^{2}\big)\Big[&J_{n-2}(n e)-2 J_{n}(n e) \\
-            &+J_{n+2}(n e)\Big]^{2} \\
+            &+J_{n+2}(n e)\Big]^{2}
             \end{aligned}\\
@@
 \begin{equation}{\lwFuncURL{utils}{beta}}
-    \beta(m_1, m_2) = \frac{64}{5} \frac{G^3}{c^5} m_1 m_2 (m_1 + m_2),
+    \beta(m_1, m_2) \equiv \frac{64}{5} \frac{G^3}{c^5} m_1 m_2 (m_1 + m_2),
     \label{eq:beta_peters}
 \end{equation}
-where $m_1$ is the primary mass and $m_2$ is the secondary mass. This gives the semi-major axis of a circular binary as a function of time, $t$, as \citep[][Eq.~5.9]{Peters+1964}
+where $c$ is the speed of light, $m_1$ is the primary mass and $m_2$ is the secondary mass.
+This gives the semi-major axis of a circular binary as a function of time, $t$, as \citep[][Eq.~5.9]{Peters+1964}
 \begin{equation}{\lwFuncURL{evol}{evol_circ}}
@@
 The orbital evolution is more complex for eccentric binaries since the semi-major axis and eccentricity both evolve simultaneously and depend on one another.
-These equations cannot be solved analytically and require numerical integration.
+The final expression cannot be solved analytically and require numerical integration.
 The semi major axis, $a$, and eccentricity, $e$, are related as \citep[][Eq.~5.11]{Peters+1964}
@@
 \end{align}
-\noindent The standard threshold employed by \lw{} for small eccentricities is $e=0.01$ and for large eccentricities is $e=0.99$, though we note that this can be customised by the user as well.
+\noindent The standard threshold employed by \lw{} for small eccentricities is $e = 0.15$ and for large eccentricities is $e=0.9999$ (as this approximates $t_{\rm merge}$ with an error below roughly 2\%), though we note that this can be customised by the user if desired.
+
+In addition, we implement the fit to Eq.~\ref{eq:t_merge_eccentric} from \citet{Mandel+2021} that approximates the merger time as
+\begin{equation}{\lwFuncURL{evol}{t_merge_mandel_fit}}
+    \begin{split}
+        t_{\rm merge} \approx& t_{\rm merge, circ} (1 - e^2_0)^{7/2} \\
+    &\times(1 + 0.27 e_0^{10} + 0.33 e^{20}_0 + 0.2 e_0^{1000} ),
+    \end{split}
+\end{equation}
+which gives $t_{\rm merge}$ with an error below 3\% for eccentricities below $0.9999$.
+We additionally add a rudimentary polynomial fit to further reduce this error to below $0.5\%$.
+The user may specify whether to use this fit or perform the full integral when calculating merger times in \lw{}.
 
@@
 The strength of a gravitational wave in a detector at any one moment is determined by the strain amplitude, $h_0$.
-However, for the LISA mission, the signal can be present in the detector for many years.
+However, for stellar-origin sources at mHz frequencies, the signal can be present in the detector for many years.
 This means that, the $n^{\rm th}$ harmonic of the binary will spend approximately $f_n / \dot{f}_n$ seconds (or $f_n^2 / \dot{f}_n$ cycles) in the vicinity of a frequency $f_n$ \citep{Finn+2000}.
@@
 
-Therefore, to account for the integration of the signal over the mission, we can introduce the `characteristic' strain amplitude of the $n^{\rm th}$ harmonic \citep[e.g][]{Finn+2000, Moore+2015}\footnote{Note that this is factor of 2 different from \citet{Finn+2000}.
+Therefore, to account for the integration of the signal over the mission, we instead use the `characteristic' strain amplitude of the $n^{\rm th}$ harmonic \citep[e.g][]{Finn+2000, Moore+2015}\footnote{Note that this is factor of 2 different from \citet{Finn+2000}.
 This is because the factor of 2 is already included in the \citet{Robson+2019} sensitivity curve and so is removed here.}
@@
 \end{equation}
-where $D_L$ is the luminosity distance to the binary, $\dot{E}_n$ is the power radiated in the $n^{\rm th}$ harmonic and $\dot{f}_n$ is the rate of change of the $n^{\rm th}$ harmonic frequency.
+where $D_L$ is the luminosity distance to the source (note that for Milky Way sources this is simply the distance to the source), $\dot{E}_n$ is the power radiated in the $n^{\rm th}$ harmonic and $\dot{f}_n$ is the rate of change of the $n^{\rm th}$ harmonic frequency.
 
@@
 where $g(n, e)$ is given in Eq.~\ref{eq:g(n,e)}.
-By substituting $a$ for $f_{\rm orb}$ (Eq.~\ref{eq:kepler3rd_reverse}) and applying the definition of the chirp mass (Eq.~\ref{eq:chirpmass}) we obtain a more useful form for making gravitational wave predictions
+By substituting $a$ for $f_{\rm orb}$ (using Eq.~\ref{eq:kepler3rd_reverse}) and applying the definition of the chirp mass (Eq.~\ref{eq:chirpmass}) we obtain a more useful form for making gravitational wave predictions
 \begin{equation}{}
@@
 \end{equation}
-With definitions of both $\dot{E}_n$ and $\dot{f}_n$, we are now in a position to find an expression for the characteristic strain by plugging Eq.~\ref{eq:edot} and Eq.~\ref{eq:fdot} into Eq.~\ref{eq:char_strain}:
+With definitions of both $\dot{E}_n$ and $\dot{f}_n$, we are now in a position to find an expression for the characteristic strain by plugging Eq.~\ref{eq:edot} and Eq.~\ref{eq:fdot} into Eq.~\ref{eq:char_strain_dedf}:
 \begin{equation}{\lwFuncURL{strain}{h_c_n}}
@@
 Because the LISA detectors are not stationary and instead follow an Earth-trailing orbit, the antenna pattern of LISA is not isotropically distributed or stationary.
-For sources that have a known position, inclination, and polarisation, we can consider the amplitude modulation of the strain due to the average motion of LISA's orbit.
+For sources that have unknown positions, inclinations, and polarisations, we use an average for the detector.
+However, for sources where these quantities are known we can consider the amplitude modulation of the strain due to the average motion of LISA's orbit.
+
+We write that the position of the source on the sky is given by the ecliptic coordinates ($\theta$, $\phi$), the inclination of a source is $\iota$ and the polarisation of a source (determined by its orientation relative to the detector) is given by $\psi$.
 We closely follow the results of \citet{Cornish2003} to write down the amplitude modulation as
@@
 \end{equation}
-In the equations above, the inclination is given by $\iota$, the right ascension and declination are given by $\phi$ and $\theta$ respsectively, and the polarisation is given by $\psi$.
-
 The orbital motion of LISA smears the source frequency by roughly $10^{-4}\,\rm{mHz}$ due to the antenna pattern changing as the detector orbits, the Doppler shift from the motion, and the phase modulation from the $+$ and $\cross$ polarisations in the antenna pattern.
@@
 
-We note that since the orbit averaging is carried out in Fourier space, this requires the frequency to be monochromatic and thus is only implemented in \lw{} for quasi-circular binaries.
+We note that since the orbit averaging is carried out in Fourier space, this requires the frequency to be monochromatic and thus is only implemented in \lw{} for quasi-circular binaries (as eccentric systems emit at many frequency harmonics).
 We also note that since the majority of the calculations in \lw{} are carried out for the full position, polarisation, and inclination averages, we place a pre-factor of $5/4$ on the amplitude modulation in the software implementation to undo the factor of $4/5$ which arises from the averaging of Equations~\ref{eq:response_fplus} and \ref{eq:response_fcross}.
@@
 \end{equation}
-where $L = 2.5 \unit{Gm}$ is detector arm length, $f^* = c / 2 \pi L = 19.09 \unit{mHz}$ is the transfer frequency, 
+where $L = 2.5 \unit{Gm}$ is detector arm length, $f_* = c / 2 \pi L = 19.09 \unit{mHz}$ is the transfer frequency, 
 \begin{equation}{}
@@
 \end{equation}
-is the galactic confusion noise \citep[][Eq.~14]{Robson+2019}, where the amplitude $A$ is fixed as $9 \times 10^{-45}$ and the various parameters change over time:
-$$
-    \begin{array}{|c|c|c|c|c|}
-        \hline
-        & 6 \mathrm{mo} & 1 \mathrm{yr} & 2 \mathrm{yr} & 4 \mathrm{yr} \\
-        \hline
-        \alpha & 0.133 & 0.171 & 0.165 & 0.138 \\
-        \beta & 243 & 292 & 299 & -221 \\
-        \kappa & 482 & 1020 & 611 & 521 \\
-        \gamma & 917 & 1680 & 1340 & 1680 \\
-        f_{k} & 0.00258 & 0.00215 & 0.00173 & 0.00113 \\
-        \hline
-    \end{array}
-$$
+is the galactic confusion noise \citep[][Eq.~14]{Robson+2019}, where the amplitude $A$ is fixed as $9 \times 10^{-45}$ and the various parameters change over time and are listed in \citealt[][Table~1]{Robson+2019}.
+\lw{} allows the user to opt to use the \citet{Robson+2019} confusion noise, a custom function for the confusion noise or to remove the confusion noise entirely.
 
@@
 
-\subsection{SNR for 6-link LISA {\normalfont (\texorpdfstring{\lwModLink{snr}}{snr})}}\label{sec:deriv_snr}
-
+\subsection{SNR for LISA {\normalfont (\texorpdfstring{\lwModLink{snr}}{snr})}}\label{sec:deriv_snr}
 We note that this section draws heavily from \citet{Flanagan+1998} Section II C.
@@
 \subsubsection{Defining general SNR}
-In order to calculate the signal to noise ratio for a given source of gravitational waves (GWs) in the LISA detector, we need to consider the following parameters:
+In order to calculate the signal to noise ratio for a given source of gravitational waves (GWs) in a 6-link LISA detector, we need to consider the following parameters:
 
@@
 \end{align}
-where $\tilde{s}(f)$ is the Fourier transform of the signal, $s(t)$, and $P_{\rm n}(f)$ is the one sided power spectral density of the noise defined as as $\langle n(t)^{\star}n(t)\rangle = \int_0^{\infty} \frac{1}{2}P_{\rm n}(f) df$ \citep[c.f.][Eq.\,2]{Robson+2019}.
+where $\tilde{s}(f)$ is the Fourier transform of the signal, $s(t)$, and $P_{\rm n}(f)$ is the one-sided power spectral density of the noise defined as as $\langle n(t)^{\star}n(t)\rangle = \int_0^{\infty} \frac{1}{2}P_{\rm n}(f) df$ \citep[c.f.][Eq.\,2]{Robson+2019}.
 Here, $\tilde{s}(f)$ is implicitly also dependent on $D_L, \theta, \phi, \psi, \iota,$ and $\beta$ as
@@
 
-For an evolving and eccentric binary, no approximate can be made and the SNR is found using Eq.~\ref{eq:snr_general}.
+For an evolving and eccentric binary, no approximation can be made and the SNR is found using Eq.~\ref{eq:snr_general}.
 
@@
 
-The most fundamental use case of \lw{} is to compute the SNR of a binary system in LISA.
+The most fundamental use case of \lw{} is to compute the SNR of an individual binary system.
 This can be accomplished in \lw{} with only two lines of code - one line to set up the source and another to compute the SNR.
@@
 where $m_1, m_2$ are the primary and secondary masses, $d$ is the distance to the source, $f_{\rm orb}$ is the orbital frequency and $e$ is the eccentricity.
-As we don't specify a position, polarisation or inclination, \lw{} will calculate the SNR averaged over these quantities.
-One can now instantiate a source in \lw{} using these parameters (leaving the LISA mission parameters as the default values, such that we compute the SNR for a 4-year LISA mission).
+As we do not specify a position, polarisation or inclination, \lw{} will calculate the SNR averaged over these quantities.
+One can now instantiate a source in \lw{} using these parameters (leaving the mission parameters as the default values, such that we compute the SNR for a 4-year LISA mission).
 As shown in the linked demo, \lw{} quickly computes that the SNR of this binary is $4.49$.
@@
 
-Moreover, this can be generalised to a population of many binary systems with ease.
+This can be generalised to a population of many binary systems with ease.
 Instead of inputting single values for each parameter, one can input arrays of values where each entry corresponds to a different binary.
@@
 
-The role of eccentricity is an important concept to consider in the detection of gravitational waves with LISA as sources can still have significant eccentricity during their inspiral phase.
+The role of eccentricity is important to consider in the detection of gravitational waves with LISA and other space-based detectors, as sources can still have significant eccentricity during their inspiral phase.
 A high eccentricity has two major effects on the SNR of a gravitational wave source in LISA and we can investigate this using \lw{}.
 
-Let's use three toy sources that are identical apart from their eccentricities, $e_i$.
+Let's consider three hypothetical systems that are identical apart from their eccentricities, $e_i$.
 \begin{align*}{}
@@
 \end{align*}
-Using \lw{} to calculate their signal-to-noise ratios, $\rho_i$, we find
+Using \lw{} to calculate their signal-to-noise ratios (for a 4-year LISA mission), $\rho_i$, we find
 \begin{equation*}{}
@@
 The reason for this is that eccentric binaries emit gravitational waves at many harmonic frequencies (unlike circular binaries, which emit predominantly twice the orbital frequency).
-This leads to the gravitational wave signal being diluted over many frequencies higher than the orbital frequency, where the higher the eccentricity, the more harmonics are required to capture all of the gravitational luminosity \citep[see][Fig.\,3]{Peters+1963}.
+This leads to the gravitational wave signal being diluted over many frequencies higher than the orbital frequency, where the higher the eccentricity, the more harmonics are required to capture all of the gravitational luminosity \citep[see Fig.\,3 of][]{Peters+1963}.
 Therefore, if the eccentricity is too high, the majority of the signal may be emitted at a frequency to which LISA is less sensitive.
@@
     \includegraphics[width=\columnwidth]{figures/merger_time.pdf}
-    \caption{The merger time for a binary with both a primary and secondary mass of $10 \unit{M_{\odot}}$ over different eccentricities and orbital frequencies.}
+    \caption{The merger time for a binary with both a primary and secondary mass of $10 \unit{M_{\odot}}$ over different eccentricities and orbital frequencies.
+The dashed line indicates a merger time of 4 years, the default LISA mission length.}
     \label{fig:merger_time}
@@
 However, for high eccentricities ($e > 0.8$), the eccentricity significantly reduces the merger time.
+Additionally, we can see that any binary that is to the right of the dashed line on this plot at the start of a 4-year LISA mission, would merge before the mission ended.
 
-\subsection{Compare gravitational wave detectors\texorpdfstring{ - \tutorialLink{https://legwork.readthedocs.io/en/latest/demos/CompareSensitivityCurves.html}}{}}
+\subsection{LISA verification binaries\texorpdfstring{ - \tutorialLink{https://legwork.readthedocs.io/en/latest/demos/VerificationBinaries.html}}{}}
+\citet{Kupfer+2018} presents the LISA verification binaries, a collection of known binary systems that have gravitational-waves that are strong enough to be detected by LISA.
+In \lw{}, we provide easy access to this data through the \href{https://legwork.readthedocs.io/en/latest/api/legwork.source.VerificationBinaries}{\color{\lwColour}{\texttt{VerificationBinaries}}} class, which is a subclass of \href{https://legwork.readthedocs.io/en/latest/api/legwork.source.Source}{\color{\lwColour}{\texttt{Source}}}.
+This means that the class works identically to \texttt{source} but has the verification binary data preloaded into the variables.
+In addition to the base variables, this class also includes the designation of each binary and the SNR that \citet{Kupfer+2018} computed\footnote{We note that this SNR differs from the SNR that \lw{} gives for each binary.
+This is because \citet{Kupfer+2018} run a full LISA simulation for these binaries, whilst we follow the orbit-averaged approach (see Section~\ref{sec:amplitude_mod}), since the former would be intractable for any large number of sources.}.
+
+As an example of how you could use this data, we use the \texttt{VerificationBinaries} class to plot the sources on the LISA sensitivity curve with the SNR calculated by \citet{Kupfer+2018} for a 4-year LISA mission and colour the binaries by their primary mass.
+We see that the verification binaries tend to be detected between $1$-$10 \unit{mHz}$ and have masses estimated to be between $0.1$-$1 \unit{M_{\odot}}$.
+
+\begin{figure}[htb]
+    \centering
+    \includegraphics[width=\columnwidth]{verification_binaries_on_sc.pdf}
+    \caption{The LISA verification binaries from \citet{Kupfer+2018} plotted on the LISA sensitivity curve \citep{Robson+2019} for a 4-year LISA mission. Points are coloured by their primary mass.}
+    \label{fig:verification_binaries_on_sc}
+\end{figure}
+
+\subsection{Comparing gravitational wave detectors\texorpdfstring{ - \tutorialLink{https://legwork.readthedocs.io/en/latest/demos/CompareSensitivityCurves.html}}{}}
 
@@
 \lw{} is capable of adjusting the LISA mission specifications or using a different sensitivity curve and thus we can use it to explore these differences.
-
-As a first step, we can use \lw{} to plot a series of sensitivity curves in Figure~\ref{fig:detector_sc_compare}.
-We show the LISA sensitivity curve for the default 4 year mission length but also illustrate how the curve changes for shorter mission lengths.
-At 0.5 and 2 years, we see a stronger noise level around $3 \unit{mHz}$ as a result of the increased Galactic confusion noise.
-This noise decreases with increasing mission length since more individual foreground sources can be resolved and thus removed from the confusion noise.
-We also see that using an approximated response function smooths out the sensitivity curve at higher frequencies.
-Finally, the TianQin curve is higher than the 4 year LISA curve until around $5 \unit{mHz}$, beyond which it has a lower noise level.
 
@@
 \end{figure}
+
+As a first step, we can use \lw{} to plot a series of sensitivity curves in Figure~\ref{fig:detector_sc_compare}.
+We show the LISA sensitivity curve for the default 4 year mission length but also illustrate how the curve changes for shorter mission lengths.
+At 0.5 and 2 years, we see a stronger noise level around $3 \unit{mHz}$ as a result of the increased Galactic confusion noise.
+This noise decreases with increasing mission length since more individual foreground sources can be resolved and thus removed from the confusion noise.
+We also see that using an approximated response function smooths out the sensitivity curve at higher frequencies.
+Finally, the TianQin curve is higher than the 4 year LISA curve until around $5 \unit{mHz}$, beyond which it has a lower noise level.
 
@@
 Note that \lw{} could also be used in this way to find the SNR of any system in which the orbital evolution is known.
-Thus for a triple system or a binary experiencing gas drag (as long the evolution of the eccentricity and orbital frequency is known) \lw{} is entirely capable of calculating the SNR evolution.
+Thus for a triple system or a binary experiencing gas drag (as long as the evolution of the eccentricity and orbital frequency is known) \lw{} is entirely capable of calculating the SNR evolution.
 
-\begin{figure}
+\begin{figure}[htb]
     \centering
@@
     \label{fig:snr_over_time}
-\end{figure}
-
-\subsection{LISA verification binaries\texorpdfstring{ - \tutorialLink{https://legwork.readthedocs.io/en/latest/demos/VerificationBinaries.html}}{}}
-\citet{Kupfer+2018} presents the LISA verification binaries, a collection of known binary systems that have gravitational-waves that are strong enough to be detected by LISA.
-In \lw{}, we provide easy access to this data through the \href{https://legwork.readthedocs.io/en/latest/api/legwork.source.VerificationBinaries}{\color{\lwColour}{\texttt{VerificationBinaries}}} class, which is a subclass of \href{https://legwork.readthedocs.io/en/latest/api/legwork.source.Source}{\color{\lwColour}{\texttt{Source}}}.
-This means that the class works identically to \texttt{source} but has the verification binary data preloaded into the variables.
-In addition to the base variables, this class also includes the designation of each binary and the SNR that \citet{Kupfer+2018} computed\footnote{We note that this SNR differs from the SNR that \lw{} gives for each binary.
-This is because \citet{Kupfer+2018} run a full LISA simulation for these binaries, whilst we follow the orbit-averaged approach (see Section~\ref{sec:amplitude_mod}), since the former would be intractable for any large number of sources.}.
-
-As an example of how you could use this data, we use the \texttt{VerificationBinaries} class to plot the sources on the LISA sensitivity curve with the SNR calculated by \citet{Kupfer+2018} for a 4-year LISA mission and colour the binaries by their primary mass.
-We see that the verification binaries tend to be detected between $1$-$10 \unit{mHz}$ and have masses estimated to be between $0.1$-$1 \unit{M_{\odot}}$.
-
-\begin{figure}[htb]
-    \centering
-    \includegraphics[width=\columnwidth]{verification_binaries_on_sc.pdf}
-    \caption{The LISA verification binaries from \citet{Kupfer+2018} plotted on the LISA sensitivity curve \citep{Robson+2019} for a 4-year LISA mission. Points are coloured by their primary mass.}
-    \label{fig:verification_binaries_on_sc}
 \end{figure}
@@
     % People
-    We are grateful to Valeria Korol, Tyson Littenberg, Alberto Sesana, Stas Babak, Ilya Mandel, Mike Lau, Lieke van Son, Floor Broekgaarden, Stephen Justham, Will Farr, Tom Callister, the CCA GW group, the BinCosmos group and the COMPAS group for stimulating discussions that influenced and motivated us to complete this project.
+    We are grateful to Stat Babak, Floor Broekgaarden, Tom Callister, Will Farr, Stephen Justham, Valeria Korol, Mike Lau, Tyson Littenberg, Ilya Mandel, Alberto Sesana, Lieke van Son, the CCA GW group, the BinCosmos group and the COMPAS group for stimulating discussions that influenced and motivated us to complete this project.
 We thank the BinCosmos group for testing an early version of the package and providing useful feedback.
-We also thank Lieke van Son for her innovation in inventing a name for \lw{}!
+In particular, we thank Lieke van Son for her innovation in inventing the name \lw{}!
+TW also thanks Floor Broekgaarden for first suggesting that he investigate LISA and the derivation of the SNR calculation.
 

### 2021-11-15 src/ms.tex
remove anchors from links, fix typos

@@
 \newcommand{\lwModLink}[1]{\href{https://legwork.readthedocs.io/en/latest/modules.html\#module-legwork.#1}{\color{\lwColour}{\texttt{#1}}}}
-\newcommand{\lwFuncURL}[2]{https://legwork.readthedocs.io/en/latest/api/legwork.#1.#2.html\#legwork.#1.#2}
+\newcommand{\lwFuncURL}[2]{https://legwork.readthedocs.io/en/latest/api/legwork.#1.#2.html}
 
@@
 \end{equation}
-
 For circular binaries, gravitational-wave emission occurs at twice the orbital frequency ($f_{\rm GW} = 2 f_{\rm orb}$).
@@
 \end{equation}
-where $D_L$ is the luminosity distance to the source (note that for Milky Way sources this is simply the distance to the source), $\dot{E}_n$ is the power radiated in the $n^{\rm th}$ harmonic and $\dot{f}_n$ is the rate of change of the $n^{\rm th}$ harmonic frequency.
+where $D_L$ is the luminosity distance to the source (note that for Milky Way sources, or any sources with redshift $\sim 0$, this is simply the distance to the source), $\dot{E}_n$ is the power radiated in the $n^{\rm th}$ harmonic and $\dot{f}_n$ is the rate of change of the $n^{\rm th}$ harmonic frequency.
 
@@
 For the TianQin sensitivity curve we use the power spectral density given in \citet[][Eq.~13]{Huang+2020}
-\begin{equation}{}
+\begin{equation}{\lwFuncURL{psd}{tianqin_psd}}
     \begin{split}
@@
     % People
-    We are grateful to Stat Babak, Floor Broekgaarden, Tom Callister, Will Farr, Stephen Justham, Valeria Korol, Mike Lau, Tyson Littenberg, Ilya Mandel, Alberto Sesana, Lieke van Son, the CCA GW group, the BinCosmos group and the COMPAS group for stimulating discussions that influenced and motivated us to complete this project.
+    We are grateful to Stas Babak, Floor Broekgaarden, Tom Callister, Will Farr, Stephen Justham, Valeria Korol, Mike Lau, Tyson Littenberg, Ilya Mandel, Alberto Sesana, Lieke van Son, the CCA GW group, the BinCosmos group and the COMPAS group for stimulating discussions that influenced and motivated us to complete this project.
 We thank the BinCosmos group for testing an early version of the package and providing useful feedback.

### 2021-11-16 src/ms.tex
minor updates to rearrange use cases

@@
 \begin{abstract}
-% Original
-%    We present \lw{}, a Python package for making predictions about stellar-origin gravitational wave sources and their detectability in LISA and other space-based gravitational wave detectors.
-\lw{} can be used to evolve sources over time, calculate gravitational wave strains, compute signal-to-noise ratios and visualise the results.
-In this paper we give an overview of the structure and functionality of the package, as well as highlight several optimisations that make it particularly efficient for use in population studies which can contain tens-of-millions of sources.
-We demonstrate the various capabilities of \lw{} through a series of example use cases.
-These begin with a basic example of calculating the signal-to-noise ratio of a source but also include using \lw{} to calculate horizon distances and make comparisons between gravitational-wave detectors.
-We additionally explain in detail the derivation of the equations behind \lw{} in order to clarify some conflicts currently present in the literature.
-
-% -------------
-
-% Selma version
-% We present \lw{} (LISA Evolution and Gravitational Wave Orbit Kit) an open-source Python package developed to aid studies of stellar-origin gravitational wave sources detectable by space-based gravitational wave detectors such as LISA.
-% %
-% This package can be used to follow the gravitational wave driven inspiral of a compact binary consisting of, for example, white dwarfs, neutron stars and/or stellar-mass black holes.
-We calculate the gravitational wave strains using the post-Newtonian approximations and estimate the signal-to-noise ratio for a given detector sensitivity.
-We optimised \lw{} to make it feasible to make predictions for populations of tens-of-millions of sources.
-In principle, \lw{} can be used for any systems with a user-specified orbital evolution, such as those affected by a third object or gas drag.
-% %
-% This paper describes the package and presents several use cases.
-We provide the derivations behind the expressions and we identify and clarify some discrepancies in the expressions presented in earlier literature.
-We hope that \lw{} will enable and accelerate future studies triggered by the rapidly growing interest in gravitational wave sources.
-
 We present \lw{} (LISA Evolution and Gravitational Wave Orbit Kit), an open-source Python package for making predictions about stellar-origin gravitational wave sources and their detectability in LISA or other space-based gravitational wave detectors.
@@
 
-\lw{} has been adopted in multiple studies.
+\lw{} has been developed with stellar-origin binary population studies in mind.
 Wagg et al.\ (in prep) investigates several populations of potential LISA sources (double black holes, black hole neutron stars and double neutron stars).
@@
 The \lw{} package is composed of seven modules that each focus on a particular aspect of calculations useful for gravitational wave sources that are detectable by space-based detectors.
-In Fig.~\ref{fig:package_overview}, we illustrate the general structure of the package with each of its modules.
+In Figure~\ref{fig:package_overview}, we illustrate the general structure of the package with each of its modules.
 The \texttt{source} module is the central module of the package and provides an simple interface to the functions in the rest of the modules.
-For more complex analyses, users may want to interact directly with individual modules, particularly those in the top row of Fig.~\ref{fig:package_overview} as they comprise the core functionality of \lw{}.
+For more complex analyses, users may want to interact directly with individual modules, particularly those in the top row of Figure~\ref{fig:package_overview} as they comprise the core functionality of \lw{}.
 Below we explain the capabilities of each module in detail.
@@
 In addition, you can use this module to evolve binary orbit parameters forward in time with any number or arrangement of timesteps.
-We discuss the relevant equations in Sec.~\ref{sec:deriv_evol}.
+We discuss the relevant equations in Section~\ref{sec:deriv_evol}.
 
@@
 Each of these functions is capable of computing the strain for an array of binaries at any number of timesteps and evaluated at any number of frequency harmonics.
-We discuss the relevant equations in Sec.~\ref{sec:deriv_strain}.
+We discuss the relevant equations in Section~\ref{sec:deriv_strain}.
 
@@
 Additionally, this module allows the user to specify a custom detector sensitivity curve.
-We discuss the relevant equations in Sec.~\ref{sec:deriv_psd}.
+We discuss the relevant equations in Section~\ref{sec:deriv_psd}.
 
@@
 It contains four functions that cover the permutations of whether a source is circular or eccentric and stationary in frequency space on the timescale of the mission or evolving.
-We discuss the relevant equations in Sec.~\ref{sec:deriv_snr}.
+We discuss the relevant equations in Section~\ref{sec:deriv_snr}.
 
@@
 \lwModLink{utils} is a collection of miscellaneous utility functions mainly consisting of conversions between variables as well as constants and expressions from \citet{Peters+1964}.
-We discuss the relevant equations in Sec.~\ref{sec:deriv_utils}.
+We discuss the relevant equations in Section~\ref{sec:deriv_utils}.
 
@@
 
-Firstly, we found that the runtime of calculating strains and SNRs for large populations of sources was mainly limited by the computation of (1) the relative gravitational-wave power in each harmonic for eccentric systems (see Eq.~\ref{eq:g(n,e)}) (2) the sensitivity curve of the given detector.
+Firstly, we find that the runtime of calculating strains and SNRs for large populations of sources is mainly limited by the computation of (1) the relative gravitational-wave power in each harmonic for eccentric systems (see Eq.~\ref{eq:g(n,e)}) (2) the sensitivity curve of the given detector.
 Therefore, in order to significantly reduce the runtime of strain and SNR computations, by default \lw{} automatically interpolates these functions upon instantiation of any \texttt{Source} class with a large number of sources.
@@
 We note that since the orbit averaging is carried out in Fourier space, this requires the frequency to be monochromatic and thus is only implemented in \lw{} for quasi-circular binaries (as eccentric systems emit at many frequency harmonics).
-We also note that since the majority of the calculations in \lw{} are carried out for the full position, polarisation, and inclination averages, we place a pre-factor of $5/4$ on the amplitude modulation in the software implementation to undo the factor of $4/5$ which arises from the averaging of Equations~\ref{eq:response_fplus} and \ref{eq:response_fcross}.
 
@@
     \includegraphics[width=\textwidth]{figures/horizon_distance.pdf}
-    \caption{The horizon distance for circular stellar mass binaries in a four-year LISA mission.
+    \caption{The horizon distance for circular, stellar-mass binaries in a 4-year LISA mission.
 The filled contours indicate the horizon distance for different orbital frequencies and chirp masses.
 We add white dotted contours at $8, 50, 800 \unit{kpc}$ and $40 \unit{Mpc}$ to highlight the distances to the centre of the Milky Way, the Magellanic Clouds, the Andromeda galaxy and the nearest ground-based gravitational wave detection (GW170817, \citealp{Abbott+2017_GW170817}) respectively.
-The diagonal line black line shows the frequencies and chirp masses at which the merger time is equal to the observation time.
+The diagonal black line shows the frequencies and chirp masses at which the merger time is equal to the observation time.
 This line emphasises the sharp contrast for the horizon distance for binaries that merge before the LISA mission finishes observing (to the right of the line).
@@
 
-This can be most efficiently accomplished using \lw{}'s source class.
-Although the source class only reads in one-dimensional lists of sources, one can flatten a grid of chirp masses and orbital frequencies to make the input work.
-\lw{} can then compute the merger times and signal-to-noise ratio of each source with only two lines of code.
-These results can then be reshaped to match the original grid of chirp masses and frequencies.
-
-We convert these SNRs to horizon distances using Eq.~\ref{eq:snr_to_hor_dist} and plot the result in Figure~\ref{fig:horizon_distance}.
+This can be most efficiently accomplished using \lw{}'s source class, since \lw{} can then compute the merger times and signal-to-noise ratio of each source with only two lines of code.
+We convert the SNRs to horizon distances using Eq.~\ref{eq:snr_to_hor_dist} and plot the result in Figure~\ref{fig:horizon_distance}.
 The shape of the LISA sensitivity curve is clearly reflected in the horizon distance.
@@
 The role of eccentricity is important to consider in the detection of gravitational waves with LISA and other space-based detectors, as sources can still have significant eccentricity during their inspiral phase.
-A high eccentricity has two major effects on the SNR of a gravitational wave source in LISA and we can investigate this using \lw{}.
+A high eccentricity has two major effects on the SNR of a gravitational wave source in LISA and we can investigate these effects using \lw{}.
 
@@
 \end{align*}
-Using \lw{} to calculate their signal-to-noise ratios (for a 4-year LISA mission), $\rho_i$, we find
+Using \lw{} to calculate their signal-to-noise ratios in a 4-year LISA mission, $\rho_i$, we find
 \begin{equation*}{}
-    \rho_i = \{ 31.7, 50.2, 38.8 \}
+    \rho_i = \{ 31.7, 50.2, 38.8 \}.
 \end{equation*}
@@
 This means that an eccentric binary will not only inspiral faster than an otherwise identical circular binary, but also will always produce a stronger gravitational wave strain.
-The enhancement factor and its exact dependence on eccentricity is discussed in more detail Section~\ref{sec:derivations} (specifically Eq.~\ref{eq:eccentricity_enhancement_factor}).
+We discuss the enhancement factor and its exact dependence on eccentricity in more detail in Section~\ref{sec:derivations} (see specifically Eq.~\ref{eq:eccentricity_enhancement_factor}).
 
@@
 The reason for this is that eccentric binaries emit gravitational waves at many harmonic frequencies (unlike circular binaries, which emit predominantly twice the orbital frequency).
-This leads to the gravitational wave signal being diluted over many frequencies higher than the orbital frequency, where the higher the eccentricity, the more harmonics are required to capture all of the gravitational luminosity \citep[see Fig.\,3 of][]{Peters+1963}.
+This leads to the gravitational wave signal being diluted over many frequencies higher than the orbital frequency, where the higher the eccentricity, the more harmonics are required to capture all of the gravitational luminosity \citep[see Figure~3 of][]{Peters+1963}.
 Therefore, if the eccentricity is too high, the majority of the signal may be emitted at a frequency to which LISA is less sensitive.
 
-We can illustrate this point with \lw{} by calculating the SNR at each individual harmonic using the \lwModLink{snr} module.
-We plot this distribution of signal over different harmonics with the LISA sensitivity curve overlaid in Fig.~\ref{fig:role_eccentricity} using \lw{}'s \lwModLink{visualisation} module.
+We can illustrate this point with \lw{} by calculating the SNR at each individual frequency harmonic using the \lwModLink{snr} module.
+We plot this distribution of signal over different frequency harmonics with the LISA sensitivity curve overlaid in Figure~\ref{fig:role_eccentricity} using \lw{}'s \lwModLink{visualisation} module.
 A point is plotted for each harmonic of each source that has an SNR greater than unity and such that its height above the sensitivity curve corresponds to its SNR.
@@
 
-From Fig.~\ref{fig:role_eccentricity}, we can better understand why a source with $e = 0.9$ has a lower SNR than the same source with $e = 0.6$.
-From the dotted lines, we can note that the signal from the $e = 0.9$ source is concentrated at a frequency of around $4 \times 10^{-2} \unit{Hz}$.
-The LISA sensitivity at this point is much weaker than the $6 \times 10^{-3} \unit{Hz}$ at which the $e =0.6$ source is concentrated.
+From Figure~\ref{fig:role_eccentricity}, we can better understand why a source with $e = 0.9$ has a lower SNR than the same source with $e = 0.6$.
+From the dotted lines, we can note that the signal from the $e = 0.9$ source is concentrated at a frequency of around $40 \unit{mHz}$.
+The LISA sensitivity at this point is much weaker than the $6 \unit{mHz}$ at which the $e =0.6$ source is concentrated.
 Therefore, although the strain from a more eccentric binary is stronger, the SNR is lower due to the increased noise in the LISA detector.
@@
 Overall, we can therefore conclude that for LISA sources of this nature, higher eccentricity will produce more detectable binaries only if the orbital frequency is not already at or above the minimum of the LISA sensitivity curve.
+
+Another consideration for more massive binaries is whether the increased eccentricity will cause the binary to merge before the mission ends, which would cause a significant decrease in signal-to-noise ratio.
+We can also use \lw{} to find how the merger time of a source varies with frequency and eccentricity over a grid of sources.
 
@@
 
-Another consideration for more massive binaries is whether the increased eccentricity will cause the binary to merge before the mission ends, which would cause a significant decrease in signal-to-noise ratio.
-We can also use \lw{} to find how the merger time of a source varies with frequency and eccentricity over a grid of sources.
-
 We plot the results of this calculation in Figure~\ref{fig:merger_time}.
-This plot shows that for most eccentricities the merger is time is largely determined by the orbital frequency.
-However, for high eccentricities ($e > 0.8$), the eccentricity significantly reduces the merger time.
+This plot shows that, for most eccentricities, the merger time is largely determined by the orbital frequency.
+However, for high eccentricities ($e > 0.8$), the eccentricity leads to a significant reduction in the merger time.
 Additionally, we can see that any binary that is to the right of the dashed line on this plot at the start of a 4-year LISA mission, would merge before the mission ended.
-
-\subsection{LISA verification binaries\texorpdfstring{ - \tutorialLink{https://legwork.readthedocs.io/en/latest/demos/VerificationBinaries.html}}{}}
-\citet{Kupfer+2018} presents the LISA verification binaries, a collection of known binary systems that have gravitational-waves that are strong enough to be detected by LISA.
-In \lw{}, we provide easy access to this data through the \href{https://legwork.readthedocs.io/en/latest/api/legwork.source.VerificationBinaries}{\color{\lwColour}{\texttt{VerificationBinaries}}} class, which is a subclass of \href{https://legwork.readthedocs.io/en/latest/api/legwork.source.Source}{\color{\lwColour}{\texttt{Source}}}.
-This means that the class works identically to \texttt{source} but has the verification binary data preloaded into the variables.
-In addition to the base variables, this class also includes the designation of each binary and the SNR that \citet{Kupfer+2018} computed\footnote{We note that this SNR differs from the SNR that \lw{} gives for each binary.
-This is because \citet{Kupfer+2018} run a full LISA simulation for these binaries, whilst we follow the orbit-averaged approach (see Section~\ref{sec:amplitude_mod}), since the former would be intractable for any large number of sources.}.
-
-As an example of how you could use this data, we use the \texttt{VerificationBinaries} class to plot the sources on the LISA sensitivity curve with the SNR calculated by \citet{Kupfer+2018} for a 4-year LISA mission and colour the binaries by their primary mass.
-We see that the verification binaries tend to be detected between $1$-$10 \unit{mHz}$ and have masses estimated to be between $0.1$-$1 \unit{M_{\odot}}$.
-
-\begin{figure}[htb]
-    \centering
-    \includegraphics[width=\columnwidth]{verification_binaries_on_sc.pdf}
-    \caption{The LISA verification binaries from \citet{Kupfer+2018} plotted on the LISA sensitivity curve \citep{Robson+2019} for a 4-year LISA mission. Points are coloured by their primary mass.}
-    \label{fig:verification_binaries_on_sc}
-\end{figure}
-
-\subsection{Comparing gravitational wave detectors\texorpdfstring{ - \tutorialLink{https://legwork.readthedocs.io/en/latest/demos/CompareSensitivityCurves.html}}{}}
-
-It may also be useful to consider how changing the specifications of the LISA detector, or using a different detector entirely, could affect the SNR of a particular source.
-\lw{} is capable of adjusting the LISA mission specifications or using a different sensitivity curve and thus we can use it to explore these differences.
-
-\begin{figure}[htb]
-    \centering
-    \includegraphics[width=\columnwidth]{figures/detector_sc_compare.pdf}
-    \caption{The strain spectral density of the LISA detector with different specifications \citep{Robson+2019} and the TianQin detector \citep{Huang+2020}.
-We show the LISA curve for three different mission lengths and once with an approximate response function.}
-    \label{fig:detector_sc_compare}
-\end{figure}
-
-As a first step, we can use \lw{} to plot a series of sensitivity curves in Figure~\ref{fig:detector_sc_compare}.
-We show the LISA sensitivity curve for the default 4 year mission length but also illustrate how the curve changes for shorter mission lengths.
-At 0.5 and 2 years, we see a stronger noise level around $3 \unit{mHz}$ as a result of the increased Galactic confusion noise.
-This noise decreases with increasing mission length since more individual foreground sources can be resolved and thus removed from the confusion noise.
-We also see that using an approximated response function smooths out the sensitivity curve at higher frequencies.
-Finally, the TianQin curve is higher than the 4 year LISA curve until around $5 \unit{mHz}$, beyond which it has a lower noise level.
-
-Although comparing the sensitivity curves would suffice for a stationary and circular source (since it would remain at a single frequency), \lw{} can also be used to see how the relative SNR between two detectors changes over a range of eccentricities and frequencies.
-
-Using \lw{}, we can compute the SNR of a grid of sources (spanning a range of frequencies and eccentricities) for both detectors.
-In Figure~\ref{fig:detector_snr_ratio}, we show the ratio of the SNR in LISA to the SNR in TianQin.
-This plot shows that for circular binaries, the SNR of the source in LISA is stronger up to an orbital frequency of approximately $2.5 \unit{mHz}$, beyond which the SNR of the source is stronger in TianQin.
-This transition frequency becomes lower with increasing eccentricity as one would expect since eccentric sources emit more at higher harmonics and thus higher frequencies.
-
-\begin{figure}[htb]
-    \centering
-    \includegraphics[width=\columnwidth]{figures/detector_snr_ratio.pdf}
-    \caption{The ratio of the SNR in LISA (for a four year mission) to the SNR in TianQin.
-The dashed line indicates the transition at which the SNR is equal in both detectors.
-We annotate the regions in which either detector has a higher SNR and also annotate the mass and distance of each source in the grid.}
-    \label{fig:detector_snr_ratio}
-\end{figure}
+Therefore, if increasing a binary's eccentricity moved it to the right of this line, its SNR will decrease significantly.
 
@@
 
-We plot this evolution of the eccentricity and frequency in the top two panels of Fig.~\ref{fig:snr_over_time} as a function of the time before the merger.
+We plot this evolution of the eccentricity and frequency in the top two panels of Figure~\ref{fig:snr_over_time} as a function of the time before the merger.
 We see that the binary circularises and increases its orbital frequency as it inspirals as we would expect.
@@
 To take this a step further, we can consider the binary at each timestep to be a separate source with the current eccentricity and frequency.
-It is then trivial to use \lw{} to calculate the SNR for each of these `sources' and thus attain the SNR evolution, which we plot in the last panel of Fig.~\ref{fig:snr_over_time}.
+It is then trivial to use \lw{} to calculate the SNR for each of these `sources' and thus attain the SNR evolution, which we plot in the last panel of Figure~\ref{fig:snr_over_time}.
 
@@
     \includegraphics[width=\columnwidth]{figures/snr_over_time.pdf}
-    \caption{The evolution of a binary system's eccentricity (top), orbital frequency (middle) and signal-to-noise ratio (bottom).
+    \caption{The evolution of a binary system's eccentricity (top), orbital frequency (middle) and SNR (bottom).
 Each panel is annotated with the constant parameters of the system.
@@
     \label{fig:snr_over_time}
+\end{figure}
+
+\subsection{Comparing gravitational wave detectors\texorpdfstring{ - \tutorialLink{https://legwork.readthedocs.io/en/latest/demos/CompareSensitivityCurves.html}}{}}
+
+It may also be useful to consider how changing the specifications of the LISA detector, or using a different detector entirely, could affect the SNR of a particular source.
+\lw{} is capable of adjusting the LISA mission specifications or using a different sensitivity curve and thus we can use it to explore these differences.
+
+As a first step, we can use \lw{} to plot a series of sensitivity curves in Figure~\ref{fig:detector_sc_compare}.
+We show the LISA sensitivity curve for the default 4 year mission length but also illustrate how the curve changes for shorter mission lengths.
+At 0.5 and 2 years, we see a stronger noise level around $3 \unit{mHz}$ as a result of the increased Galactic confusion noise.
+This noise decreases with increasing mission length since more individual foreground sources can be resolved and thus removed from the confusion noise.
+We also see that using an approximated response function smooths out the sensitivity curve at higher frequencies.
+Finally, the TianQin curve is higher than the 4 year LISA curve until around $5 \unit{mHz}$, beyond which it has a lower noise level.
+
+\begin{figure}[htb]
+    \centering
+    \includegraphics[width=\columnwidth]{figures/detector_sc_compare.pdf}
+    \caption{The strain spectral density of the LISA detector with different specifications \citep{Robson+2019} and the TianQin detector \citep{Huang+2020}.
+We show the LISA curve for three different mission lengths and once with an approximate response function.}
+    \label{fig:detector_sc_compare}
+\end{figure}
+
+Although comparing the sensitivity curves would suffice for a stationary and circular source (since it would remain at a single frequency), \lw{} can also be used to see how the relative SNR between two detectors changes over a range of eccentricities and frequencies.
+
+Using \lw{}, we can compute the SNR of a grid of sources (spanning a range of frequencies and eccentricities) for both detectors.
+In Figure~\ref{fig:detector_snr_ratio}, we show the ratio of the SNR in LISA to the SNR in TianQin.
+This plot shows that for circular binaries, the SNR of the source in LISA is stronger up to an orbital frequency of approximately $2.5 \unit{mHz}$, beyond which the SNR of the source is stronger in TianQin.
+This transition frequency becomes lower with increasing eccentricity as one would expect since eccentric sources emit more at higher harmonics and thus higher frequencies.
+
+\begin{figure}[htb]
+    \centering
+    \includegraphics[width=\columnwidth]{figures/detector_snr_ratio.pdf}
+    \caption{The ratio of the SNR in LISA (for a 4-year mission) to the SNR in TianQin.
+The dashed line indicates the transition at which the SNR is equal in both detectors.
+We annotate the regions in which either detector has a higher SNR and also annotate the mass and distance of each source in the grid.}
+    \label{fig:detector_snr_ratio}
+\end{figure}
+
+\subsection{LISA verification binaries\texorpdfstring{ - \tutorialLink{https://legwork.readthedocs.io/en/latest/demos/VerificationBinaries.html}}{}}
+\citet{Kupfer+2018} presents the LISA verification binaries, a collection of known binary systems that have gravitational-waves that are strong enough to be detected by LISA.
+In \lw{}, we provide easy access to this data through the \href{https://legwork.readthedocs.io/en/latest/api/legwork.source.VerificationBinaries}{\color{\lwColour}{\texttt{VerificationBinaries}}} class, which is a subclass of \href{https://legwork.readthedocs.io/en/latest/api/legwork.source.Source}{\color{\lwColour}{\texttt{Source}}}.
+This means that the class works identically to \texttt{Source}, but it has the verification binary data (such as their masses and orbital frequencies) pre-loaded into the variables.
+
+In addition to the base variables, this class also includes the designation of each binary and the SNR that \citet{Kupfer+2018} computed.
+We note that this SNR differs from the SNR that \lw{} gives for each binary.
+This is because \citet{Kupfer+2018} run a full, detailed LISA simulation for these binaries, whilst we follow the orbit-averaged approach (see Section~\ref{sec:amplitude_mod}), since the former would be intractable for any large number of sources.
+
+As an example of how you could use this data, we use the \texttt{VerificationBinaries} class to plot the sources on the LISA sensitivity curve with the SNR calculated by \citet{Kupfer+2018} for a 4-year LISA mission and colour the binaries by their primary mass.
+We see that the verification binaries tend to be detected with frequencies between $1$-$10 \unit{mHz}$ and have masses estimated to be between $0.1$-$1 \unit{M_{\odot}}$.
+
+\begin{figure}[htb]
+    \centering
+    \includegraphics[width=\columnwidth]{verification_binaries_on_sc.pdf}
+    \caption{The LISA verification binaries from \citet{Kupfer+2018} plotted on the LISA sensitivity curve \citep{Robson+2019} for a 4-year LISA mission. Points are coloured by their primary mass.}
+    \label{fig:verification_binaries_on_sc}
 \end{figure}

### 2021-11-16 src/ms.tex
missed path in vb figure
final updates to introduction

@@
 
-The potential to detect stellar-origin sources with LISA has been studied in the past \citep[e.g.][]{Nelemans+2001, Liu+2009, Liu+2014, Ruiter+2010, Belczynski+2010, Yu+2010, Nissanke+2012}.
-More recently, the direct detection of gravitational waves with ground-based detectors has led to renewed interest in this topic with many recent papers addressing the issue \citep[e.g.][]{Korol+2017, Korol+2018, Korol+2019, Korol+2020, Christian+2017, Kremer+2017, Kremer+2018, Lamberts+2018, Lamberts+2019, Fang+2019, Andrews+2020, Lau+2020, Breivik+2020, Breivik+2020a, Roebber+2020, Chen+2020, Sesana+2020, Shao+2021}.
+The potential to detect stellar-origin sources with LISA has been studied in the past by various groups \citep[e.g.][]{Nelemans+2001, Liu+2009, Liu+2014, Ruiter+2010, Belczynski+2010, Yu+2010, Nissanke+2012}.
+The recent direct detection of gravitational waves with ground-based detectors has led to renewed interest in this topic \citep[e.g.][]{Korol+2017, Korol+2018, Korol+2019, Korol+2020, Christian+2017, Kremer+2017, Kremer+2018, Lamberts+2018, Lamberts+2019, Fang+2019, Andrews+2020, Lau+2020, Breivik+2020, Breivik+2020a, Roebber+2020, Chen+2020, Sesana+2020, Shao+2021}.
 
@@
 \lw{} is an open-source Python package designed to streamline the process of making predictions of LISA detection rates for stellar-origin binaries such that it is as fast, reliable and simple as possible.
-This goal makes \lw{} unique among other implementations of gravitational-wave tools in the literature, which focus on a more broad coverage of the gravitational-wave spectrum and source classes, rather than an optimised approach for certain sources.
-\citep[e.g.][]{Moore+2015,Yi2021}.
 With \lw{} one can evolve the orbits of a binary or a collection of binaries and calculate their strain amplitudes for any range of frequency harmonics.
@@
 
+We note that \lw{} is not the only initiative of this kind.
+We highlight the ``Gravitational Wave Universe Toolbox'' presented by \citet{Yi2021} which was developed to simulate observations on the GW universe with different detectors covering the full gravitational-wave spectrum and source classes.
+We also highlight ``GWPlotter'' by \citep{Moore+2015}, which provides an interactive plotting tool to compare the sensitivity of different gravitational wave detectors.
+\lw{} differs from the tools listed here as we have tried to provide tools that are optimised to rapidly make predictions for large populations of stellar-origin sources and we have focused on space-based detectors.
+
 \lw{} has been developed with stellar-origin binary population studies in mind.
+We highlight two upcoming papers that use our package.
 Wagg et al.\ (in prep) investigates several populations of potential LISA sources (double black holes, black hole neutron stars and double neutron stars).
@@
 \end{equation}
-where $G$ is the gravitational constant. Inversely we could write
+where $G$ is the gravitational constant. Inversely,
 \begin{equation}{\lwFuncURL{utils}{get_a_from_f_orb}}
@@
 \end{equation}
-where $c_0$ satisfies the initial conditions such that $a(e_0) = a_0$. The time derivative of the eccentricity, $e$, is given by
+where $c_0$ satisfies the initial conditions such that $a(e_0) = a_0$. The time derivative of the eccentricity, $e$, is
 \begin{equation}{\lwFuncURL{evol}{de_dt}}
@@
     \begin{split}
-        t_{\rm merge} \approx& t_{\rm merge, circ} (1 - e^2_0)^{7/2} \\
+        t_{\rm merge} \approx&\ t_{\rm merge, circ} (1 - e^2_0)^{7/2} \\
     &\times(1 + 0.27 e_0^{10} + 0.33 e^{20}_0 + 0.2 e_0^{1000} ),
@@
     \centering
-    \includegraphics[width=\columnwidth]{verification_binaries_on_sc.pdf}
+    \includegraphics[width=\columnwidth]{figures/verification_binaries_on_sc.pdf}
     \caption{The LISA verification binaries from \citet{Kupfer+2018} plotted on the LISA sensitivity curve \citep{Robson+2019} for a 4-year LISA mission. Points are coloured by their primary mass.}

### 2021-11-16 src/ms.tex
fix python link
arrange figures more nicely

@@
 
-This can be most efficiently accomplished using \lw{}'s source class, since \lw{} can then compute the merger times and signal-to-noise ratio of each source with only two lines of code.
+This can be most efficiently accomplished using \lw{}'s \href{https://legwork.readthedocs.io/en/latest/api/legwork.source.Source}{\color{\lwColour}{\texttt{Source}}} class, since \lw{} can then compute the merger times and signal-to-noise ratio of each source with only two lines of code.
 We convert the SNRs to horizon distances using Eq.~\ref{eq:snr_to_hor_dist} and plot the result in Figure~\ref{fig:horizon_distance}.
@@
 
+\subsection{Comparing gravitational wave detectors\texorpdfstring{ - \tutorialLink{https://legwork.readthedocs.io/en/latest/demos/CompareSensitivityCurves.html}}{}}
+
+It may also be useful to consider how changing the specifications of the LISA detector, or using a different detector entirely, could affect the SNR of a particular source.
+\lw{} is capable of adjusting the LISA mission specifications or using a different sensitivity curve and thus we can use it to explore these differences.
+
+As a first step, we can use \lw{} to plot a series of sensitivity curves in Figure~\ref{fig:detector_sc_compare}.
+We show the LISA sensitivity curve for the default 4 year mission length but also illustrate how the curve changes for shorter mission lengths.
+At 0.5 and 2 years, we see a stronger noise level around $3 \unit{mHz}$ as a result of the increased Galactic confusion noise.
+This noise decreases with increasing mission length since more individual foreground sources can be resolved and thus removed from the confusion noise.
+We also see that using an approximated response function smooths out the sensitivity curve at higher frequencies.
+Finally, the TianQin curve is higher than the 4 year LISA curve until around $5 \unit{mHz}$, beyond which it has a lower noise level.
+
+\begin{figure}[tb]
+    \centering
+    \includegraphics[width=\columnwidth]{figures/detector_sc_compare.pdf}
+    \caption{The strain spectral density of the LISA detector with different specifications \citep{Robson+2019} and the TianQin detector \citep{Huang+2020}.
+We show the LISA curve for three different mission lengths and once with an approximate response function.}
+    \label{fig:detector_sc_compare}
+\end{figure}
+
+Although comparing the sensitivity curves would suffice for a stationary and circular source (since it would remain at a single frequency), \lw{} can also be used to see how the relative SNR between two detectors changes over a range of eccentricities and frequencies.
+
+Using \lw{}, we can compute the SNR of a grid of sources (spanning a range of frequencies and eccentricities) for both detectors.
+In Figure~\ref{fig:detector_snr_ratio}, we show the ratio of the SNR in LISA to the SNR in TianQin.
+This plot shows that for circular binaries, the SNR of the source in LISA is stronger up to an orbital frequency of approximately $2.5 \unit{mHz}$, beyond which the SNR of the source is stronger in TianQin.
+This transition frequency becomes lower with increasing eccentricity as one would expect since eccentric sources emit more at higher harmonics and thus higher frequencies.
+
+\begin{figure}[htb]
+    \centering
+    \includegraphics[width=\columnwidth]{figures/detector_snr_ratio.pdf}
+    \caption{The ratio of the SNR in LISA (for a 4-year mission) to the SNR in TianQin.
+The dashed line indicates the transition at which the SNR is equal in both detectors.
+We annotate the regions in which either detector has a higher SNR and also annotate the mass and distance of each source in the grid.}
+    \label{fig:detector_snr_ratio}
+\end{figure}
+
 \subsection{Track SNR of a binary over time\texorpdfstring{ - \tutorialLink{https://legwork.readthedocs.io/en/latest/demos/SNROverTime.html}}{}}
@@
 \end{align*}
-and use \lw{} to evolve the system until 100 years before its merger with 1000 linearly spaced timesteps, recording the eccentricity and frequency at each timestep.
+and use \lw{}'s \lwModLink{evol} module to evolve the system until 100 years before its merger with 1000 linearly spaced timesteps, recording the eccentricity and frequency at each timestep.
 
@@
     \label{fig:snr_over_time}
-\end{figure}
-
-\subsection{Comparing gravitational wave detectors\texorpdfstring{ - \tutorialLink{https://legwork.readthedocs.io/en/latest/demos/CompareSensitivityCurves.html}}{}}
-
-It may also be useful to consider how changing the specifications of the LISA detector, or using a different detector entirely, could affect the SNR of a particular source.
-\lw{} is capable of adjusting the LISA mission specifications or using a different sensitivity curve and thus we can use it to explore these differences.
-
-As a first step, we can use \lw{} to plot a series of sensitivity curves in Figure~\ref{fig:detector_sc_compare}.
-We show the LISA sensitivity curve for the default 4 year mission length but also illustrate how the curve changes for shorter mission lengths.
-At 0.5 and 2 years, we see a stronger noise level around $3 \unit{mHz}$ as a result of the increased Galactic confusion noise.
-This noise decreases with increasing mission length since more individual foreground sources can be resolved and thus removed from the confusion noise.
-We also see that using an approximated response function smooths out the sensitivity curve at higher frequencies.
-Finally, the TianQin curve is higher than the 4 year LISA curve until around $5 \unit{mHz}$, beyond which it has a lower noise level.
-
-\begin{figure}[htb]
-    \centering
-    \includegraphics[width=\columnwidth]{figures/detector_sc_compare.pdf}
-    \caption{The strain spectral density of the LISA detector with different specifications \citep{Robson+2019} and the TianQin detector \citep{Huang+2020}.
-We show the LISA curve for three different mission lengths and once with an approximate response function.}
-    \label{fig:detector_sc_compare}
-\end{figure}
-
-Although comparing the sensitivity curves would suffice for a stationary and circular source (since it would remain at a single frequency), \lw{} can also be used to see how the relative SNR between two detectors changes over a range of eccentricities and frequencies.
-
-Using \lw{}, we can compute the SNR of a grid of sources (spanning a range of frequencies and eccentricities) for both detectors.
-In Figure~\ref{fig:detector_snr_ratio}, we show the ratio of the SNR in LISA to the SNR in TianQin.
-This plot shows that for circular binaries, the SNR of the source in LISA is stronger up to an orbital frequency of approximately $2.5 \unit{mHz}$, beyond which the SNR of the source is stronger in TianQin.
-This transition frequency becomes lower with increasing eccentricity as one would expect since eccentric sources emit more at higher harmonics and thus higher frequencies.
-
-\begin{figure}[htb]
-    \centering
-    \includegraphics[width=\columnwidth]{figures/detector_snr_ratio.pdf}
-    \caption{The ratio of the SNR in LISA (for a 4-year mission) to the SNR in TianQin.
-The dashed line indicates the transition at which the SNR is equal in both detectors.
-We annotate the regions in which either detector has a higher SNR and also annotate the mass and distance of each source in the grid.}
-    \label{fig:detector_snr_ratio}
 \end{figure}
@@
 
-\software{\lw{} is written in \texttt{Python}, available from \url{python.org}.
+\software{\lw{} is written in \texttt{Python}, available from \url{https://www.python.org}.
 We make use of the following Python packages: \texttt{matplotlib} \citep{Hunter+2007}, \texttt{NumPy} \citep{2020NumPy-Array},

### 2021-11-16 src/ms.tex
add showyourwork reference

@@
 We make use of the following Python packages: \texttt{matplotlib} \citep{Hunter+2007}, \texttt{NumPy} \citep{2020NumPy-Array},
-\texttt{Astropy} \citep[\url{http://www.astropy.org}][]{AstropyCollaboration+2013,AstropyCollaboration+2018}, \texttt{Seaborn} \citep{Waskom+2021}, \texttt{SciPy} \citep{2020SciPy-NMeth}, \texttt{Numba} \citep{numba} and \texttt{Schwimmbad} \citep{Price-Whelan+2017}.}
+\texttt{Astropy} \citep[\url{http://www.astropy.org}][]{AstropyCollaboration+2013,AstropyCollaboration+2018}, \texttt{Seaborn} \citep{Waskom+2021}, \texttt{SciPy} \citep{2020SciPy-NMeth}, \texttt{Numba} \citep{numba} and \texttt{Schwimmbad} \citep{Price-Whelan+2017}.
+This paper was compiled using \texttt{showyourwork} \citep{Luger+2021}.}
 

### 2021-11-16 src/ms.tex
some final acknowledgements

@@
 In particular, we thank Lieke van Son for her innovation in inventing the name \lw{}!
-TW also thanks Floor Broekgaarden for first suggesting that he investigate LISA and the derivation of the SNR calculation.
+TW thanks Floor Broekgaarden for first suggesting that he investigate LISA and the derivation of the SNR calculation.
+KB thanks Shane L.
+Larson and Kyle Kremer for \emph{several} conversations about the SNR derivation.
 

### 2021-11-18 src/figures/detector_snr_ratio.py
change colourbar scale on ratio plot

@@ -59,7 +59,7 @@ ratio = ratio.reshape(F.shape)
 
 # make contours of the ratio of SNR
 ratio_cont = ax.contourf(F, E, ratio, cmap="PRGn_r",
-                         norm=TwoSlopeNorm(vcenter=1.0, vmin=0.0, vmax=2.0), levels=20)
+                         norm=TwoSlopeNorm(vcenter=1.0, vmin=0.0, vmax=3.6), levels=20)
 
 for c in ratio_cont.collections:
     c.set_edgecolor("face")
@@ -70,7 +70,7 @@ ax.contour(F, E, ratio, levels=[1.0], colors="grey", linewidths=2.0, linestyles=
 # add a colourbar
 cbar = fig.colorbar(ratio_cont, fraction=2/14, pad=0.02,
                     label=r"$\rho_{\rm LISA} / \rho_{\rm TianQin}$",
-                    ticks=np.arange(0, 2 + 0.5, 0.5))
+                    ticks=np.arange(0, 3.5 + 0.5, 0.5))
 
 # annotate which regions suit each detector
 ax.annotate("LISA stronger", xy=(0.1, 0.53), xycoords="axes fraction", fontsize=0.7 * fs,

### 2021-11-19 src/ms.tex
change equation, add note, acknowledge

@@
     \begin{split}
-    S_{N}(f) &= \frac{1}{L^{2}}\left[\frac{4 S_{a}}{(2 \pi f)^{4}}\left(1+\frac{10^{-4} \unit{Hz}}{f}\right)+S_{x}\right] \\
+    S_{N}(f) &= \frac{10}{3 L^{2}}\left[\frac{4 S_{a}}{(2 \pi f)^{4}}\left(1+\frac{10^{-4} \unit{Hz}}{f}\right)+S_{x}\right] \\
     & \times\left[1+0.6\left(\frac{f}{f_{*}}\right)^{2}\right],
@@
 where $L = \sqrt{3} \times 10^5 \unit{km}$ is the arm length, $S_a = 1 \times 10^{-30} \unit{m^2}{s^{-4}}{Hz^{-1}}$ is the acceleration noise, $S_x = 1 \times 10^{-24} \unit{m^2}{Hz^{-1}}$ is the displacement measurement noise and $f_* = c / 2 \pi L$ is the transfer frequency.
+Note that Eq.~\ref{eq:tianqin} includes an extra factor of $10 / 3$ compared to \citet[][Eq.~13]{Huang+2020}.
+\citet{Huang+2020} absorb this factor into the waveform rather than include it in the power spectral density.
+We include it to match the convention used by \citet{Robson+2019} for the LISA sensitivity curve (see the factor of $10/3$ in Eq.~\ref{eq:LISA_Sn}) so that the sensitivity curves can be compared fairly.
 
@@
     % People
-    We are grateful to Stas Babak, Floor Broekgaarden, Tom Callister, Will Farr, Stephen Justham, Valeria Korol, Mike Lau, Tyson Littenberg, Ilya Mandel, Alberto Sesana, Lieke van Son, the CCA GW group, the BinCosmos group and the COMPAS group for stimulating discussions that influenced and motivated us to complete this project.
+    We are grateful to Stas Babak, Floor Broekgaarden, Tom Callister, Will Farr, Yi-Ming Hu, Stephen Justham, Valeria Korol, Mike Lau, Tyson Littenberg, Ilya Mandel, Alberto Sesana, Lieke van Son, the CCA GW group, the BinCosmos group and the COMPAS group for stimulating discussions that influenced and motivated us to complete this project.
 We thank the BinCosmos group for testing an early version of the package and providing useful feedback.

### 2021-11-19 src/figures/role_eccentricity.py
fix quantity issues

@@ -3,6 +3,9 @@ import numpy as np
 import astropy.units as u
 import matplotlib.pyplot as plt
 
+from astropy.visualization import quantity_support
+quantity_support()
+
 plt.rc('font', family='serif')
 plt.rcParams['text.usetex'] = False
 fs = 24

### 2021-11-19 src/figures/verification_binaries_on_sc.py

@@ -3,6 +3,9 @@ import numpy as np
 import astropy.units as u
 import matplotlib.pyplot as plt
 
+from astropy.visualization import quantity_support
+quantity_support()
+
 plt.rc('font', family='serif')
 plt.rcParams['text.usetex'] = False
 fs = 24
@@ -23,8 +26,7 @@ plt.rcParams.update(params)
 vbs = lw.source.VerificationBinaries()
 vbs.snr = np.array(vbs.true_snr)
 
-fig, ax = lw.visualisation.plot_sensitivity_curve(frequency_range=np.logspace(-4, 0, 1000) * u.Hz,
-                                                  show=False)
+fig, ax = lw.visualisation.plot_sensitivity_curve(frequency_range=np.logspace(-4, 0, 1000) * u.Hz, show=False)
 fig, ax = vbs.plot_sources_on_sc(scatter_s=100, marker="*", snr_cutoff=7, c=vbs.m_1[vbs.snr > 7].to(u.Msun),
                                  fig=fig, ax=ax, show=False, cmap="Oranges", vmin=0.0, vmax=1.0)
 cbar = fig.colorbar(ax.get_children()[1])

### 2021-11-19 src/figures/detector_snr_ratio.py
adjust to new sc curve

@@ -22,7 +22,7 @@ params = {'figure.figsize': (12, 8),
 plt.rcParams.update(params)
 
 # spread out some frequencies and eccentricities
-f_orb_s = np.logspace(-4, -1, 200) * u.Hz
+f_orb_s = np.logspace(-4, -1, 200)
 ecc_s = np.linspace(0, 0.9, 150)
 
 # turn them into a grid
@@ -37,15 +37,15 @@ m_2 = np.repeat(10, len(F_flat)) * u.Msun
 dist = np.repeat(8, len(F_flat)) * u.kpc
 
 # define a set of sources
-sources = lw.source.Source(m_1=m_1, m_2=m_2, f_orb=F_flat, ecc=E_flat, dist=dist, gw_lum_tol=1e-3)
+sources = lw.source.Source(m_1=m_1, m_2=m_2, f_orb=F_flat * u.Hz, ecc=E_flat, dist=dist, gw_lum_tol=1e-3)
 sources.get_merger_time()
 
 # compute the LISA SNR
 LISA_snr = sources.get_snr(verbose=True, which_sources=sources.t_merge > 0.1 * u.yr)
 
 # compute the TianQin SNR
-sources.update_sc_params({"instrument": "TianQin", "t_obs": 4 * u.yr, "L": None})
-TQ_snr = sources.get_snr(instrument="TianQin", verbose=True, which_sources=sources.t_merge > 0.1 * u.yr)
+sources.update_sc_params({"instrument": "TianQin", "L": np.sqrt(3) * 1e5 * u.km})
+TQ_snr = sources.get_snr(verbose=True, which_sources=sources.t_merge > 0.1 * u.yr)
 
 # create a figure
 fig, ax = plt.subplots(figsize=(14, 12))
@@ -54,12 +54,13 @@ ax.set_xlabel(r"Orbital Frequency, $f_{\rm orb} \, [{\rm Hz}]$")
 ax.set_ylabel(r"Eccentricity, $e$")
 
 ratio = np.zeros_like(LISA_snr)
-ratio[LISA_snr > 0] = (LISA_snr[LISA_snr > 0] / TQ_snr[LISA_snr > 0])
+nonzero = np.logical_and(LISA_snr > 0, TQ_snr > 0)
+ratio[nonzero] = LISA_snr[nonzero] / TQ_snr[nonzero]
 ratio = ratio.reshape(F.shape)
 
 # make contours of the ratio of SNR
[…]

### 2021-12-06 src/ms.tex
add recently submitted papers!

@@
 \lw{} has been developed with stellar-origin binary population studies in mind.
-We highlight two upcoming papers that use our package.
-Wagg et al.\ (in prep) investigates several populations of potential LISA sources (double black holes, black hole neutron stars and double neutron stars).
+We highlight two recent papers that use our package.
+\citet{Wagg+2021} investigates several populations of potential LISA sources (double black holes, black hole neutron stars and double neutron stars).
 They use \lw{} to evolve each synthesised source over the age of the Milky Way, make predictions about the LISA detectable population and explore how it varies with different binary physics assumptions.
-Additionally, Thiele et al.\ (in prep) examines the implications of assuming a metallicity-dependent binary fraction for the formation of close double white dwarfs (WDWDs) in the LISA frequency band.
+Additionally, \citet{Thiele+2021} examines the implications of assuming a metallicity-dependent binary fraction for the formation of close double white dwarfs (WDWDs) in the LISA frequency band.
 They use \lw{} to calculate the SNR of WDWDs and, in particular, apply a custom noise model that combines the LISA sensitivity curve from \citet{Robson+2019} with a new fit for the Galactic confusion noise based on their WDWD population.
@@
     \caption{Package structure of \lw{}. Each box represents a module and describes its function. The arrows indicate the inter-dependencies of the modules.}
+    % \marginicon{\href{https://raw.githubusercontent.com/TeamLEGWORK/LEGWORK-paper/main/src/static/package_overview.png}{\color{lwColour}\faFileImage}}}
     \label{fig:package_overview}

### 2021-12-06 src/ms.tex
update title based on JOSS comments

@@
 
-\title{LEGWORK: A python package for computing the evolution and detectability \\ of stellar-origin gravitational-wave sources with space-based detectors}
+\title{Computing the evolution and detectability of stellar-origin gravitational-wave sources\\in space-based detectors using the LEGWORK python package}
 

### 2021-12-08 src/ms.tex
revert title, add margin icon for fig 1

--- 2021-12-06 src/ms.tex
@@
 
-\lw{} can be installed with pip or obtained from the GitHub repository \href{https://github.com/TeamLEGWORK/LEGWORK}{\faGithub}\footnote{\url{https://github.com/TeamLEGWORK/LEGWORK}}.
+\lw{} can be installed with pip or obtained from the GitHub repository \href{https://github.com/TeamLEGWORK/LEGWORK}{\color{\lwColour}\faGithub}\footnote{\url{https://github.com/TeamLEGWORK/LEGWORK}}.
 All examples shown in this paper and code to reproduce the figures are available in the repository.
@@
     \caption{Package structure of \lw{}. Each box represents a module and describes its function. The arrows indicate the inter-dependencies of the modules.}
-    % \marginicon{\href{https://raw.githubusercontent.com/TeamLEGWORK/LEGWORK-paper/main/src/static/package_overview.png}{\color{lwColour}\faFileImage}}}
+    \marginicon{\href{https://raw.githubusercontent.com/TeamLEGWORK/LEGWORK-paper/main/src/static/package_overview.png}{\color{\lwColour}\faFileImage}}
     \label{fig:package_overview}

### 2022-01-24 src/ms.tex
tiny typo
missed "to zero"

@@
 \end{equation}
-where $a_0$ is the initial semi-major axis. Moreover, we can solve for the merger time, the time until the binary will merge, by setting the final semi-major axis in Eq.~\ref{eq:a_over_time_circ}
+where $a_0$ is the initial semi-major axis.
+Moreover, we can solve for the merger time, the time until the binary will merge, by setting the final semi-major axis in Eq.~\ref{eq:a_over_time_circ} to zero.
 \begin{equation}{\lwFuncURL{evol}{get_t_merge_circ}}

### 2022-01-24 src/ms.tex
different colour for changes

--- 2021-12-08 src/ms.tex
@@
-\documentclass[twocolumn]{aastex631}
+\documentclass[twocolumn, linenumbers]{aastex631}
 \received{\today}
@@
 \newcommand{\todo}[1]{{\color{red}{[TODO: #1}]}}
+\newcommand{\referee}[1]{{\color{WildStrawberry} #1}}
 
@@
 \end{equation}
-where $a_0$ is the initial semi-major axis. Moreover, we can solve for the merger time, the time until the binary will merge, by setting the final semi-major axis in Eq.~\ref{eq:a_over_time_circ}
+where $a_0$ is the initial semi-major axis.
+Moreover, we can solve for the merger time, the time until the binary will merge, by setting the final semi-major axis in Eq.~\ref{eq:a_over_time_circ} \referee{to zero}.
 \begin{equation}{\lwFuncURL{evol}{get_t_merge_circ}}

### 2022-01-25 src/ms.tex
it should be frequency space
average the final SNRs too

@@
 \newcommand{\todo}[1]{{\color{red}{[TODO: #1}]}}
+
+% referee command so we can highlight changes
+\definecolor{WildStrawberry}{RGB}{239, 85, 159}
 \newcommand{\referee}[1]{{\color{WildStrawberry} #1}}
@@
     \begin{split}
-        |\tilde{s}(f)|^2 = |&F_+(\theta, \phi, \psi)\tilde{h}_+(t, D_L, \iota, \beta) \\
-        &+ F_{\times}(\theta, \phi, \psi)\tilde{h}_{\times}(t, D_L, \iota, \beta)|^2,
+        |\tilde{s}(f)|^2 = |&F_+(\theta, \phi, \psi)\tilde{h}_+(\referee{f}, D_L, \iota, \beta) \\
+        &+ F_{\times}(\theta, \phi, \psi)\tilde{h}_{\times}(\referee{f}, D_L, \iota, \beta)|^2,
     \end{split}
@@
     \begin{split}
-        |\tilde{s}(f)|^2 &= |F_+(\theta, \phi, \psi)\tilde{h}_+(t, D_L, \iota, \beta)|^2\\
-        &+ |F_{\times}(\theta, \phi, \psi)\tilde{h}_{\times}(t, D_L, \iota, \beta)|^2,
+        |\tilde{s}(f)|^2 &= |F_+(\theta, \phi, \psi)\tilde{h}_+(\referee{f}, D_L, \iota, \beta)|^2\\
+        &+ |F_{\times}(\theta, \phi, \psi)\tilde{h}_{\times}(\referee{f}, D_L, \iota, \beta)|^2,
     \end{split}
@@
 \begin{equation}{\lwFuncURL{snr}{snr_circ_evolving}}
-    \rho^2_{\rm c, e} = \frac{1}{4} \int_{f_{2, i}}^{f_{2, f}} \frac{h_{c, 2}^2}{f_2^2 S_{\rm n}(f_2)} \dd{f_2}. \label{eq:snr_chirp_circ}
+    \referee{\langle \rho \rangle^2_{\rm c, e}} = \frac{1}{4} \int_{f_{2, i}}^{f_{2, f}} \frac{h_{c, 2}^2}{f_2^2 S_{\rm n}(f_2)} \dd{f_2}. \label{eq:snr_chirp_circ}
 \end{equation}
@@
 \begin{align}
-    \rho^2_{\rm e, s} &= \frac{1}{4} \sum_{n=1}^{\infty}  \lim_{\Delta f \to 0} \int_{f_{n}}^{f_{n} + \Delta f_n} \frac{h_{c, n}^2}{f_n^2 S_{\rm n}(f_n)} \dd{f_n}, \\
+    \referee{\langle \rho \rangle^2_{\rm e, s}} &= \frac{1}{4} \sum_{n=1}^{\infty}  \lim_{\Delta f \to 0} \int_{f_{n}}^{f_{n} + \Delta f_n} \frac{h_{c, n}^2}{f_n^2 S_{\rm n}(f_n)} \dd{f_n}, \\
     &= \frac{1}{4} \sum_{n=1}^{\infty} \frac{\Delta f_n \cdot h_{c, n}^2}{f_n^2 S_{\rm n}(f_n)}, \\
@@
 \begin{equation}{\lwFuncURL{snr}{snr_ecc_stationary}}
-    \rho^2_{\rm e, s} = \frac{1}{4} \sum_{n=1}^{\infty} \frac{h_{n}^2 T_{\rm obs}}{S_{\rm n}(f_n)}. \label{eq:snr_stat_ecc}
+    \referee{\langle \rho \rangle^2_{\rm e, s}} = \frac{1}{4} \sum_{n=1}^{\infty} \frac{h_{n}^2 T_{\rm obs}}{S_{\rm n}(f_n)}. \label{eq:snr_stat_ecc}
 \end{equation}
@@
 \begin{equation}{\lwFuncURL{snr}{snr_circ_stationary}}
-    \rho^2_{\rm c, s} = \frac{1}{4} \frac{h_2^2 T_{\rm obs}}{S_{\rm n}(f_2)}.
+    \referee{\langle \rho \rangle^2_{\rm c, s}} = \frac{1}{4} \frac{h_2^2 T_{\rm obs}}{S_{\rm n}(f_2)}.
     \label{eq:snr_stat_circ}
@@
 As we do not specify a position, polarisation or inclination, \lw{} will calculate the SNR averaged over these quantities.
-One can now instantiate a source in \lw{} using these parameters (leaving the mission parameters as the default values, such that we compute the SNR for a 4-year LISA mission).
+\referee{If a user specifies the position, then if either of the polarisation or inclination are not specified then they will be randomly generated.
+LEGWORK does not allow users to specify polarisations or inclinations without positions as presume that the user must know the position if they know the polarisation or inclination of the source.} One can now instantiate a source in \lw{} using these parameters (leaving the mission parameters as the default values, such that we compute the SNR for a 4-year LISA mission).
 As shown in the linked demo, \lw{} quickly computes that the SNR of this binary is $4.49$.

### 2022-01-25 src/ms.tex
add small part about changing sc_params

@@
 Using \lw{} we find that the SNR for each of these cases is $\rho = [2.47, 4.49, 7.85]$.
+\referee{This also need not be limited to a 4-year LISA mission.
+With \lw{} we can additionally specify various parameters for the detector.
+For example, using \lw{} we can find that, for a 5-year TianQin mission with no confusion noise, the SNR for each of these cases is $\rho = [1.07, 1.95, 3.41]$.}
 

### 2022-01-29 src/ms.tex
add PN clarification

@@
 The planned space-based gravitational wave detector LISA (Laser Interferometer Space Antenna) will present an entirely new view of gravitational waves by focusing on lower frequencies ($10^{-5} < f / \unit{Hz} < 10^{-1}$) than ground-based detectors.
-This will enable the study of many new source classes including mergers of supermassive black holes \citep[e.g.][]{Begelman+1980, Klein+2016, Bellovary2019}, extreme mass ratio inspirals \citep[e.g.,][]{Berti2006, Barack2007, Babak2017, Moore2017}, and cosmological GW backgrounds \citep[e.g.,][]{Bartolo2016, Caprini2016, Caldwell2019}.
+This will enable the study of many new source classes including mergers of supermassive black holes \citep[e.g.][]{Begelman+1980, Klein+2016, Bellovary2019}, extreme mass ratio inspirals \citep[e.g.][]{Berti2006, Barack2007, Babak2017, Moore2017}, and cosmological GW backgrounds \citep[e.g.][]{Bartolo2016, Caprini2016, Caldwell2019}.
 However, this frequency regime is also of interest for the detection of local stellar-mass binaries during their inspiral phase.
@@
 With \lw{} one can evolve the orbits of a binary or a collection of binaries and calculate their strain amplitudes for any range of frequency harmonics.
-One can compute the sensitivity curve for LISA or other future gravitational wave detectors (e.g.
-TianQin's curve, or that of a custom instrument) and use it to compute the signal-to-noise ratio of a collection of sources.
+One can compute the sensitivity curve for LISA or other future gravitational wave detectors (e.g.\ TianQin's curve, or that of a custom instrument) and use it to compute the signal-to-noise ratio of a collection of sources.
 Furthermore, \lw{} provides tools to visualise all of the results with easy-to-use plotting functions.
@@
 Specifically, we implement the post-Newtonian expressions by \citet{Peters+1963} and \citet{Peters+1964} for the evolution of binary orbits due to the emission of gravitational waves, equations for the strain amplitudes and signal-to-noise ratios of binaries from various papers \citep[e.g.][]{Flanagan+1998, Finn+2000, Cornish2003, Barack+2004, Moore+2015} and approximations for the LISA and TianQin sensitivity curves given in \citet{Robson+2019} and \citet{Huang+2020} respectively.
+\referee{The post-Newtonian expressions are approximately of order 0.5 as they account for the orbital evolution from energy loss due to the emission of GWs, but don’t include other effects such as spin-orbit coupling.
+We find this is an excellent approximation for stellar-origin sources in the LISA band as any higher order terms are either zero or negligible.}
 

### 2022-01-29 src/ms.tex
data editors won't like that link

@@
 A \docsIcon{} symbol in an equation directly links to the relevant online \lw{} documentation for the implementation of that equation, which additionally contains a link to exact code used to reproduce the equation.
-These derivations are also given in more detail in the \lw{} documentation \href{https://legwork.readthedocs.io/en/latest/notebooks/Derivations.html}{here}, where we show each of the intervening steps in more detail.
+These derivations are also given in more detail in the \lw{} documentation, where we show each of the intervening steps in more detail.
 

### 2022-01-29 src/ms.tex
add note about confusion noises

@@
 \lwModLink{psd} is used for evaluating the effective noise power spectral density of a detector at different frequencies.
-The module currently contains the LISA and TianQin sensitivity curves that can be tweaked by adjusting parameters such as the observation time, confusion noise and even the arm length.
-Additionally, this module allows the user to specify a custom detector sensitivity curve.
+The module currently contains the LISA and TianQin sensitivity curves that can be tweaked by adjusting parameters such as the observation time, response function and even the arm length.
+\referee{For the Galactic confusion noise, a user can choose one of three models \citep{Robson+2019,Huang+2020,Thiele+2021}, use their own custom model, or turn it off entirely.} Additionally, this module allows the user to specify a custom detector sensitivity curve.
 We discuss the relevant equations in Section~\ref{sec:deriv_psd}.
@@
 
+\subsection{\referee{Units and automated testing}}
+
 To ensure stability with physical units, all quantities included in \lw{} use the \texttt{astropy.units} module \citep{AstropyCollaboration+2013, AstropyCollaboration+2018}.
 This means that all inputs to \lw{} can be given in the units of the user's choice and will be automatically converted.
+
 Furthermore, all of the source code in \lw{} is fully tested with continuous integration in the \lw{} GitHub repository.
@@
 Similarly, we verify that the antenna patterns described below produce the expected values when averaged over source positions, inclinations, and polarisations.
+
+\pagebreak
 

### 2022-01-29 src/ms.tex
re-organise strain section

@@
 \end{equation}
-It will be important to know the relative gravitational-wave power radiated into the $n^{\rm th}$ harmonic for a binary with eccentricity $e$ for the following strain and SNR calculations.
+It will be important to know the relative gravitational-wave power radiated into the $n^{\rm th}$ harmonic for a binary with eccentricity $e$ for the strain and SNR calculations.
 This is given by \citet[][Eq.\,20]{Peters+1963}
@@
 \subsection{Strains {\normalfont (\texorpdfstring{\lwModLink{strain}}{strain})}}\label{sec:deriv_strain}
+\referee{\subsubsection{Characteristic Strain}
 The strength of a gravitational wave in a detector at any one moment is determined by the strain amplitude, $h_0$.
@@
 
-Therefore, to account for the integration of the signal over the mission, we instead use the `characteristic' strain amplitude of the $n^{\rm th}$ harmonic \citep[e.g][]{Finn+2000, Moore+2015}\footnote{Note that this is factor of 2 different from \citet{Finn+2000}.
+Therefore, to account for the integration of the signal over the mission, we instead use the `characteristic' strain amplitude of the $n^{\rm th}$ harmonic, $h_{c, n}$, which is the term present in the general signal-to-noise ratio equation.
+This can be related the to the strain amplitude in the $n^{\rm th}$ harmonic, $h_{0, n}$, as \citep[e.g][]{Finn+2000, Moore+2015}\footnote{Note that this is factor of 2 different from \citet{Finn+2000}.
 This is because the factor of 2 is already included in the \citet{Robson+2019} sensitivity curve and so is removed here.}
@@
 \end{equation}
-where $h_{0, n}$ is the strain amplitude in the $n^{\rm th}$ harmonic.
-
 The characteristic strain represents the strain measured by the detector over the duration of the mission (approximated as a single broad-band burst), whilst the strain amplitude is the strength of the GW emission at each instantaneous moment.
-
-\subsubsection{Characteristic Strain}
-
-The characteristic strain from a stellar mass binary in the $n^{\rm th}$ harmonic is given by (e.g. \citealp[][Eq.\,56]{Barack+2004}; \citealp[][Eq.\,5.1]{ Flanagan+1998})
+For a stellar mass binary, the characteristic strain in the $n^{\rm th}$ harmonic is given by (e.g.
+\citealp[][Eq.\,56]{Barack+2004}; \citealp[][Eq.\,5.1]{ Flanagan+1998})}
 \begin{equation}{}

### 2022-02-06 src/ms.tex
add orb subscripts

@@
 \begin{equation}{\lwFuncURL{strain}{amplitude_modulation}}
-    A_{\rm{mod}}^{2}=\frac{1}{2} \left[\left(1+\cos ^{2} \iota\right)^{2}\left\langle F_{+}^{2}\right\rangle+4 \cos ^{2} \iota\left\langle F_{\times}^{2}\right\rangle\right],
+    A_{\rm{mod}}^{2}=\frac{1}{2} \left[\left(1+\cos ^{2} \iota\right)^{2}\left\langle F_{+}^{2}\right\rangle_{\rm \referee{orb}}+4 \cos ^{2} \iota\left\langle F_{\times}^{2}\right\rangle_{\rm \referee{orb}}\right],
 \label{eq:amp_mod}
 \end{equation}
-where $\left\langle F_{+}^{2}\right\rangle$ and $\left\langle F_{\times}^{2}\right\rangle$, the orbit-averaged detector responses, are defined as
+where $\left\langle F_{+}^{2}\right\rangle_{\rm \referee{orb}}$ and $\left\langle F_{\times}^{2}\right\rangle_{\rm \referee{orb}}$, the orbit-averaged detector responses, are defined as
 \begin{equation}{\lwFuncURL{utils}{F_plus_squared}}
     \begin{split}
-        \avg{ F_{+}^{2}} = \frac{1}{4}\big(\cos ^{2} 2 \psi\left\langle D_{+}^{2}\right\rangle &-\sin 4 \psi\left\langle D_{+} D_{\times}\right\rangle\\
-        &+\sin ^{2} 2 \psi\left\langle D_{\times}^{2}\right\rangle\big),
+        \avg{ F_{+}^{2}}_{\rm \referee{orb}} = \frac{1}{4}\big(&\cos ^{2} 2 \psi\left\langle D_{+}^{2}\right\rangle_{\rm \referee{orb}} \\
+        -&\sin 4 \psi\left\langle D_{+} D_{\times}\right\rangle_{\rm \referee{orb}}\\
+        +&\sin ^{2} 2 \psi\left\langle D_{\times}^{2}\right\rangle_{\rm \referee{orb}}\big),
     \end{split}
@@
     \begin{split}
-        \avg{ F_{\times}^{2}} = \frac{1}{4}\big(\cos^{2} 2 \psi \avg{ D_{\times}^{2}} &+\sin 4 \psi \avg{ D_{+} D_{\times}}\\
-        &+\sin ^{2} 2 \psi \avg{ D_{+}^{2}} \big),
+        \avg{ F_{\times}^{2}} = \frac{1}{4}\big(&\cos^{2} 2 \psi \avg{ D_{\times}^{2}}_{\rm \referee{orb}}\\
+        +&\sin 4 \psi \avg{ D_{+} D_{\times}}_{\rm \referee{orb}}\\
+        +&\sin ^{2} 2 \psi \avg{ D_{+}^{2}}_{\rm \referee{orb}} \big),
     \end{split}
@@
     \begin{split}
-        \avg{ D_{+} D_{\times}} = \frac{243}{512} \cos \theta \sin 2 \phi &\left(2 \cos ^{2} \phi-1\right) \\ &\times \left(1+\cos ^{2} \theta\right),
+        \avg{ D_{+} D_{\times}}_{\rm \referee{orb}} = \frac{243}{512} \cos \theta \sin 2 \phi &\left(2 \cos ^{2} \phi-1\right) \\ &\times \left(1+\cos ^{2} \theta\right),
     \end{split}
@@
     \begin{split}
-        \avg{ D_{\times}^{2}} = \frac{3}{512}\big(120 \sin ^{2} \theta &+\cos ^{2} \theta \\
+        \avg{ D_{\times}^{2}}_{\rm \referee{orb}} = \frac{3}{512}\big(120 \sin ^{2} \theta &+\cos ^{2} \theta \\
         &+162 \sin ^{2} 2 \phi \cos ^{2} \theta\big),
@@
     \begin{split}
-        \avg{ D_{+}^{2} } =  \frac{3}{2048}\big[&487+158 \cos ^{2} \theta+7 \cos ^{4} \theta\\
+        \avg{ D_{+}^{2} }_{\rm \referee{orb}} =  \frac{3}{2048}\big[&487+158 \cos ^{2} \theta+7 \cos ^{4} \theta\\
         &-162 \sin ^{2} 2 \phi\left(1+\cos ^{2} \theta\right)^{2}\big].

### 2022-02-17 src/ms.tex
fix some alignment
add in description of requirement for quasi-circular binaries in amplitude modulation use case

@@
 
-We note that since the orbit averaging is carried out in Fourier space, this requires the frequency to be monochromatic and thus is only implemented in \lw{} for quasi-circular binaries (as eccentric systems emit at many frequency harmonics).
+\referee{We note that the amplitude modulation is only implemented in \lw{} for quasi-circular binaries to remain consistent with the calculation in \cite{Cornish2003}.
+Since the expected use case of LEGWORK is estimation of the detectability of large populations of mHz stellar-remnant binaries, for which predictions are uncertain by orders of magnitude in some cases, an extension of \cite{Cornish2003} which includes eccentric binaries is out of the scope of \lw{}.}
 
@@
         |\tilde{s}(f)|^2 = |&F_+(\theta, \phi, \psi)\tilde{h}_+(\referee{f}, D_L, \iota, \beta) \\
-        &+ F_{\times}(\theta, \phi, \psi)\tilde{h}_{\times}(\referee{f}, D_L, \iota, \beta)|^2,
+        + &F_{\times}(\theta, \phi, \psi)\tilde{h}_{\times}(\referee{f}, D_L, \iota, \beta)|^2,
     \end{split}

### 2022-02-17 src/ms.tex
adding ambition for lw 2.0

@@
 \referee{We note that the amplitude modulation is only implemented in \lw{} for quasi-circular binaries to remain consistent with the calculation in \cite{Cornish2003}.
-Since the expected use case of LEGWORK is estimation of the detectability of large populations of mHz stellar-remnant binaries, for which predictions are uncertain by orders of magnitude in some cases, an extension of \cite{Cornish2003} which includes eccentric binaries is out of the scope of \lw{}.}
+Since the expected use case of LEGWORK is estimation of the detectability of large populations of mHz stellar-remnant binaries, for which predictions are uncertain by orders of magnitude in some cases, an extension of \cite{Cornish2003} which includes eccentric binaries is out of the current scope of \lw{}.}
 

### 2022-03-01 src/ms.tex
move eq.44 into averaging section

@@
 
-In LISA's case, when averaged over all angles and polarisations, the antenna patterns are orthogonal and thus $\langle F_+ F_{\times}\rangle = 0$. This means we can rewrite Eq.~\ref{eq:signal} as 
+\subsubsection{Average over position and polarisation}
+\referee{Now, we can consider averaging over different quantities.
+In LISA's case, when averaged over all angles and polarisations, the antenna patterns are orthogonal and thus $\langle F_+ F_{\times}\rangle = 0$.
+This means we can rewrite Eq.~\ref{eq:signal} as
 \begin{equation}{}
@@
 \end{equation}
-which can then be applied to Eq.~\ref{eq:snr_general_start} as
-\begin{equation}{}
-\label{eq:snr_general_simpler}
-    \rho^2 = 4 \int_0^{\infty} \frac{|F_+\tilde{h}_+|^2 + |F_{\times}\tilde{h}_{\times}|^2}{P_{\rm n}(f)} df.
-\end{equation}
-
-\subsubsection{Average over position and polarisation}
-Now, we can consider averaging over different quantities. In particular, we can average over the sky position and polarisation as
-
+which can then be applied to Eq.~\ref{eq:snr_general_start} to give
 \begin{equation}{}
@@
     \langle \rho \rangle^2_{\theta,\phi,\psi} = 4 \int_0^{\infty} df \int \frac{d\Omega_{\theta,\phi}}{4\pi} \int \frac{d\psi}{\pi} \frac{|F_+\,\tilde{h}_+|^2 + |F_{\times}\,\tilde{h}_{\times}|^2}{P_{\rm n}(f)}.
-\end{equation}
+\end{equation}}
 From \cite{Robson+2019}, we can write the position and polarisation average of the signal response function of the instrument, $\mathcal{R}$, as

### 2022-03-03 src/ms.tex
switch to SI units everywhere

@@
 \label{eq:energy_flx}
-    \frac{dE}{dAdt} = \frac{1}{16\pi} \overline{\left[\left(\frac{dh_{+}}{dt}\right)^2 + \left(\frac{dh_{\times}}{dt}\right)^2\right]},
+    \frac{dE}{dAdt} = \frac{1}{16\pi} \referee{\frac{c^3}{G}} \overline{\left[\left(\frac{dh_{+}}{dt}\right)^2 + \left(\frac{dh_{\times}}{dt}\right)^2\right]},
 \end{equation}
@@
 \begin{align}
-    \int_{-\infty}^{+\infty}dt\int dA \frac{dE}{dAdt} &= \int_{0}^{\infty}df \int dA \frac{\pi f^2}{2} \left(|\tilde{h}_{+}|^2 + |\tilde{h}_{\times}|^2 \right).
+    \int_{-\infty}^{+\infty}dt\int dA \frac{dE}{dAdt} &= \int_{0}^{\infty}df \int dA \referee{\frac{c^3}{G}} \frac{\pi f^2}{2} \left(|\tilde{h}_{+}|^2 + |\tilde{h}_{\times}|^2 \right).
 \label{eq:Parseval}
@@
 \begin{equation}{}
-    \int_{-\infty}^{+\infty}dt\int dA \frac{dE}{dAdt} = \int_{0}^{\infty}df \frac{\pi f^2}{2} \int d\Omega \left(|\tilde{H}_{+}|^2 + |\tilde{H}_{\times}|^2 \right).
+    \int_{-\infty}^{+\infty}dt\int dA \frac{dE}{dAdt} = \int_{0}^{\infty}df \frac{\pi f^2 \referee{c^3}}{2 \referee{G}} \int d\Omega \left(|\tilde{H}_{+}|^2 + |\tilde{H}_{\times}|^2 \right).
 \label{eq:Parseval_2}
@@
 \begin{equation}{}
-    \int d\Omega \frac{dE}{d\Omega df} = \frac{\pi f^2}{2} \int d\Omega \left(|\tilde{H}_{+}|^2 + |\tilde{H}_{\times}|^2 \right) .
+    \int d\Omega \frac{dE}{d\Omega df} = \frac{\pi f^2 \referee{c^3}}{2 \referee{G}} \int d\Omega \left(|\tilde{H}_{+}|^2 + |\tilde{H}_{\times}|^2 \right) .
     \label{eq:se_flux}
@@
 \begin{equation}{}
-    \langle \rho \rangle^2 = \frac{4}{D_L^2} \int_0^{\infty} df \frac{1}{P_{\rm n}(f)/\mathcal{R}(f)} \int \frac{d\Omega}{4\pi} \frac{dE}{d\Omega df} \frac{2}{\pi f^2}.
+    \langle \rho \rangle^2 = \frac{4 \referee{G}}{\referee{c^3} D_L^2}\int_0^{\infty} df \frac{1}{P_{\rm n}(f)/\mathcal{R}(f)} \int \frac{d\Omega}{4\pi} \frac{dE}{d\Omega df} \frac{2}{\pi f^2}.
 \end{equation}
@@
 \begin{equation}{}
-    \langle \rho \rangle^2 = \frac{2}{\pi^2 D_L^2}\int_0^{\infty}df \frac{dE}{df}\frac{1}{f^2 P_{\rm n}(f)/\mathcal{R}(f)}.
+    \langle \rho \rangle^2 = \frac{2 \referee{G}}{\pi^2 \referee{c^3} D_L^2} \int_0^{\infty}df \frac{dE}{df}\frac{1}{f^2 P_{\rm n}(f)/\mathcal{R}(f)}.
 \end{equation}
-Finally, noting that $dE/df = dE/dt \times dt/df = \dot{E}/\dot{f}$, we can use the definition of the characteristic strain from Eq.~\ref{eq:char_strain_dedf} (and use $c=G=1$),
-\begin{equation}{}
-    h_{c}^2 = \frac{1}{\pi^2 D_L^2} \left(\frac{2\dot{E}}{\dot{f}}\right),
-\end{equation}
-to finish up our position, direction, and orientation/polarisation averaged SNR as
+Finally, noting that $dE/df = dE/dt \times dt/df = \dot{E}/\dot{f}$, we can use the definition of the characteristic strain from Eq.~\ref{eq:char_strain_dedf} to finish up our position, direction, and orientation/polarisation averaged SNR as
 \begin{equation}{}

### 2022-03-03 src/ms.tex
typo fix, acknowledge our great reviewer

@@
 \referee{If a user specifies the position, then if either of the polarisation or inclination are not specified then they will be randomly generated.
-LEGWORK does not allow users to specify polarisations or inclinations without positions as presume that the user must know the position if they know the polarisation or inclination of the source.} One can now instantiate a source in \lw{} using these parameters (leaving the mission parameters as the default values, such that we compute the SNR for a 4-year LISA mission).
+LEGWORK does not allow users to specify polarisations or inclinations without positions as we presume that the user must know the position if they know the polarisation or inclination of the source.} One can now instantiate a source in \lw{} using these parameters (leaving the mission parameters as the default values, such that we compute the SNR for a 4-year LISA mission).
 As shown in the linked demo, \lw{} quickly computes that the SNR of this binary is $4.49$.
@@
 Larson and Kyle Kremer for \emph{several} conversations about the SNR derivation.
+We additionally thank the anonymous reviewer for their useful comments, which helped to improve the quality and clarity of this paper.
 

### 2022-03-03 src/figures/snr_over_time.py
update environment and showyourwork

@@ -41,7 +41,8 @@ source = lw.source.Source(m_1=np.repeat(m_1, len(ecc_evol)),
                           m_2=np.repeat(m_2, len(ecc_evol)),
                           dist=np.repeat(dist, len(ecc_evol)),
                           ecc=ecc_evol,
-                          f_orb=f_orb_evol)
+                          f_orb=f_orb_evol,
+                          interpolate_g=False)
 
 snr = source.get_snr()
 

### 2022-03-03 src/figures/verification_binaries_on_sc.py
colourbar was for wrong collection

@@ -29,7 +29,8 @@ vbs.snr = np.array(vbs.true_snr)
 fig, ax = lw.visualisation.plot_sensitivity_curve(frequency_range=np.logspace(-4, 0, 1000) * u.Hz, show=False)
 fig, ax = vbs.plot_sources_on_sc(scatter_s=100, marker="*", snr_cutoff=7, c=vbs.m_1[vbs.snr > 7].to(u.Msun),
                                  fig=fig, ax=ax, show=False, cmap="Oranges", vmin=0.0, vmax=1.0)
-cbar = fig.colorbar(ax.get_children()[1])
+
+cbar = fig.colorbar(ax.get_children()[2])
 cbar.set_label(r"Primary Mass, $m_1 \, [{\rm M_{\odot}}]$")
 
 ax.legend(handles=[ax.get_children()[1]], labels=["LISA Verification Binaries (Kupfer+18)"], fontsize=0.7*fs, markerscale=2)

### 2022-06-02 src/scripts/detector_sc_compare.py
upgrade showyourwork

@@ -2,6 +2,7 @@ import legwork as lw
 import numpy as np
 import astropy.units as u
 import matplotlib.pyplot as plt
+import paths
 
 plt.rc('font', family='serif')
 plt.rcParams['text.usetex'] = False
@@ -49,4 +50,4 @@ ax.legend(fontsize=0.7*fs)
 
 ax.set_rasterization_zorder(10000)
 
-plt.savefig("detector_sc_compare.pdf", format="pdf", bbox_inches="tight")
+plt.savefig(paths.figures / "detector_sc_compare.pdf", format="pdf", bbox_inches="tight")

### 2022-06-02 src/scripts/merger_time.py

@@ -2,6 +2,7 @@ import legwork as lw
 import numpy as np
 import astropy.units as u
 import matplotlib.pyplot as plt
+import paths
 
 plt.rc('font', family='serif')
 plt.rcParams['text.usetex'] = False
@@ -56,4 +57,4 @@ ax.clabel(mission_length, fmt={np.log10(4): r"$t_{\rm merge} = 4\,{\rm years}$"}
 
 ax.set_rasterization_zorder(10000)
 
-plt.savefig("merger_time.pdf", format="pdf", bbox_inches="tight")
+plt.savefig(paths.figures / "merger_time.pdf", format="pdf", bbox_inches="tight")

### 2022-06-02 src/scripts/role_eccentricity.py

@@ -2,6 +2,7 @@ import legwork as lw
 import numpy as np
 import astropy.units as u
 import matplotlib.pyplot as plt
+import paths
 
 from astropy.visualization import quantity_support
 quantity_support()
@@ -89,4 +90,4 @@ ax.set_ylim(1e-20, 2e-18)
 
 ax.set_rasterization_zorder(10000)
 
-plt.savefig("role_eccentricity.pdf", format="pdf", bbox_inches="tight")
+plt.savefig(paths.figures / "role_eccentricity.pdf", format="pdf", bbox_inches="tight")

### 2022-06-02 src/scripts/snr_over_time.py

@@ -2,6 +2,7 @@ import legwork as lw
 import numpy as np
 import astropy.units as u
 import matplotlib.pyplot as plt
+import paths
 
 plt.rc('font', family='serif')
 plt.rcParams['text.usetex'] = False
@@ -86,4 +87,4 @@ for ax in axes:
 
 ax.set_rasterization_zorder(10000)
 
-plt.savefig("snr_over_time.pdf", format="pdf", bbox_inches="tight")
+plt.savefig(paths.figures / "snr_over_time.pdf", format="pdf", bbox_inches="tight")

### 2022-06-16 src/tex/ms.tex
upgrade showyourwork
fix amplitude modulation to match Babak+21

--- 2022-03-03 src/ms.tex
@@
-\documentclass[twocolumn, linenumbers]{aastex631}
+\documentclass[twocolumn]{aastex631}
 \received{\today}
@@
 
+\usepackage{showyourwork}
+
 \newcommand{\todo}[1]{{\color{red}{[TODO: #1}]}}
@@
 \definecolor{WildStrawberry}{RGB}{239, 85, 159}
-\newcommand{\referee}[1]{{\color{WildStrawberry} #1}}
+\newcommand{\referee}[1]{{#1}}
 
@@
     \centering
-    \includegraphics[width=\columnwidth]{static/package_overview.png}
+    \includegraphics[width=\columnwidth]{figures/package_overview.png}
     \caption{Package structure of \lw{}. Each box represents a module and describes its function. The arrows indicate the inter-dependencies of the modules.}
@@
 We write that the position of the source on the sky is given by the ecliptic coordinates ($\theta$, $\phi$), the inclination of a source is $\iota$ and the polarisation of a source (determined by its orientation relative to the detector) is given by $\psi$.
-We closely follow the results of \citet{Cornish2003} to write down the amplitude modulation as
+We follow the results of \citet{Cornish2003} to define the amplitude modulation.
+However, we adapt their expression to remain in the frequency domain and follow the conventions of more recent papers \citep[e.g.][Eq.\ 67]{Babak+2021} to write the amplitude modulation as
 
 \begin{equation}{\lwFuncURL{strain}{amplitude_modulation}}
-    A_{\rm{mod}}^{2}=\frac{1}{2} \left[\left(1+\cos ^{2} \iota\right)^{2}\left\langle F_{+}^{2}\right\rangle_{\rm \referee{orb}}+4 \cos ^{2} \iota\left\langle F_{\times}^{2}\right\rangle_{\rm \referee{orb}}\right],
+    A_{\rm{mod}}^{2}= \frac{1}{4} \left(1+\cos ^{2} \iota\right)^{2}\left\langle F_{+}^{2}\right\rangle_{\rm \referee{orb}}+ \cos ^{2} \iota\left\langle F_{\times}^{2}\right\rangle_{\rm \referee{orb}},
 \label{eq:amp_mod}
@@
     \begin{split}
-        S_{\rm n}(f) &= \frac{10}{3 L^2} \qty(P_{\rm OMS}(f) + \frac{4 P_{\rm acc}(f)}{(2 \pi f)^4}) \\
-        &\times \qty(1 + \frac{6}{10} \qty(\frac{f}{f_*}^2)) + S_c(f),
+        S_{\rm n}(f) &= \frac{10}{3 L^2} \qty(P_{\rm OMS}(f) + 2\qty(1 + \cos^2 \qty(\frac{f}{f_*})) \frac{P_{\rm acc}(f)}{(2 \pi f)^4}) \\
+        &\times \qty(1 + \frac{6}{10} \qty(\frac{f}{f_*})^2) + S_c(f),
     \end{split}
@@
     \label{fig:horizon_distance}
+    \script{horizon_distance.py}
 \end{figure*}
@@
     \label{fig:role_eccentricity}
+    \script{role_eccentricity.py}
 \end{figure}
@@
     \label{fig:merger_time}
+    \script{merger_time.py}
 \end{figure}
@@
     \label{fig:detector_sc_compare}
+    \script{detector_sc_compare.py}
 \end{figure}
@@
     \label{fig:detector_snr_ratio}
+    \script{detector_snr_ratio.py}
 \end{figure}
@@
     \label{fig:snr_over_time}
+    \script{snr_over_time.py}
 \end{figure}
@@
     \label{fig:verification_binaries_on_sc}
+    \script{verification_binaries_on_sc.py}
 \end{figure}

### 2022-08-04 src/tex/ms.tex
remove erroneous factors of 1/4
update to latest LEGWORK version before arXiv upload

@@
 \begin{equation}{\lwFuncURL{snr}{snr_circ_evolving}}
-    \referee{\langle \rho \rangle^2_{\rm c, e}} = \frac{1}{4} \int_{f_{2, i}}^{f_{2, f}} \frac{h_{c, 2}^2}{f_2^2 S_{\rm n}(f_2)} \dd{f_2}. \label{eq:snr_chirp_circ}
+    \referee{\langle \rho \rangle^2_{\rm c, e}} = \int_{f_{2, i}}^{f_{2, f}} \frac{h_{c, 2}^2}{f_2^2 S_{\rm n}(f_2)} \dd{f_2}. \label{eq:snr_chirp_circ}
 \end{equation}
-
 For a stationary and eccentric binary we can approximate the integral.
 \begin{align}
-    \referee{\langle \rho \rangle^2_{\rm e, s}} &= \frac{1}{4} \sum_{n=1}^{\infty}  \lim_{\Delta f \to 0} \int_{f_{n}}^{f_{n} + \Delta f_n} \frac{h_{c, n}^2}{f_n^2 S_{\rm n}(f_n)} \dd{f_n}, \\
-    &= \frac{1}{4} \sum_{n=1}^{\infty} \frac{\Delta f_n \cdot h_{c, n}^2}{f_n^2 S_{\rm n}(f_n)}, \\
-    &= \frac{1}{4} \sum_{n=1}^{\infty} \frac{\dot{f}_n \Delta T \cdot h_{c, n}^2}{f_n^2 S_{\rm n}(f_n)}, \\
-    &= \frac{1}{4} \sum_{n=1}^{\infty} \qty(\frac{\dot{f}_n}{f_n^2} h_{c, n}^2) \frac{T_{\rm obs}}{S_{\rm n}(f_n)},
+    \referee{\langle \rho \rangle^2_{\rm e, s}} &= \sum_{n=1}^{\infty}  \lim_{\Delta f \to 0} \int_{f_{n}}^{f_{n} + \Delta f_n} \frac{h_{c, n}^2}{f_n^2 S_{\rm n}(f_n)} \dd{f_n}, \\
+    &= \sum_{n=1}^{\infty} \frac{\Delta f_n \cdot h_{c, n}^2}{f_n^2 S_{\rm n}(f_n)}, \\
+    &= \sum_{n=1}^{\infty} \frac{\dot{f}_n \Delta T \cdot h_{c, n}^2}{f_n^2 S_{\rm n}(f_n)}, \\
+    &= \sum_{n=1}^{\infty} \qty(\frac{\dot{f}_n}{f_n^2} h_{c, n}^2) \frac{T_{\rm obs}}{S_{\rm n}(f_n)},
 \end{align}
-where we have applied \eqref{eq:strain-charstrain} to convert between strains. This gives the following expression
+where we have applied Eq.~\ref{eq:strain-charstrain} to convert between strains. This gives the following expression
 \begin{equation}{\lwFuncURL{snr}{snr_ecc_stationary}}
-    \referee{\langle \rho \rangle^2_{\rm e, s}} = \frac{1}{4} \sum_{n=1}^{\infty} \frac{h_{n}^2 T_{\rm obs}}{S_{\rm n}(f_n)}. \label{eq:snr_stat_ecc}
+    \referee{\langle \rho \rangle^2_{\rm e, s}} = \sum_{n=1}^{\infty} \frac{h_{n}^2 T_{\rm obs}}{S_{\rm n}(f_n)}. \label{eq:snr_stat_ecc}
 \end{equation}
@@
 \begin{equation}{\lwFuncURL{snr}{snr_circ_stationary}}
-    \referee{\langle \rho \rangle^2_{\rm c, s}} = \frac{1}{4} \frac{h_2^2 T_{\rm obs}}{S_{\rm n}(f_2)}.
+    \referee{\langle \rho \rangle^2_{\rm c, s}} = \frac{h_2^2 T_{\rm obs}}{S_{\rm n}(f_2)}.
     \label{eq:snr_stat_circ}
 \end{equation}
-
 For SNR calculations that take into account the amplitude modulation due to LISA's orbital motion (Section~\ref{sec:amplitude_mod}, we apply the calculations as described above but include the modulation in either the strain or characteristic strain as is appropriate.

### 2022-08-04 src/scripts/detector_snr_ratio.py

@@ -4,6 +4,7 @@ import astropy.units as u
 import matplotlib.pyplot as plt
 from matplotlib.colors import TwoSlopeNorm
 import paths
+from copy import copy
 
 plt.rc('font', family='serif')
 plt.rcParams['text.usetex'] = False
@@ -42,10 +43,10 @@ sources = lw.source.Source(m_1=m_1, m_2=m_2, f_orb=F_flat * u.Hz, ecc=E_flat, di
 sources.get_merger_time()
 
 # compute the LISA SNR
-LISA_snr = sources.get_snr(verbose=True, which_sources=sources.t_merge > 0.1 * u.yr)
+LISA_snr = copy(sources.get_snr(verbose=True, which_sources=sources.t_merge > 0.1 * u.yr))
 
 # compute the TianQin SNR
-sources.update_sc_params({"instrument": "TianQin", "L": np.sqrt(3) * 1e5 * u.km})
+sources.update_sc_params({"instrument": "TianQin"})
 TQ_snr = sources.get_snr(verbose=True, which_sources=sources.t_merge > 0.1 * u.yr)
 
 # create a figure

### 2022-08-04 src/tex/ms.tex
update arXiv references

@@
 We note that \lw{} is not the only initiative of this kind.
-We highlight the ``Gravitational Wave Universe Toolbox'' presented by \citet{Yi2021} which was developed to simulate observations on the GW universe with different detectors covering the full gravitational-wave spectrum and source classes.
+We highlight the ``Gravitational Wave Universe Toolbox'' presented by \citet{Yi+2022} which was developed to simulate observations on the GW universe with different detectors covering the full gravitational-wave spectrum and source classes.
 We also highlight ``GWPlotter'' by \citep{Moore+2015}, which provides an interactive plotting tool to compare the sensitivity of different gravitational wave detectors.
